---
title: "Pregnant Female Data Analysis Colorado 2022"
author: "Robin Bedard"
date: '2023-01-12'
output: pdf_document
---


# Packages


```{r}
`%nin%` = Negate(`%in%`)
library("tidyverse")
#library("stringr")
#library("tidyr")
library("PerformanceAnalytics")
library("lme4")
library("lmerTest")
#install.packages("readr")
#library("readr")
library("emmeans")
library("AICcmodavg")
library("ggpubr")
```







# Load & Tidy Data

## Osml, Mass, SVL

```{r}
#Body measurement and measurements that are not replicated
mother_data_final <- read_rds("data/FinalMotherViridis.RDS") 

#Osmolarity data after outliers were removed and replicates were averaged 
mother_temp_osm <- read_rds("data/clean_MotherOsmolality.RDS")

#merging the two data frames so osmolarity data is with all other data
mother_data_all_final <- left_join(mother_data_final, mother_temp_osm, 
                       by = c("Indiv_ID", "CEWL_Blood_Collect_Date")) %>% 
  mutate(Preg_Stage = factor(Preg_Stage, 
                      levels = c("DAC", "1WAC", "2WAC", "DAB", "1WAB")))
```


## CEWL, Osml, Mass, SVL

```{r}
mother_data_all_final_2 <- read_rds("data/mother_data_all_final_2.RDS")
```


## Birthing Timeline

This dataframe includes a column "Day Relative" which is the number of days, relative to the day they gave birth, that the measurements were taken.

```{r}
day_scale <- read_csv("data/day_relative_to_birth.csv")

day_scale_clean <- day_scale %>%
  mutate(IndivID = as.factor(str_trim(IndivID)),
         CEWLBloodCollectDate = as.Date(str_trim(CEWLBloodCollectDate),
                                         format = "%m/%d/%y"),
         DayRelativeToZero = as.numeric(DayRelativeToZero)
  ) %>%
  #rename all column names 
  dplyr::select(Indiv_ID = IndivID, 
                CEWL_Blood_Collect_Date = CEWLBloodCollectDate,
                Day_Relative = DayRelativeToZero) %>%
  fill(Indiv_ID)
```

## Tmt Timeline

First, uploading the CSV with the new column of days relative to number of days in hydration treatment.

```{r}
days_in_tmt <- read_csv("data/days_in_tmt.csv")

days_in_tmt_clean <- days_in_tmt %>%
  mutate(IndivID = as.factor(str_trim(IndivID)),
         CEWLBloodCollectDate = as.Date(str_trim(CEWLBloodCollectDate),
                                         format = "%m/%d/%y"),
         DaysInTrmt = as.numeric(DaysInTrmt),
         GaveBirth = as.factor(GaveBirth)
  ) %>%
  #rename all column names 
  dplyr::select(Indiv_ID = IndivID, 
                CEWL_Blood_Collect_Date = CEWLBloodCollectDate,
                Days_in_Treatment = DaysInTrmt, 
                Gave_Birth = GaveBirth)  %>%
  fill(Indiv_ID)
```



## Merge Data


```{r}
mother_data_all_final_full <- mother_data_all_final_2 %>% 
  left_join(day_scale_clean, 
            by = c("Indiv_ID", "CEWL_Blood_Collect_Date")) %>% 
  left_join(days_in_tmt_clean, 
            by = c("Indiv_ID", "CEWL_Blood_Collect_Date")) %>% 
  mutate(Hydration_Trmt = factor(Hydration_Trmt))

summary(mother_data_all_final_full)
```






## Sub-dfs

First, making a dataframe with the snakes that did give birth. 

```{r}
birth_snakes <- mother_data_all_final_full %>%
  filter(Gave_Birth == "Y") %>% 
  # Robin removes this snake, but I don't remember why
  filter(Indiv_ID != 117)
```

Now, a dataframe with the snakes that did not give birth.

```{r}
no_birth_snakes <- mother_data_all_final_full %>%
  filter(Gave_Birth == "N")
```

At capture measurements... I need a dataframe with only the baseline measurements. 

```{r}
mothers_baseline <- mother_data_all_final_full %>%
  filter(Preg_Stage == "DAC") #DAC= day after capture
```



















# BASELINE CEWL (at capture)

```{r}
baseline_cewl_1 <- lme4::lmer(data = mothers_baseline,
                      CEWL_g_m2h ~
                        Tb_at_CEWL +
                        msmt_temp_C +
                        msmt_RH_percent +
                        Mass_g +
                        SVL_cm +
                        (1|CEWL_Blood_Collect_Date))
                    
car::vif(baseline_cewl_1)
drop1(baseline_cewl_1)
anova(baseline_cewl_1)
```


```{r}
baseline_cewl_2 <- lme4::lmer(data = mothers_baseline,
                      CEWL_g_m2h ~
                        Tb_at_CEWL +
                        msmt_temp_C +
                        msmt_RH_percent +
                        (1|CEWL_Blood_Collect_Date))
                    
drop1(baseline_cewl_2)
anova(baseline_cewl_2)
```


```{r}
baseline_cewl_3 <- lme4::lmer(data = mothers_baseline,
                      CEWL_g_m2h ~
                        msmt_temp_C +
                        msmt_RH_percent +
                        (1|CEWL_Blood_Collect_Date))
                    
drop1(baseline_cewl_3)
anova(baseline_cewl_3)
```


```{r}
baseline_cewl_4 <- lme4::lmer(data = mothers_baseline,
                      CEWL_g_m2h ~
                        msmt_RH_percent +
                        (1|CEWL_Blood_Collect_Date))
```


```{r}
baseline_cewl_null <- lme4::lmer(data = mothers_baseline,
                      CEWL_g_m2h ~ 1 +
                        (1|CEWL_Blood_Collect_Date))
```


## Model selection


```{r}
baseline_cewl_mods <- list(baseline_cewl_1, baseline_cewl_2, 
                           baseline_cewl_3, baseline_cewl_4,
                           baseline_cewl_null)

#specify model names
baeline_cewl_mod_names_all <- c('model1', 
                    'model2',
                    'model3',
                    'model4',
                    'modelnull')

#calculate AIC of each model
cewl_AICc_all <- data.frame(aictab(cand.set = baseline_cewl_mods, 
                                 modnames = baeline_cewl_mod_names_all))
cewl_AICc_all
```




## Final model

Best model was 3 which included:

```{r}
baseline_final_mod <- lmerTest::lmer(data = mothers_baseline,
                      CEWL_g_m2h ~
                        msmt_temp_C +
                        msmt_RH_percent +
                        (1|CEWL_Blood_Collect_Date))

summary(baseline_final_mod)
anova(baseline_final_mod)
```






####?Pub Fig
```{r}
ggplot() +
  geom_jitter(data = mothers_baseline, 
             aes(x = Hydration_Trmt, 
                 y = CEWL_g_m2h, 
                 color = Hydration_Trmt),
             size = 2,
             alpha = 0.5,
             show.legend = TRUE) +
  geom_point(data = mom_baseline_cewl_CI, 
             aes(x = Hydration_Trmt, 
                 y = emmean),
             color = "black", 
             size = 3) +
  theme_classic() +
  annotate(geom = "text", x = 1.6, y = 10, label = "p = 0.30", 
           size = 5) +
  scale_color_manual(values = c("C" = "orange2", "W" = "dodgerblue")) +
  labs(x = "", y = "CEWL (g m2h-1)") +
  geom_errorbar(data = mom_baseline_cewl_CI, aes(x = Hydration_Trmt,
                               y = emmean, 
                               ymin = lower.CL, 
                               ymax = upper.CL,
                               width = .3),
                color = "black") +
  theme(text = element_text(color = "black", 
                            size = 22),
        axis.text = element_text(color = "black", 
                                 size = 16)) +
scale_y_continuous(limits = c(8, 30.5), breaks = seq(8, 31, by = 2)) -> baseline_cewl_fig
```
###?Post Treatment Model
```{r}
not_dac_or_1wab <- mother_data_all_final_8 %>%
  filter(Preg_Stage != "DAC") %>%
  filter(Preg_Stage != "1WAB") %>%
  filter(Preg_Stage != "2WAC")

df_1wac <- mother_data_all_final_8 %>%
  filter(Preg_Stage == "1WAC")

df_dab <- mother_data_all_final_8 %>%
  filter(Preg_Stage == "DAB")

dab_no_dac <- df_dab[c(9, 10, 11, 13, 14, 15, 16, 17, 18), ]

post_tmt_df <- full_join(df_1wac, dab_no_dac)
```

#?SAVANNAH: OLD POST TREATMENT CEWL MODEL
 post treatment linear model to see the effect of treatment on cewl. This has one measurement per individual. For most individuals it is their one week after capture measuremeant. If the snake gave birth prior to that one week timeframe, this is their post birth osmolality.
```{r}
post_tmt_cewl_lm <- lm(data = post_tmt_df, CEWL_g_m2h ~ Hydration_Trmt)

summary(post_tmt_cewl_lm)
anova(post_tmt_cewl_lm)
```
Getting confidence intervals for figure. 
```{r}
CI_mom_CEWL <- data.frame(emmeans(post_tmt_cewl_lm, "Hydration_Trmt"))
```

#####?Pub Figure
```{r}
ggplot() +
  geom_jitter(data = post_tmt_df, 
             aes(x = Hydration_Trmt, 
                 y = CEWL_g_m2h, 
                 color = Hydration_Trmt),
             size = 2,
             alpha = 0.5,
             show.legend = TRUE) +
  geom_point(data = CI_mom_CEWL, 
             aes(x = Hydration_Trmt, 
                 y = emmean),
             color = "black", 
             size = 2) +
  theme_classic() +
  annotate(geom = "text", x = 1.3, y = 30, label = "p = 0.58", 
           size = 5) +
  scale_color_manual(values = c("C" = "orange2", "W" = "dodgerblue")) +
  labs(x = "", y = "") +
  geom_errorbar(data = CI_mom_CEWL, aes(x = Hydration_Trmt,
                               y = emmean, 
                               ymin = lower.CL, 
                               ymax = upper.CL,
                               width = .3),
                color = "black")+
  theme(text = element_text(color = "black", 
                            size = 22),
        axis.text = element_text(color = "black", 
                                 size = 16)) +
  scale_y_continuous(limits = c(8, 30.5), breaks = seq(8, 31, by = 2)) -> cewl_posttmt_mothers

ggsave("Mother CEWL v Treatment Experimental.png", 
       plot = cewl_v_tmt_mothers,
       width = 4,
       height = 4)

```


##?Initial Models (Experimental)
Is there a difference in cewl between the treatment group and the control group the day after capture? 
```{r}
DAC_cewl <- mother_data_all_final_8 %>%
  dplyr::filter(Preg_Stage == "DAC")

DAC_cewl_lm <- lm(CEWL_g_m2h ~ Hydration_Trmt, data = DAC_cewl)

summary(DAC_cewl_lm)
anova(DAC_cewl_lm)

#Result: Baseline rates of CEWL did not differ between treatment groups (estimate = 1.68, SE = 1.60, F(1,27) = 1.10, p = 0.30).
mother_data_all_final_8 %>%
  dplyr::filter(Preg_Stage == "DAC") %>%
  ggplot(aes(x = Hydration_Trmt, y = Plasma_Osmol_Rep_mean, fill = Hydration_Trmt)) +
  geom_boxplot() +
  theme_classic() +
  labs(x = "Hydration Treatment", y = "Plasma Osmolarity")
```
Snakes that DID give birth
```{r}
BirthSnakes_CEWL_LMM_1 <- lme4::lmer(data = birth_snakes,
                      CEWL_g_m2h ~
                        Hydration_Trmt *
                        (Day_Relative + Days_in_Treatment) +
                        calibrated_cloacal_temp +
                        msmt_temp_C +
                        msmt_RH_percent +
                        (1|Indiv_ID))

summary(BirthSnakes_CEWL_LMM_1)
#Lower t values are less significant
drop1(BirthSnakes_CEWL_LMM_1)
anova(BirthSnakes_CEWL_LMM_1)
#Warning means random effects are small. 
```
Based on model, 1 the first variable to drop is the interaction between hydration treatment and the number of days in treatment. 
```{r}
BirthSnakes_CEWL_LMM_2 <- lme4::lmer(data = birth_snakes,
                      CEWL_g_m2h ~
                        Hydration_Trmt *
                        Day_Relative +
                        calibrated_cloacal_temp +
                        msmt_temp_C +
                        msmt_RH_percent +
                        Days_in_Treatment +
                        (1|Indiv_ID))

summary(BirthSnakes_CEWL_LMM_2)
#Lower t values are less significant
drop1(BirthSnakes_CEWL_LMM_2)
anova(BirthSnakes_CEWL_LMM_2)
#Warning means random effects are small. 
```
Based on model 2, the next variable to drop is days in treatment. 
```{r}
BirthSnakes_CEWL_LMM_3 <- lme4::lmer(data = birth_snakes,
                      CEWL_g_m2h ~
                        Hydration_Trmt *
                        Day_Relative +
                        calibrated_cloacal_temp +
                        msmt_temp_C +
                        msmt_RH_percent +
                        (1|Indiv_ID))

summary(BirthSnakes_CEWL_LMM_3)
#Lower t values are less significant
drop1(BirthSnakes_CEWL_LMM_3)
anova(BirthSnakes_CEWL_LMM_3)
#Warning means random effects are small. 
```
Based on model 3, the next variable to drop is the interaction between hydration treatment and day relative. 
```{r}
BirthSnakes_CEWL_LMM_4 <- lme4::lmer(data = birth_snakes,
                      CEWL_g_m2h ~
                        Hydration_Trmt +
                        Day_Relative +
                        calibrated_cloacal_temp +
                        msmt_temp_C +
                        msmt_RH_percent +
                        (1|Indiv_ID))

summary(BirthSnakes_CEWL_LMM_4)
#Lower t values are less significant
drop1(BirthSnakes_CEWL_LMM_4)
anova(BirthSnakes_CEWL_LMM_4)
#Warning means random effects are small. 
```
Based on model 4, the next variable to drop is hydration treatment. 
```{r}
BirthSnakes_CEWL_LMM_5 <- lme4::lmer(data = birth_snakes,
                      CEWL_g_m2h ~
                        calibrated_cloacal_temp +
                        msmt_temp_C +
                        Day_Relative +
                        msmt_RH_percent +
                        (1|Indiv_ID))

summary(BirthSnakes_CEWL_LMM_5)
#Lower t values are less significant
drop1(BirthSnakes_CEWL_LMM_5)
anova(BirthSnakes_CEWL_LMM_5)
#Warning means random effects are small. 
```
Next variable to drop is day relative 
```{r}
BirthSnakes_CEWL_LMM_6 <- lme4::lmer(data = birth_snakes,
                      CEWL_g_m2h ~
                        calibrated_cloacal_temp +
                        msmt_temp_C +
                        msmt_RH_percent +
                        (1|Indiv_ID))

summary(BirthSnakes_CEWL_LMM_6)
#Lower t values are less significant
drop1(BirthSnakes_CEWL_LMM_6)
anova(BirthSnakes_CEWL_LMM_6)
#Warning means random effects are small. 
```
next to drop is body temp
```{r}
BirthSnakes_CEWL_LMM_7 <- lme4::lmer(data = birth_snakes,
                      CEWL_g_m2h ~
                        msmt_temp_C +
                        msmt_RH_percent +
                        (1|Indiv_ID))

summary(BirthSnakes_CEWL_LMM_7)
#Lower t values are less significant
drop1(BirthSnakes_CEWL_LMM_7)
anova(BirthSnakes_CEWL_LMM_7)
#Warning means random effects are small. 
```
Next to drop is ambient temp
```{r}
BirthSnakes_CEWL_LMM_8 <- lme4::lmer(data = birth_snakes,
                      CEWL_g_m2h ~
                        msmt_RH_percent +
                        (1|Indiv_ID))

summary(BirthSnakes_CEWL_LMM_8)
#Lower t values are less significant
drop1(BirthSnakes_CEWL_LMM_8)
anova(BirthSnakes_CEWL_LMM_8)
#Warning means random effects are small. 
```
null model 
```{r}
BirthSnakes_CEWL_LMM_null <- lme4::lmer(data = birth_snakes,
                      CEWL_g_m2h ~ 1 + (1|Indiv_ID))

summary(BirthSnakes_CEWL_LMM_null)
#Lower t values are less significant
drop1(BirthSnakes_CEWL_LMM_null)
anova(BirthSnakes_CEWL_LMM_null)
#Warning means random effects are small. 
```
Model Selection
```{r CEWL mod compare}
cewl_models <- list(BirthSnakes_CEWL_LMM_1, BirthSnakes_CEWL_LMM_2, BirthSnakes_CEWL_LMM_3, BirthSnakes_CEWL_LMM_4, BirthSnakes_CEWL_LMM_5, BirthSnakes_CEWL_LMM_6, BirthSnakes_CEWL_LMM_7, BirthSnakes_CEWL_LMM_8, BirthSnakes_CEWL_LMM_null)

#specify model names
cewl_mod_names <- c('model1', 
                    'model2', 
                    'model3',
                    'model4',
                    'model5',
                    'model6',
                    'model7',
                    'model8',
                    'modelnull')

#calculate AIC of each model
cewl_AICc <- data.frame(aictab(cand.set = cewl_models, 
                                 modnames = cewl_mod_names))
cewl_AICc
```










# EXPERIMENTAL CEWL

Since day relative to birth is not significant, I can include all snakes in one model together. 

```{r}
CEWL_LMM_1 <- lme4::lmer(data = mother_data_all_final_full,
                      CEWL_g_m2h ~
                        Hydration_Trmt *
                        Days_in_Treatment +
                        Tb_at_CEWL +
                        msmt_temp_C +
                        msmt_RH_percent +
                        (1|Indiv_ID))

car::vif(CEWL_LMM_1)
drop1(CEWL_LMM_1)
anova(CEWL_LMM_1)
```


```{r}
CEWL_LMM_2 <- lme4::lmer(data = mother_data_all_final_full,
                      CEWL_g_m2h ~
                        Hydration_Trmt +
                        Days_in_Treatment +
                        Tb_at_CEWL +
                        msmt_temp_C +
                        msmt_RH_percent +
                        (1|Indiv_ID))
drop1(CEWL_LMM_2)
anova(CEWL_LMM_2)
```


```{r}
CEWL_LMM_3 <- lme4::lmer(data = mother_data_all_final_full,
                      CEWL_g_m2h ~
                        Hydration_Trmt +
                        Days_in_Treatment +
                        msmt_temp_C +
                        msmt_RH_percent +
                        (1|Indiv_ID))

drop1(CEWL_LMM_3)
anova(CEWL_LMM_3)
```

```{r}
CEWL_LMM_4 <- lme4::lmer(data = mother_data_all_final_full,
                      CEWL_g_m2h ~
                        Hydration_Trmt +
                        msmt_temp_C +
                        msmt_RH_percent +
                        (1|Indiv_ID))

drop1(CEWL_LMM_4)
anova(CEWL_LMM_4)
```


```{r}
CEWL_LMM_5 <- lme4::lmer(data = mother_data_all_final_full,
                      CEWL_g_m2h ~
                        msmt_temp_C +
                        msmt_RH_percent +
                        (1|Indiv_ID))

drop1(CEWL_LMM_5)
anova(CEWL_LMM_5)
```


```{r}
CEWL_LMM_6 <- lme4::lmer(data = mother_data_all_final_full,
                      CEWL_g_m2h ~
                        msmt_RH_percent +
                        (1|Indiv_ID))
```



```{r}
CEWL_LMM_null <- lme4::lmer(data = mother_data_all_final_full,
                      CEWL_g_m2h ~ 1 +
                        (1|Indiv_ID))
```


## Model selection

```{r}
cewl_models_all <- list(CEWL_LMM_1, 
                        CEWL_LMM_2, 
                        CEWL_LMM_3, 
                        CEWL_LMM_4, 
                        CEWL_LMM_5, 
                        CEWL_LMM_6, 
                        CEWL_LMM_null)

#specify model names
cewl_mod_names_all <- c('model1', 
                    'model2', 
                    'model3',
                    'model4',
                    'model5',
                    'model6',
                    'modelnull')

#calculate AIC of each model
cewl_AICc_all <- data.frame(aictab(cand.set = cewl_models_all, 
                                 modnames = cewl_mod_names_all))
cewl_AICc_all
```



## Final model

The best model is model 4.

```{r}
CEWL_LMM_best <- lmerTest::lmer(data = mother_data_all_final_full,
                      CEWL_g_m2h ~
                        Hydration_Trmt +
                        msmt_temp_C +
                        msmt_RH_percent +
                        (1|Indiv_ID))

summary(CEWL_LMM_best)
anova(CEWL_LMM_best, type = "3", ddf = "Kenward-Roger")
```



## Model assumptions

```{r}
plot(CEWL_LMM_best)
shapiro.test(residuals(CEWL_LMM_best))
```












# BASELINE OSMOL

check whether proximity to birthing date affected osmol:

```{r}
mothers_baseline_birthsnakes <- mothers_baseline %>%
  filter(Gave_Birth == "Y")

partur <- lm(data = mothers_baseline_birthsnakes, 
             Plasma_Osmol_Rep_mean ~ Day_Relative)

summary(partur)
anova(partur)
```
Day relative to birth was not significant. Will run all individuals in one model. 


```{r}
baseline_osmol_1 <- lme4::lmer(data = mothers_baseline,
                      Plasma_Osmol_Rep_mean ~
                        Mass_g +
                        SVL_cm +
                        (1|CEWL_Blood_Collect_Date))
                    
summary(baseline_osmol_1)
drop1(baseline_osmol_1)
anova(baseline_osmol_1)

TukeyHSD(aov(data = mothers_baseline, formula = Plasma_Osmol_Rep_mean ~ Rookery_Capture_ID))
```
The capture date didn't account for any of the variance so first dropping the random effect.

```{r}
baseline_osmol_2 <- lm(data = mothers_baseline,
                      Plasma_Osmol_Rep_mean ~
                        Mass_g +
                        SVL_cm)
                    
drop1(baseline_osmol_2)
anova(baseline_osmol_2)
```


```{r}
baseline_osmol_3 <- lm(data = mothers_baseline,
                      Plasma_Osmol_Rep_mean ~
                        SVL_cm)
                    
anova(baseline_osmol_3)
```




```{r}
baseline_osmol_null <- lm(data = mothers_baseline,
                      Plasma_Osmol_Rep_mean ~ 1)
```

## Model selection

```{r}
baseline_osmol_mods <- list(baseline_osmol_2, 
                            baseline_osmol_3, 
                            baseline_osmol_null)

#specify model names
baeline_osmol_mod_names_all <- c('model2', 'model3', 'modelnull')

#calculate AIC of each model
cewl_AICc_all <- data.frame(aictab(cand.set = baseline_osmol_mods, 
                                 modnames = baeline_osmol_mod_names_all))
cewl_AICc_all
```

They are all equivalent.



###?Pub Figure

Linear model mother osmolality DAC

```{r}
osmol_tmt_DAC_lm <- lm(data = mothers_baseline, Plasma_Osmol_Rep_mean ~ Hydration_Trmt)
mom_baseline_osmol_CI <- data.frame(emmeans(osmol_tmt_DAC_lm, "Hydration_Trmt"))

summary(osmol_tmt_DAC_lm)
anova(osmol_tmt_DAC_lm)

ggplot(data = mothers_baseline,
       aes(x = Body_Condition,
           y = Plasma_Osmol_Rep_mean)) +
  geom_point() +
  geom_smooth(method = "lm")
```
Getting CI
```{r}
mom_baseline_osmol_CI <- data.frame(emmeans(osmol_tmt_DAC_lm, "Hydration_Trmt"))
```

```{r}
ggplot() +
  geom_jitter(data = mothers_baseline, 
             aes(x = Hydration_Trmt, 
                 y = Plasma_Osmol_Rep_mean, 
                 color = Hydration_Trmt),
             size = 2,
             alpha = 0.5,
             show.legend = TRUE) +
  geom_point(data = mom_baseline_osmol_CI, 
             aes(x = Hydration_Trmt, 
                 y = emmean),
             color = "black", 
             size = 3) +
  theme_classic() +
  annotate(geom = "text", x = 1, y = 370, label = "p < 0.0001", 
           size = 5) +
  scale_color_manual(values = c("C" = "orange2", "W" = "dodgerblue")) +
  labs(x = "", y = "Osmolality (mmol kg-1)", color = "Treatment", title = "Before Treatment") +
  geom_errorbar(data = mom_baseline_osmol_CI, aes(x = Hydration_Trmt,
                               y = emmean, 
                               ymin = lower.CL, 
                               ymax = upper.CL,
                               width = .3),
                color = "black") +
   theme(text = element_text(color = "black",
                            size = 22),
        axis.text = element_text(color = "black", 
                                 size = 16),
        legend.text = element_text(color = "black",
                                 size = 22),
        plot.title = element_text(color = "black",
                                  size = 22),
        legend.text.align = 0,
        legend.position = "right") + 
  scale_y_continuous(limits = c(270, 382), breaks = seq(270, 382, by = 20)) -> baseline_osmol_mothers_tmrmt_fig

ggsave("Mother Baseline Osmolality by Treatment.png", 
       plot = baseline_osmol_mothers_tmrmt_fig,
       width = 4,
       height = 4)
```

##?Initial Models  (Experimental)
Is there a difference in osmolarity between the treatment group and the control group the day after capture? 
```{r}
DAC_osmol <- mother_data_all_final_8 %>%
  dplyr::filter(Preg_Stage == "DAC")

DAC_osmol_lm <- lm(Plasma_Osmol_Rep_mean ~ Hydration_Trmt, data = DAC_osmol)

summary(DAC_osmol_lm)
anova(DAC_osmol_lm)

#Result: On average, the hydration treatment had higher baseline levels of osmolarity compared to the control group (estimate = 25.03, SE = 5.41, F(1,27) = 21.38, p < 0.0001).
mother_data_all_final_8 %>%
  dplyr::filter(Preg_Stage == "DAC") %>%
  ggplot(aes(x = Hydration_Trmt, y = Plasma_Osmol_Rep_mean, fill = Hydration_Trmt)) +
  geom_boxplot() +
  theme_classic() +
  labs(x = "Hydration Treatment", y = "Plasma Osmolarity")
```
####?Post Treatment Osmolality
```{r}
not_dac_or_1wab <- mother_data_all_final_8 %>%
  filter(Preg_Stage != "DAC") %>%
  filter(Preg_Stage != "1WAB") %>%
  filter(Preg_Stage != "2WAC")

df_1wac <- mother_data_all_final_8 %>%
  filter(Preg_Stage == "1WAC")

df_dab <- mother_data_all_final_8 %>%
  filter(Preg_Stage == "DAB")

dab_no_dac <- df_dab[c(9, 10, 11, 13, 14, 15, 16, 17, 18), ]

osmolality_post_tmt_df <- full_join(df_1wac, dab_no_dac)
```

#SAVANNAH: OLD POST TREATMENT OSMOL MODEL

****Remember that birthing effecting osmolality, so we created two separate models for the snakes that gave birth and those that didn't. See both below. 

post treatment linear model to see the effect of treatment on osmolality. This has one measurement per individual. For most individuals it is their one week after capture measuremeant. If the snake gave birth prior to that one week timeframe, this is their post birth osmolality.
```{r}
post_tmt_osmol_lm <- lm(data = osmolality_post_tmt_df, Plasma_Osmol_Rep_mean ~ Hydration_Trmt)

summary(post_tmt_osmol_lm)
anova(post_tmt_osmol_lm)
```



```{r}
#getting CI
CI_mothers_osmol <- data.frame(emmeans(post_tmt_osmol_lm, "Hydration_Trmt"))

#CI_mothers_osmol <- data.frame(pairs(emmeans(post_tmt_osmol_lm, "Hydration_Trmt")))
```

#####Pub Fig (all snakes)
```{r}
post_tmt_osmol_lm %>%
ggplot() +
  geom_jitter(aes(x = Hydration_Trmt, 
                 y = Plasma_Osmol_Rep_mean, 
                 color = Hydration_Trmt),
             size = 2,
             alpha = 0.5,
             show.legend = TRUE) +
  geom_point(data = CI_mothers_osmol, 
             aes(x = Hydration_Trmt, 
                 y = emmean),
             color = "black", 
             size = 3) +
  theme_classic() +
  annotate(geom = "text", x = 1.5, y = 370, label = "p = 0.054", 
           size = 5) +
  scale_color_manual(values = c("C" = "orange2", "W" = "dodgerblue")) +
  labs(x = "", y = "", color = "", title = "After Treatment") +
  geom_errorbar(data = CI_mothers_osmol, aes(x = Hydration_Trmt,
                               y = emmean, 
                               ymin = lower.CL, 
                               ymax = upper.CL,
                               width = .3),
                color = "black") +
  theme(text = element_text(color = "black",
                            size = 22),
        axis.text = element_text(color = "black", 
                                 size = 16),
        legend.text = element_text(color = "black",
                                 size = 22),
        plot.title = element_text(color = "black",
                                  size = 22),
        legend.text.align = 0,
        legend.position = "right") +
  scale_y_continuous(limits = c(270, 382), breaks = seq(270, 382, by = 20)) -> mother_osmol_posttmt_fig
```







# EXP OSMOL - BIRTH MOTHERS

```{r}
BirthSnakes_LMM_1 <- lme4::lmer(data = birth_snakes,
                      Plasma_Osmol_Rep_mean ~
                        Hydration_Trmt *
                        Days_in_Treatment +
                        Day_Relative +
                        Mass_g +
                        SVL_cm +
                        (1|Indiv_ID))

drop1(BirthSnakes_LMM_1)
anova(BirthSnakes_LMM_1)
```


```{r}
BirthSnakes_LMM_2 <- lme4::lmer(data = birth_snakes,
                      Plasma_Osmol_Rep_mean ~
                        Hydration_Trmt *
                        Days_in_Treatment +
                        Day_Relative +
                        (1|Indiv_ID))

drop1(BirthSnakes_LMM_2)
anova(BirthSnakes_LMM_2)
```


```{r}
BirthSnakes_LMM_3 <- lme4::lmer(data = birth_snakes,
                      Plasma_Osmol_Rep_mean ~
                        Hydration_Trmt +
                        Days_in_Treatment +
                        Day_Relative +
                        (1|Indiv_ID))

drop1(BirthSnakes_LMM_3)
anova(BirthSnakes_LMM_3)
```

```{r}
BirthSnakes_LMM_4 <- lme4::lmer(data = birth_snakes,
                      Plasma_Osmol_Rep_mean ~
                        Days_in_Treatment +
                        Day_Relative +
                        (1|Indiv_ID))

drop1(BirthSnakes_LMM_4)
anova(BirthSnakes_LMM_4)
```


```{r}
BirthSnakes_LMM_5 <- lme4::lmer(data = birth_snakes,
                      Plasma_Osmol_Rep_mean ~
                        Day_Relative +
                        (1|Indiv_ID))

drop1(BirthSnakes_LMM_5)
anova(BirthSnakes_LMM_5)
```


```{r}
BirthSnakes_LMM_null<- lme4::lmer(data = birth_snakes,
                      Plasma_Osmol_Rep_mean ~ 1 +
                        (1|Indiv_ID))
```



## Model selection

```{r}
osmolarity_models <- list(BirthSnakes_LMM_1, BirthSnakes_LMM_2, 
                          BirthSnakes_LMM_3, BirthSnakes_LMM_4, 
                          BirthSnakes_LMM_5, BirthSnakes_LMM_null)

#specify model names
osmolarity_mod_names <- c('model1', 
                    'model2', 
                    'model3',
                    'model4',
                    'model5',
                    'modelnull')

#calculate AIC of each model
osmolarity_AICc <- data.frame(aictab(cand.set = osmolarity_models, 
                                 modnames = osmolarity_mod_names))
osmolarity_AICc
```


## Final model


```{r}
BirthSnakes_LMM_best <- lmerTest::lmer(data = birth_snakes,
                      Plasma_Osmol_Rep_mean ~
                        Hydration_Trmt *
                        Days_in_Treatment +
                        Day_Relative +
                        (1|Indiv_ID))

summary(BirthSnakes_LMM_best)
anova(BirthSnakes_LMM_best)
emtrends(BirthSnakes_LMM_best, 
         "Hydration_Trmt", var = "Days_in_Treatment")
pairs(emtrends(BirthSnakes_LMM_2, 
               "Hydration_Trmt", var = "Days_in_Treatment"))
```


## Model assumptions


```{r}
plot(BirthSnakes_LMM_best)
shapiro.test(residuals(BirthSnakes_LMM_2))
```







# EXP OSMOL - NO BIRTH

```{r}
No_BirthSnakes_LMM_1 <- lme4::lmer(data = no_birth_snakes,
                      Plasma_Osmol_Rep_mean ~
                        Hydration_Trmt *
                        Days_in_Treatment +
                        (1|Indiv_ID))

drop1(No_BirthSnakes_LMM_1)
anova(No_BirthSnakes_LMM_1)
```


```{r}
No_BirthSnakes_LMM_2 <- lme4::lmer(data = no_birth_snakes,
                      Plasma_Osmol_Rep_mean ~
                        Hydration_Trmt +
                        Days_in_Treatment +
                        (1|Indiv_ID))

drop1(No_BirthSnakes_LMM_2)
anova(No_BirthSnakes_LMM_2)
```


```{r}
No_BirthSnakes_LMM_3 <- lme4::lmer(data = no_birth_snakes,
                      Plasma_Osmol_Rep_mean ~
                        Hydration_Trmt +
                        (1|Indiv_ID))
summary(No_BirthSnakes_LMM_3) # raneff no longer explains any variation
```


```{r}
No_BirthSnakes_LMM_null <- lme4::lmer(data = no_birth_snakes,
                      Plasma_Osmol_Rep_mean ~ 1 +
                        (1|Indiv_ID))
```

## Model selection

```{r}
osmolarity_models_nb <- list(No_BirthSnakes_LMM_1, 
                          No_BirthSnakes_LMM_2, 
                          No_BirthSnakes_LMM_3, 
                          No_BirthSnakes_LMM_null)

#specify model names
osmolarity_mod_names_nb <- c('model1', 
                    'model2', 
                    'model3',
                    'modelnull')

#calculate AIC of each model
osmolarity_AICc_nb <- data.frame(aictab(cand.set = osmolarity_models_nb, 
                                 modnames = osmolarity_mod_names_nb))
osmolarity_AICc_nb
```




## Final model
Best model is 1


```{r}
No_BirthSnakes_LMM_best <- lmerTest::lmer(data = no_birth_snakes,
                      Plasma_Osmol_Rep_mean ~
                        Hydration_Trmt *
                        Days_in_Treatment +
                        (1|Indiv_ID))

summary(No_BirthSnakes_LMM_1)
anova(No_BirthSnakes_LMM_1)
emtrends(No_BirthSnakes_LMM_1, 
         "Hydration_Trmt", var = "Days_in_Treatment")
pairs(emtrends(No_BirthSnakes_LMM_1, 
               "Hydration_Trmt", var = "Days_in_Treatment"))
```


## Model assumptions

```{r}
plot(No_BirthSnakes_LMM_best)
shapiro.test(residuals(No_BirthSnakes_LMM_best))
```









# CEWL vs Osmolarity 


## All values

```{r}
cewl_osmol_lm <- lm(data = mother_data_all_final_full,
                    CEWL_g_m2h ~ Plasma_Osmol_Rep_mean)
summary(cewl_osmol_lm)

cewl_osmol_lm_2 <- lm(data = mother_data_all_final_full,
                    Plasma_Osmol_Rep_mean ~ CEWL_g_m2h)
summary(cewl_osmol_lm_2)
```


## Split by timing 

```{r}
mothers_DAC <- mother_data_all_final_full %>%
  filter(Preg_Stage == "DAC")

mothers_DAB <- mother_data_all_final_full %>%
  filter(Preg_Stage == "DAB")

mothers_1WAC <- mother_data_all_final_full %>%
  filter(Preg_Stage == "1WAC")
```


## Day after capture

```{r}
dac_lm <- lm(data = mothers_DAC, CEWL_g_m2h ~ Plasma_Osmol_Rep_mean)
summary(dac_lm)
anova(dac_lm)
```





## Day after birth

```{r}
dab_lm <- lm(data = mothers_DAB, CEWL_g_m2h ~ Plasma_Osmol_Rep_mean)
summary(dab_lm)
anova(dab_lm)
```

















# TMT EFFECTS

Use a subset of data to examine only the effect of supplemental hydration: compare maternal plasma osmolality, CEWL, and body mass recorded the day after capture versus measurements taken after one week in treatment.

Run LMM with individual ID as a random effect (2 obs per ind), followed by pairwise comparisons.

If a female gave birth within one week of capture, we used her at-birth measurements.


## Prep Data

```{r}
# mothers with 1wac msmts
have_1wac <- mother_data_all_final_full %>% 
  filter(Preg_Stage == "1WAC")
# mothers that did not have a 1wac msmt bc gave birth before then
missing_1wac <- mother_data_all_final_full %>% 
  filter(!(Indiv_ID %in% have_1wac$Indiv_ID))

# 20 indivuals with dac vs 1wac comparison
dacwac <- mother_data_all_final_full %>% 
  filter(Indiv_ID %in% have_1wac$Indiv_ID) %>% 
  filter(Preg_Stage %in% c("DAC", "1WAC"))

# 9 individuals with dac vs dab comparison
dacdab <- mother_data_all_final_full %>% 
  filter(Indiv_ID %in% missing_1wac$Indiv_ID) %>% 
  filter(Preg_Stage %in% c("DAC", "DAB"))

# both comparisons
tmt_befaft <- rbind(dacdab, dacwac) %>% 
  mutate(Preg_Stage = factor(Preg_Stage,
                       labels = c("Before", "After", "After"))) 

# changes in vars
deltas <- tmt_befaft %>%
  arrange(Indiv_ID, CEWL_Blood_Collect_Date) %>% 
  group_by(Indiv_ID) %>%
  mutate(
    delta_mass = lag(Mass_g) - Mass_g,
    delta_osml = lag(Plasma_Osmol_Rep_mean) - Plasma_Osmol_Rep_mean,
    delta_CEWL = lag(CEWL_g_m2h) - CEWL_g_m2h
  ) %>%
  filter(complete.cases(delta_mass))

# check all individuals have 2 values
tmt_befaft %>% 
  group_by(Indiv_ID) %>% 
  count()

summary(tmt_befaft)
```




## MASS 

*left off here! need to go through the rest of the rmd, which I think all corresponds to fig1. Then, I can connect the baseline/tmt models to where they are presented in the ms. then, I can delete the rest of the stuff in this doc.*

```{r}
new_mass_lm <- lme4::lmer(data = tmt_befaft, 
                Mass_g ~ Preg_Stage * Hydration_Trmt + (1|Indiv_ID))

Means1 <- emmeans(new_mass_lm, pairwise ~ Preg_Stage | Hydration_Trmt)
Means1$emmean
Means1$contrasts

Means2 <- emmeans(new_mass_lm, pairwise ~ Hydration_Trmt | Preg_Stage)
Means2$emmean
Means2$contrasts

new_mass_lm_CI <- data.frame(emmeans(new_mass_lm, pairwise ~ Hydration_Trmt | Preg_Stage)$emmean)

new_mass_lm_CI <- new_mass_lm_CI %>% 
  mutate(Preg_Stage = str_replace_all(Preg_Stage, "DAC", "Before Treatment")) %>%
  mutate(Preg_Stage = str_replace_all(Preg_Stage, "1WAC", "After Treatment"))
```


Making a new column for the change in mass
```{r}

```
T-test to see if the change in mass is significantly different from 0. T-test on the mean change in mass, so only one observation per indiv. Don't need a paired t-test. 
```{r}
t.test(dac_or_1wac$delta_mass)
#Result: There was no change in mass altogether. 
```
Now seeing if the change in mass is significantly different between treatments 
```{r}
mass_lm <- lm(data = dac_or_1wac, 
   delta_mass ~ Hydration_Trmt)

summary(mass_lm)
anova(mass_lm)

#The change in mass was significantly different for the two treatment groups (estimate = 37.060, SE = 6.43, F(1, 18) = 33.13, p = <0.0001)
```
Creating a df with only W treatment and only C treatment 
```{r}
dac_or_1wac_hyd <- dac_or_1wac %>%
  filter(Hydration_Trmt == "W")

dac_or_1wac_control <- dac_or_1wac %>%
  filter(Hydration_Trmt == "C")
```

T-test to see if the change in mass is significantly different from 0 for hydration group.
```{r}
t.test(dac_or_1wac_hyd$delta_mass)
#For the hydration treatment, mass significantly increased after treatment (t = 3.72, df = 9, p = 0.0048)
```
T-test to see if the change in mass is significantly different from 0 for control group.
```{r}
t.test(dac_or_1wac_control$delta_mass)
#For the control treatment, mass significantly decreased after treatment (t = -4.74, df = 9, p = 0.0011)
```
Change in mass is significantly different for the two treatment groups. WHoo!
CI
```{r}
mass_lm_CI <- data.frame(emmeans(mass_lm, "Hydration_Trmt"))
```

Figure
```{r}
ggplot() +
  geom_jitter(data = dac_or_1wac, 
             aes(x = Hydration_Trmt, 
                 y = delta_mass, 
                 color = Hydration_Trmt),
             size = 2,
             alpha = 0.5) +
  geom_point(data = mass_lm_CI, 
             aes(x = Hydration_Trmt, 
                 y = emmean),
             color = "black", 
             size = 2) +
  theme_classic() +
  annotate(geom = "text", x = 1, y = 30, label = "p < 0.0001", 
           size = 5) +
  scale_color_manual(values = c("C" = "orange2", "W" = "royalblue4")) +
  labs(x = "", y = "Change in Mass (g)", colour = "Hydration Treatment") +
  geom_errorbar(data = mass_lm_CI, aes(x = Hydration_Trmt,
                               y = emmean, 
                               ymin = lower.CL, 
                               ymax = upper.CL,
                               width = .3),
                color = "black") +
  geom_hline(yintercept = 0, linetype = 'dashed', col = 'grey') +
  theme(text = element_text(color = "black", 
                            size = 22),
        axis.text = element_text(color = "black", 
                                 size = 16)) +
  scale_y_continuous(limits = c(-45, 60),
                  breaks = c(-45, -30, -15, 0, 15, 30, 45, 60)) -> change_mass_tmt_mothers
```

```{r}
dac_or_1wac_temp[ , 5] <- factor(dac_or_1wac_temp$Preg_Stage, levels = c("DAC", "1WAC"), labels = c("Before Treatment", "After Treatment"))
```

```{r}
dac_or_1wac <- dac_or_1wac %>%
  mutate(mass_relative = 0)
```

```{r}
dac_or_1wac[ , 5] <- factor(dac_or_1wac$Preg_Stage, levels = c("DAC", "1WAC"), labels = c("Before Treatment", "After Treatment"))
```

```{r}
mass_df <- full_join(dac_or_1wac_temp, dac_or_1wac)

as.numeric(mass_df$delta_mass)

mass_df[ ,26] <- replace(mass_df$delta_mass,is.na(mass_df$delta_mass), 0)
```


```{r}
  ggplot(data = mass_df, 
         aes(x = Preg_Stage, 
           y = delta_mass, 
           colour = Hydration_Trmt)) +
  geom_point(data = mass_df,
             aes(x = Preg_Stage, 
                 y = delta_mass, 
                 colour = Hydration_Trmt),
                 size = 2,
                alpha = 0.5) +
  theme_classic() +
  geom_hline(yintercept = 0, linetype = 'dashed', col = 'grey')+
  geom_line(aes(group = Indiv_ID)) +
  annotate(geom = "text", x = 1, y = 30, label = "p = 0.0048", 
           size = 5, color = "royalblue4") +
  annotate(geom = "text", x = 1, y = -30, label = "p = 0.0011", 
           size = 5, color = "orange2") +
  scale_color_manual(values = c("C" = "orange2", "W" = "royalblue4")) +
  labs(x = "", y = "Change in Mass (g)", colour = "Hydration Treatment") +
  theme(text = element_text(color = "black",
                            size = 22),
        axis.text = element_text(color = "black", 
                                 size = 16),
        legend.text = element_text(color = "black",
                                 size = 22),
        plot.title = element_text(color = "black",
                                  size = 22),
        legend.text.align = 0,
        legend.position = "right") +
  scale_y_continuous(limits = c(-45, 60),
                  breaks = c(-45, -30, -15, 0, 15, 30, 45, 60)) -> change_mass_indiv
```

```{r}
ggarrange(change_mass_tmt_mothers,
           change_mass_indiv,
          ncol = 1, nrow = 2,
          labels = c("A", "B"),
          common.legend = TRUE,
          legend = "bottom"
          ) -> mothers_change_mass

ggsave("mothers change in mass.png", 
       plot = mothers_change_mass, 
       width = 6, 
       height = 12)
```











## OSMOLALITY


```{r}
osmol_lm_time_tmt <- lme4::lmer(data = tmt_befaft, 
    Plasma_Osmol_Rep_mean ~ Hydration_Trmt * Preg_Stage2 + (1|Indiv_ID))

Means3 <- emmeans(osmol_lm_time_tmt, pairwise ~ Preg_Stage2 | Hydration_Trmt)
Means3$emmean
Means3$contrasts

Means4 <- emmeans(osmol_lm_time_tmt, pairwise ~ Hydration_Trmt | Preg_Stage2)
Means4$emmean
Means4$contrasts


osmol_lm_time_tmt_CI <- data.frame(emmeans(osmol_lm_time_tmt, pairwise ~ Hydration_Trmt | Preg_Stage2)$emmean)

tmt_contrasts <- data.frame(emmeans(osmol_lm_time_tmt, pairwise ~ Hydration_Trmt | Preg_Stage2)$contrasts)

pregstage_contrasts <- data.frame(emmeans(osmol_lm_time_tmt, pairwise ~ Preg_Stage2 | Hydration_Trmt)$contrasts)
#is it different between the two time points? 


summary(osmol_lm_time_tmt)
anova(osmol_lm_time_tmt)
```



```{r}
ggplot() +
  geom_jitter(data = osmol_2, 
             aes(x = Preg_Stage2, 
                 y = Plasma_Osmol_Rep_mean, 
                 color = Hydration_Trmt),
             size = 2,
             alpha = 0.5,
             show.legend = TRUE,
             position = position_jitter(height = 0, width = 0.3)) +
  theme_classic() +
#  annotate(geom = "text", x = 1, y = 370, label = "p < 0.0001", 
      #     size = 5) +
  scale_color_manual(values = c("C" = "orange2", "W" = "royalblue4")) +
  labs(x = "", y = "Plasma Osmolality (mmol kg-1)", color = "Treatment") +
  geom_line(data = osmol_lm_time_tmt_CI, 
                aes(x = Preg_Stage2,
                               y = emmean, 
                               width = .3,
                    group = Hydration_Trmt,
                   # group = 1,
                    color = Hydration_Trmt)) +
  geom_errorbar(data = osmol_lm_time_tmt_CI, 
                aes(x = Preg_Stage2,
                               y = emmean, 
                               ymin = lower.CL, 
                               ymax = upper.CL,
                               width = .3,
                    color = Hydration_Trmt)) +
  geom_point(data = osmol_lm_time_tmt_CI, 
             aes(x = Preg_Stage2, 
                 y = emmean,
                 color = Hydration_Trmt), 
             size = 3) +
   theme(text = element_text(color = "black",
                            size = 22),
        axis.text = element_text(color = "black", 
                                 size = 16),
        legend.text = element_text(color = "black",
                                 size = 22),
        plot.title = element_text(color = "black",
                                  size = 22),
        legend.text.align = 0,
        legend.position = "right") + 
  scale_y_continuous(limits = c(280, 382), breaks = seq(280, 382, by = 20)) -> mother_osmolality_all_fig

ggsave("Mother Osmolality All.png", 
       plot = mother_osmolality_all_fig,
       width = 4,
       height = 4)
```










## CEWL 


```{r}
cewl_lm_time_tmt <- lme4::lmer(data = tmt_befaft, 
          CEWL_g_m2h ~ Hydration_Trmt * Preg_Stage2 + (1|Indiv_ID))



Means5 <- emmeans(cewl_lm_time_tmt, pairwise ~ Preg_Stage2 | Hydration_Trmt)
Means5$emmean
Means5$contrasts

Means6 <- emmeans(cewl_lm_time_tmt, pairwise ~ Hydration_Trmt | Preg_Stage2)
Means6$emmean
Means6$contrasts



summary(cewl_lm_time_tmt)
anova(cewl_lm_time_tmt)

cewl_lm_time_tmt_CI <- data.frame(emmeans(cewl_lm_time_tmt, pairwise ~ Hydration_Trmt | Preg_Stage2)$emmean)

tmt_contrasts_cewl <- data.frame(emmeans(cewl_lm_time_tmt, pairwise ~ Hydration_Trmt | Preg_Stage2)$contrasts)

pregstage_contrasts_cewl <- data.frame(emmeans(cewl_lm_time_tmt, pairwise ~ Preg_Stage2 | Hydration_Trmt)$contrasts)
#is it different between the two time points? 
```

```{r}
ggplot() +
  geom_jitter(data = osmol_2, 
             aes(x = Preg_Stage2, 
                 y = CEWL_g_m2h, 
                 color = Hydration_Trmt),
             size = 2,
             alpha = 0.5,
             show.legend = TRUE,
             position = position_jitter(height = 0, width = 0.3)) +
  theme_classic() +
#  annotate(geom = "text", x = 1, y = 370, label = "p < 0.0001", 
      #     size = 5) +
  scale_color_manual(values = c("C" = "orange2", "W" = "royalblue4")) +
  labs(x = "", y = "CEWL (g m2h-1)", color = "Treatment") +
  geom_line(data = cewl_lm_time_tmt_CI, 
                aes(x = Preg_Stage2,
                               y = emmean, 
                               width = .3,
                    group = Hydration_Trmt,
                   # group = 1,
                    color = Hydration_Trmt)) +
  geom_errorbar(data = cewl_lm_time_tmt_CI, 
                aes(x = Preg_Stage2,
                               y = emmean, 
                               ymin = lower.CL, 
                               ymax = upper.CL,
                               width = .3,
                    color = Hydration_Trmt)) +
  geom_point(data = cewl_lm_time_tmt_CI, 
             aes(x = Preg_Stage2, 
                 y = emmean,
                 color = Hydration_Trmt), 
             size = 3) +
   theme(text = element_text(color = "black",
                            size = 22),
        axis.text = element_text(color = "black", 
                                 size = 16),
        legend.text = element_text(color = "black",
                                 size = 22),
        plot.title = element_text(color = "black",
                                  size = 22),
        legend.text.align = 0,
        legend.position = "right")  -> mother_cewl_all
 # scale_y_continuous(limits = c(280, 382), breaks = seq(280, 382, by = 20)) -> mother_osmolality_all_fig
```

```{r}
ggarrange(mother_osmolality_all_fig,
           mother_cewl_all,
          ncol = 1, nrow = 2,
          labels = c("A", "B"),
          common.legend = TRUE,
          legend = "bottom"
          ) -> mothers_osmol_cewl_all

ggsave("mothers change in cewl and osmol.png", 
       plot = mothers_osmol_cewl_all, 
       width = 6, 
       height = 12)
```





































#*PUBLICATION FIGURES
##*FIGURE 1
###osmol raw fig
```{r}
ggplot() +
  geom_jitter(data = osmol_2, 
             aes(x = Preg_Stage2, 
                 y = Plasma_Osmol_Rep_mean, 
                 color = Hydration_Trmt,
                 shape = Hydration_Trmt),
             size = 2.5,
             alpha = 0.5,
             show.legend = TRUE,
             position = position_jitter(height = 0, width = 0.3)) +
  theme_classic() +
 annotate(geom = "text", x = 1, y = 370, label = "*", 
           size = 10) +
 annotate(geom = "text", x = 2, y = 370, label = "*", 
           size = 10) +
 annotate(geom = "text", x = 2.5, y = 328, label = "*", 
           size = 10, color = "orange2") +
 annotate(geom = "text", x = 2.5, y = 316, label = "*", 
           size = 10, color = "royalblue4") +
  scale_color_manual(values = c("orange2", "royalblue4"), labels = c("C" = "Control", "W" = "Hydration Treatment"), name = NULL) +
  scale_shape_manual(values = c(15, 17), name = NULL, labels = c("C" = "Control", "W" = "Hydration Treatment")) +
  labs(x = "", y = "Plasma Osmolality (mmol kg-1)", color = "Treatment") +
  geom_line(data = osmol_lm_time_tmt_CI,
                aes(x = Preg_Stage2,
                               y = emmean, 
                               width = .3,
                    group = Hydration_Trmt,
                   # group = 1,
                    color = Hydration_Trmt)) +
  geom_errorbar(data = osmol_lm_time_tmt_CI, 
                aes(x = Preg_Stage2,
                               y = emmean, 
                               ymin = lower.CL, 
                               ymax = upper.CL,
                               width = .3,
                    color = Hydration_Trmt)) +
  geom_point(data = osmol_lm_time_tmt_CI, 
             aes(x = Preg_Stage2, 
                 y = emmean,
                 color = Hydration_Trmt,
                 shape = Hydration_Trmt), 
             size = 4) +
   theme(text = element_text(color = "black",
                            size = 22),
        axis.text = element_text(color = "black", 
                                 size = 16),
        legend.text = element_text(color = "black",
                                 size = 22),
        plot.title = element_text(color = "black",
                                  size = 22),
        legend.text.align = 0,
        legend.position = "right") + 
  scale_y_continuous(limits = c(280, 382), breaks = seq(280, 382, by = 20))-> mother_osmolality_all_fig_pub
```
###cewl raw fig
```{r}
ggplot() +
  geom_jitter(data = osmol_2, 
             aes(x = Preg_Stage2, 
                 y = CEWL_g_m2h, 
                 color = Hydration_Trmt,
                 shape = Hydration_Trmt),
             size = 2.5,
             alpha = 0.5,
             show.legend = TRUE,
             position = position_jitter(height = 0, width = 0.3)) +
  theme_classic() +
  annotate(geom = "text", x = 2.5, y = 16, label = "//", 
           size = 7) +
  annotate(geom = "text", x = 1, y = 28, label = "NS", 
           size = 4) +
  annotate(geom = "text", x = 2, y = 28, label = "NS", 
           size = 4) +
   scale_color_manual(values = c("orange2", "royalblue4"), labels = c("C" = "Control", "W" = "Hydration Treatment"), name = NULL) +
  scale_shape_manual(values = c(15, 17), name = NULL, labels = c("C" = "Control", "W" = "Hydration Treatment")) +
  labs(x = "", y = "CEWL (g m2h-1)", color = "Treatment") +
  geom_line(data = cewl_lm_time_tmt_CI, 
                aes(x = Preg_Stage2,
                               y = emmean, 
                               width = .3,
                    group = Hydration_Trmt,
                   # group = 1,
                    color = Hydration_Trmt)) +
  geom_errorbar(data = cewl_lm_time_tmt_CI, 
                aes(x = Preg_Stage2,
                               y = emmean, 
                               ymin = lower.CL, 
                               ymax = upper.CL,
                               width = .3,
                    color = Hydration_Trmt)) +
  geom_point(data = cewl_lm_time_tmt_CI, 
             aes(x = Preg_Stage2, 
                 y = emmean,
                 color = Hydration_Trmt,
                 shape = Hydration_Trmt), 
             size = 4) +
   theme(text = element_text(color = "black",
                            size = 22),
        axis.text = element_text(color = "black", 
                                 size = 16),
        legend.text = element_text(color = "black",
                                 size = 22),
        plot.title = element_text(color = "black",
                                  size = 22),
        legend.text.align = 0,
        legend.position = "right")  -> mother_cewl_all_pub
 # scale_y_continuous(limits = c(280, 382), breaks = seq(280, 382, by = 20)) -> 
```
###change in mass fig
```{r}
  ggplot(data = mass_df, 
         aes(x = Preg_Stage, 
           y = delta_mass, 
           colour = Hydration_Trmt,
           shape = Hydration_Trmt)) +
  geom_point(data = mass_df,
             aes(x = Preg_Stage, 
                 y = delta_mass, 
                 colour = Hydration_Trmt),
                 size = 2.5,
                alpha = .5) +
  theme_classic() +
  annotate(geom = "text", x = 2.5, y = 30, label = "*", 
           size = 10, color = "royalblue4") +
  annotate(geom = "text", x = 2.5, y = -30, label = "*", 
           size = 10, color = "orange2") +
  geom_hline(yintercept = 0, linetype = 'dashed', col = 'grey')+
  geom_line(aes(group = Indiv_ID), alpha = 0.5) +
  annotate(geom = "text", x = 2, y = 60, label = "*", 
           size = 10) +
 # annotate(geom = "text", x = 1, y = -30, label = "p = 0.0011", 
   #        size = 5, color = "orange2") +
  scale_color_manual(values = c("orange2", "royalblue4"), labels = c("C" = "Control", "W" = "Hydration Treatment"), name = NULL) +
  scale_shape_manual(values = c(15, 17), name = NULL, labels = c("C" = "Control", "W" = "Hydration Treatment")) +
  labs(x = "", y = "Change in Mass (g)", colour = "Hydration Treatment") +
  theme(text = element_text(color = "black",
                            size = 22),
        axis.text = element_text(color = "black", 
                                 size = 16),
        legend.text = element_text(color = "black",
                                 size = 22),
        plot.title = element_text(color = "black",
                                  size = 22),
        legend.text.align = 0,
        legend.position = "right") +
  scale_y_continuous(limits = c(-45, 60),
                  breaks = c(-45, -30, -15, 0, 15, 30, 45, 60)) -> change_mass_indiv_pub
```
###mass raw fig
```{r}
ggplot() +
  geom_jitter(data = dac_or_1wac_temp, 
             aes(x = Preg_Stage, 
                 y = Mass_g, 
                 color = Hydration_Trmt,
                 shape = Hydration_Trmt),
             size = 2.5,
             alpha = 0.5,
             show.legend = TRUE,
             position = position_jitter(height = 0, width = 0.3)) +
  theme_classic() +
annotate(geom = "text", x = 2.5, y = 455, label = "*", 
           size = 10, color = "orange2") +
 annotate(geom = "text", x = 2.5, y = 490, label = "*", 
           size = 10, color = "royalblue4") +
 annotate(geom = "text", x = 2, y = 730, label = "*", 
           size = 10) +
 annotate(geom = "text", x = 1, y = 740, label = "NS", 
           size = 4) +
  scale_color_manual(values = c("orange2", "royalblue4"), labels = c("C" = "Control", "W" = "Hydration Treatment"), name = NULL) +
  scale_shape_manual(values = c(15, 17), name = NULL, labels = c("C" = "Control", "W" = "Hydration Treatment")) +
  labs(x = "", y = "Mass (g)", color = "Treatment") +
  geom_line(data = new_mass_lm_CI,
                aes(x = Preg_Stage,
                               y = emmean, 
                               width = .3,
                    group = Hydration_Trmt,
                   # group = 1,
                    color = Hydration_Trmt)) +
  geom_errorbar(data = new_mass_lm_CI, 
                aes(x = Preg_Stage,
                               y = emmean, 
                               ymin = lower.CL, 
                               ymax = upper.CL,
                               width = .3,
                    color = Hydration_Trmt)) +
  geom_point(data = new_mass_lm_CI, 
             aes(x = Preg_Stage, 
                 y = emmean,
                 color = Hydration_Trmt,
                 shape = Hydration_Trmt), 
             size = 4) +
   theme(text = element_text(color = "black",
                            size = 22),
        axis.text = element_text(color = "black", 
                                 size = 16),
        legend.text = element_text(color = "black",
                                 size = 22),
        plot.title = element_text(color = "black",
                                  size = 22),
        legend.text.align = 0,
        legend.position = "right") +
  scale_y_continuous(limits = c(280, 800), 
                     breaks = seq(280, 800, by = 100)) -> mother_mass_all_fig_pub
```

###change in osmol fig
```{r}
  ggplot(data = osmol_2, 
         aes(x = Preg_Stage2, 
           y = Change_in_osmol, 
           colour = Hydration_Trmt,
           shape = Hydration_Trmt)) +
  geom_point(data = osmol_2,
             aes(x = Preg_Stage2, 
                 y = Change_in_osmol, 
                 colour = Hydration_Trmt),
                 size = 2.5,
                alpha = .5) +
  theme_classic() +
  annotate(geom = "text", x = 2.5, y = 20, label = "*", 
          size = 10, color = "orange2") +
  annotate(geom = "text", x = 2.5, y = -30, label = "*", 
          size = 10, color = "royalblue4") +
  annotate(geom = "text", x = 2, y = 45, label = "*", 
          size = 10) +
  geom_hline(yintercept = 0, linetype = 'dashed', col = 'grey')+
  geom_line(aes(group = Indiv_ID), alpha = 0.5) +
  scale_color_manual(values = c("orange2", "royalblue4"), labels = c("C" = "Control", "W" = "Hydration Treatment"), name = NULL) +
  scale_shape_manual(values = c(15, 17), name = NULL, labels = c("C" = "Control", "W" = "Hydration Treatment")) +
  labs(x = "", y = "Change in Osmolality (mmol kg-1)", colour = "Hydration Treatment") +
  theme(text = element_text(color = "black",
                            size = 22),
        axis.text = element_text(color = "black", 
                                 size = 16),
        legend.text = element_text(color = "black",
                                 size = 22),
        plot.title = element_text(color = "black",
                                  size = 22),
        legend.text.align = 0,
        legend.position = "right") +
  scale_y_continuous(limits = c(-55, 45),
                  breaks = c(-60, -45, -30, -15, 0, 15, 30, 45)) -> change_osmol_indiv_pub
```
###change in cewl fig
```{r}
  ggplot(data = osmol_2, 
         aes(x = Preg_Stage2, 
           y = Change_in_CEWL, 
           colour = Hydration_Trmt,
           shape = Hydration_Trmt)) +
  geom_point(data = osmol_2,
             aes(x = Preg_Stage2, 
                 y = Change_in_CEWL, 
                 colour = Hydration_Trmt),
                 size = 2.5,
                alpha = .5) +
  theme_classic() +
 annotate(geom = "text", x = 2.5, y = -5, label = "//", 
          size = 7) +
annotate(geom = "text", x = 2, y = 10, label = "NS", 
          size = 4) +
  #annotate(geom = "text", x = 2, y = 45, label = "*", 
         # size = 8) +
  geom_hline(yintercept = 0, linetype = 'dashed', col = 'grey')+
  geom_line(aes(group = Indiv_ID), alpha = 0.5) +
  scale_color_manual(values = c("orange2", "royalblue4"), labels = c("C" = "Control", "W" = "Hydration Treatment"), name = NULL) +
  scale_shape_manual(values = c(15, 17), name = NULL, labels = c("C" = "Control", "W" = "Hydration Treatment")) +
  labs(x = "", y = "Change in CEWL (g m2h-1)", colour = "Hydration Treatment") +
  theme(text = element_text(color = "black",
                            size = 22),
        axis.text = element_text(color = "black", 
                                 size = 16),
        legend.text = element_text(color = "black",
                                 size = 22),
        plot.title = element_text(color = "black",
                                  size = 22),
        legend.text.align = 0,
        legend.position = "right") +
 scale_y_continuous(limits = c(-16, 10),
                 breaks = c(-15, -10, -5, 0, 5, 10)) -> change_cewl_indiv_pub
  
```
####arrange
```{r}
ggarrange(mother_osmolality_all_fig_pub,
            change_osmol_indiv_pub,
            mother_mass_all_fig_pub,
          change_mass_indiv_pub,
          mother_cewl_all_pub,
          change_cewl_indiv_pub,
          ncol = 2, nrow = 3,
          labels = c("A", "B", "C", "D", "E", "F"),
          common.legend = TRUE,
          legend = "bottom"
          ) -> figure_1_publication

ggsave("Publication Figure 1.png", 
       plot = figure_1_publication, 
       width = 10, 
       height = 18)
```

##Fig 2


```{r}
ggplot(data = mother_data_all_final_8, aes(x = msmt_temp_C, y = CEWL_g_m2h)) +
  geom_point(size = 2, 
             alpha = 0.7,
             color = "springgreen3") +
  annotate(geom = "text", 
           x = 26.5, 
           y = 10, 
           label = "p < 0.0001", 
           size = 5) +
  theme_classic() +
  geom_smooth(aes(x = msmt_temp_C, y = CEWL_g_m2h),
              method = "lm", 
              se = TRUE, 
              show.legend = TRUE, 
              size = 1,
              color = "black") +
  labs(x = "Ambient Temperature (C)", 
       y = "CEWL (g m2h-1)") +
  theme(text = element_text(color = "black",
                            size = 22),
        axis.text = element_text(color = "black", 
                                 size = 16),
        legend.text = element_text(color = "black",
                                 size = 22),
        plot.title = element_text(color = "black",
                                  size = 22),
        legend.text.align = 0,
        legend.position = "right") +
  #scale_x_continuous(breaks = c(0, 2, 4, 6, 8, 10, 12, 14, 16), limits = c(0, 16)) +
 scale_y_continuous(limits = c(9, 30.5),
                  breaks = seq(9, 30.5, by = 3)) -> temp_v_cewl_females_pub

```

```{r}

ggplot(data = mother_data_all_final_8, aes(x = msmt_RH_percent, y = CEWL_g_m2h)) +
  geom_point(size = 2, 
             alpha = 0.7, 
             color = "springgreen3") +
  annotate(geom = "text", 
           x = 44, 
           y = 10, 
           label = "p < 0.0001", 
           size = 5) +
  theme_classic() +
  geom_smooth(aes(x = msmt_RH_percent, y = CEWL_g_m2h),
              method = "lm", 
              se = TRUE, 
              show.legend = TRUE, 
              size = 1,
              color = "black") +
  labs(x = "Ambient Humidity (%)", 
       y = "") +
  theme(text = element_text(color = "black",
                            size = 22),
        axis.text = element_text(color = "black", 
                                 size = 16),
        legend.text = element_text(color = "black",
                                 size = 22),
        plot.title = element_text(color = "black",
                                  size = 22),
        legend.text.align = 0,
        legend.position = "right") +
scale_x_continuous(breaks = c(34, 36, 38, 40, 42, 44, 46, 48), limits = c(34, 48)) +
 scale_y_continuous(limits = c(9, 30.5),
                  breaks = seq(9, 30.5, by = 3)) -> humidity_v_cewl_females_pub

```

```{r}
ggarrange(temp_v_cewl_females_pub, humidity_v_cewl_females_pub,
          ncol = 2, nrow = 1,
          labels = c("A", "B"),
          common.legend = TRUE,
          legend = "bottom"
          ) -> CEWL_v_temp_humidity_mothers_pub

ggsave("CEWL vs Temp and Humidity Females.png", 
       plot = CEWL_v_temp_humidity_mothers_pub, 
       width = 10, 
       height = 4)
```