---
title: "CEWL Data Wrangling"
author: "Robin Bedard & Savannah Weaver"
output: 
  rmdformats::html_clean:
    highlight: tango
    thumbnails: FALSE
    toc: TRUE
    toc_depth: 3
---


# Packages


```{r, include=FALSE}
knitr::opts_chunk$set(include = TRUE, message = FALSE, warning = FALSE)
```


```{r setup, include = TRUE, message = FALSE}
if (!require("tidyverse")) install.packages("tidyverse")
library("tidyverse") # workflow and plots
if (!require("rmdformats")) install.packages("rmdformats")
library("rmdformats") # clean html R markdown format
```




# Load Data

1. Compile a list of the filenames I need to read-in.

```{r filenames}
# make a list of file names of all data to load in
my_filenames <- paste("data/CEWL_raw", 
                   list.files(path = "data/CEWL_raw", pattern = "\\.csv$"),
                   sep = "/")
```

2. Make a function that will read in the data from each csv, name and organize the data correctly. 

```{r function to load data}
read_CEWL_file <- function(filename) {
  
  dat <- read_csv(filename) %>%
    # select only the relevant values
    # must do this bc rbind cannot handle diff ncols
    dplyr::select("SeqNo", 
                  date = "Date", 
                  time = "Time", 
                  "Comments", 
                  "Status", 
                  "Termination", 
                  CEWL_g_m2h = "TEWL [g/(m2h)]", 
                  "CV [%]", 
                  "SSWL [g/(m2)]",
                  msmt_temp_C = "AmbT [C]",
                  msmt_RH_percent = "AmbRH [%]", 
                  "ProbeSer", 
                  "FluxCal", 
                  "BaseCal", 
                  "Sensor", 
                  "CapFactor")
  
  # return the dataframe for that single csv file
  dat
}
```

3. Apply the function I made to all of the filenames I compiled, then put all of those dataframes into one dataframe.

```{r load CEWL data}
# apply function to get data from all csvs
all_CEWL_data <- lapply(my_filenames, read_CEWL_file) %>%
  # paste all data files together into one df by row
  reduce(rbind)
summary(all_CEWL_data)
```

4. Filter out failed measurements and properly format data classes.

```{r filter CEWL data}
tidy_CEWL_data <- all_CEWL_data %>%
  # only use completed measurements
  dplyr::filter(Status == "Normal") %>%
  separate(Comments, into = c("Indiv_ID", "rep_no"), sep = "-") %>% 
  # properly format data classes
  mutate(
    date_time = as.POSIXct(paste(date, time), 
                           format = "%m/%d/%y %H:%M:%S"),
    date = mdy(date),
    time = as.POSIXct(time, format = "%H:%M:%S"),
    Status = factor(Status),
    Indiv_ID = factor(Indiv_ID),
    rep_no = factor(rep_no)
  )
summary(tidy_CEWL_data)
```



# Check Data



## Number of Measurements


```{r check n msmts 1}
rep_check <- tidy_CEWL_data %>%
                group_by(Indiv_ID, date) %>%
                count() %>% 
                arrange(n)
head(rep_check)
tail(rep_check)
```



## Measurement Times

Also check that all the measurement times for a given individual on a certain date are within ~10 minutes:

```{r check msmt times}
time_check <- tidy_CEWL_data %>%
  group_by(Indiv_ID, date) %>%
  summarise(min_time = min(date_time),
            max_time = max(date_time),
            msmt_time_range_minutes = ((max_time-min_time))) %>%
  arrange(msmt_time_range_minutes)
head(time_check)
tail(time_check)
```



# Replicates

## Assess Variation

We want the Coefficient of Variation (CV) among our technical replicates to be small. We need to calculate it to identify whether there may be outliers.

```{r asses variation}
CVs <- tidy_CEWL_data %>%
  group_by(Indiv_ID, date) %>%
  summarise(mean = mean(CEWL_g_m2h),
            SD = sd(CEWL_g_m2h),
            CV = (SD/mean) *100,
            min = min(CEWL_g_m2h),
            max = max(CEWL_g_m2h),
            range = max - min
            )
summary(CVs)
hist(CVs$CV)
hist(CVs$range) 
```






## Find Outliers

```{r}
outs <- tidy_CEWL_data %>%
  group_by(Indiv_ID, date) %>%
  summarise(outs = boxplot.stats(CEWL_g_m2h)$out)

outs %>% 
  group_by(Indiv_ID, date) %>% 
  count() %>% 
  arrange(n)
```

oof, individuals 118, 120, and 324 have two outliers on a given date

so, separate second outs into another df

```{r}
out2 <- outs %>% 
  filter((Indiv_ID == 118 & outs == 30.43) | 
           (Indiv_ID == 120 & outs == 21.07) | 
           (Indiv_ID == 324 & outs == 6.98)) %>% 
  rename(out2 = outs)

out1 <- outs %>% 
  filter(!(outs %in% out2$out2))

outs_wide <- out1 %>% 
  left_join(out2, by = c("Indiv_ID", "date"))

outs_wide
```







## Remove Outliers

```{r omit outliers}
# save data for indivs with no outliers
no_outliers <- tidy_CEWL_data %>% 
  left_join(outs_wide, by = c("Indiv_ID", "date")) %>% 
  filter(is.na(outs))

# remove first set of outliers
outliers_omitted1 <- tidy_CEWL_data %>% 
  left_join(outs_wide, by = c("Indiv_ID", "date")) %>%
  filter(complete.cases(outs)) %>% 
  filter(!(CEWL_g_m2h == outs)) 

# save outliers removed round 1
outliers_omitted_save <- outliers_omitted1 %>% 
  filter(is.na(out2))

# remove 2nd round of outliers
outliers_omitted2 <- outliers_omitted1 %>% 
  filter(complete.cases(out2)) %>% 
  filter(!(CEWL_g_m2h == out2))

# put it all back together
outliers_omitted <- no_outliers %>% 
  rbind(outliers_omitted_save) %>% 
  rbind(outliers_omitted2)

# check
nrow(tidy_CEWL_data) == nrow(outs) + nrow(outliers_omitted)
```




## Re-Assess Variation

```{r re-check variation}
new_CVs <- outliers_omitted %>%
  group_by(Indiv_ID, date) %>%
  summarise(mean = mean(CEWL_g_m2h),
            SD = sd(CEWL_g_m2h),
            CV = (SD/mean) *100,
            min = min(CEWL_g_m2h),
            max = max(CEWL_g_m2h),
            range = max - min) %>%   
  mutate(num_ID = as.numeric(as.character(Indiv_ID)))

summary(new_CVs)
hist(new_CVs$CV)
hist(CVs$CV)
hist(new_CVs$range) 
hist(CVs$range) 
```


for mothers only:


```{r}
moms <- new_CVs %>% 
  filter(num_ID %in% c(101, 102, 103, 104, 105, 107, 108, 
                       110, 111, 112, 113, 114, 115, 116, 117, 119, 
                       120, 123, 124, 125, 126, 127, 128, 129, 
                       130, 131, 133, 134, 135))

moms %>% 
  ungroup() %>% 
  summarise_at(
    vars(SD, CV, range),
    list(mean = mean)
  )
```


for neonates only:

```{r}
neos <- new_CVs %>% 
  filter(as.numeric(num_ID) > 290)

neos %>% 
  ungroup() %>% 
  summarise_at(
    vars(SD, CV, range),
    list(mean = mean)
  )
```











# Get Means 

(outliers removed)

```{r get replicate means}
CEWL_final <- outliers_omitted %>%
  group_by(date, Indiv_ID) %>%
  summarise(
    CEWL_g_m2h = mean(CEWL_g_m2h),
    msmt_temp_C = mean(msmt_temp_C),
    msmt_RH_percent = mean(msmt_RH_percent),
    reps = n()
  )
summary(CEWL_final)
```




# Add VPD

```{r}
CEWL_final_VPD <- CEWL_final %>% 
  # calculate VPD
  mutate(
    e_s_kPa = 0.611 * exp((17.502*msmt_temp_C)/(msmt_temp_C + 240.97)), # saturation VP
    e_a_kPa = e_s_kPa*((msmt_RH_percent/100)), # actual VP
    VPD_kPa = e_s_kPa - e_a_kPa # VP deficit
  )
```






# Export

Save the cleaned data for models and figures.

```{r save clean data}
write_rds(CEWL_final_VPD, "data/CEWL_data_all.RDS")
write_csv(CEWL_final_VPD, "data/CEWL_data_all.csv")
```




