---
title: "Pregnant Female Data Analysis Colorado 2022"
author: "Robin Bedard"
date: '2023-01-12'
output: pdf_document
---
Loading required packages
```{r}
`%nin%` = Negate(`%in%`)
#install.packages("ggpubr")
library("ggpubr")
#install.packages("lme4")
library("lme4")
#install.packages("dplyr")
library("dplyr")
#install.packages("tidyverse")
library("tidyverse")
#install.packages("stringr")
library("stringr")
#install.packages("tidyr")
library("tidyr")
#install.packages("PerformanceAnalytics")
library("PerformanceAnalytics")
#install.packages("lmerTest")
library("lmerTest")
#install.packages("readr")
library("readr")
#install.packages("emmeans")
library("emmeans")
#install.packages("AICcmodavg")
library("AICcmodavg")
```

#Cleaning and Organizing
```{r}
setwd("/Users/robinbedard/Desktop/Old Work/Thesis/RDS_files")

#Body measurement and measurements that are not replicated
mother_data_final <- read_rds("FinalMotherViridis.RDS") 
#Osmolarity data after outliers were removed and replicates were averaged 
mother_temp_osm <- read_rds("clean_MotherOsmolality.RDS")
##merging the two data frames so osmolarity data is with all other data
mother_data_all_final <- left_join(mother_data_final, mother_temp_osm, by =c("Indiv_ID", "CEWL_Blood_Collect_Date"))
```
Some data cleaning...
Factoring the pregnancy stages so that they are plotted in the proper order. 
```{r}
mother_data_all_final$Preg_Stage <- factor(mother_data_all_final$Preg_Stage, levels = c("DAC", "1WAC", "2WAC", "DAB", "1WAB")) 
```
Uploading the RDS file that has ALL of the data to do CEWL analysis. This has all body measurements, all CEWL measurements, and all osmolarity measurements for the mothers. CEWL measurements were analyzed on a separate RMD then joined with other dataframe. 
```{r}
mother_data_all_final_2 <- readRDS("/Users/robinbedard/Desktop/Old Work/Thesis/RDS_files/mother_data_all_final_2.RDS")
```

This dataframe includes a column "Day Relative" which is the number of days, relative to the day they gave birth, that the measurements were taken.
```{r}
setwd("/Users/robinbedard/Desktop/Old Work/Thesis/csv files") 
day_scale <- read.csv("DAY RELATIVE TO DAY OF BIRTH - Sheet1.csv")

day_scale_clean <- day_scale %>%
  mutate(IndivID = as.factor(str_trim(IndivID)),
         CEWL.BloodCollectDate = as.Date(str_trim(CEWL.BloodCollectDate),
                                         format = "%m-%d-%y"),
         DayRelativeToZero = as.numeric(DayRelativeToZero)
  ) %>%
  #rename all column names 
  dplyr::select(Indiv_ID = IndivID, CEWL_Blood_Collect_Date = CEWL.BloodCollectDate, Day_Relative = DayRelativeToZero)  %>%
fill(Indiv_ID)

#joining the final table with the day relative to birth column to create a new final dataset 
mother_data_all_final_3 <- left_join(mother_data_all_final_2, day_scale_clean, by = c("Indiv_ID", "CEWL_Blood_Collect_Date"))
```

Averaging the osmolarities by day relative by treatment group
```{r}
osmol_means_by_tmt_dayrelative <- mother_data_all_final_3 %>%
  group_by(Day_Relative, Hydration_Trmt) %>%
  summarise(mean = mean(Plasma_Osmol_Rep_mean))
```
First, uploading the CSV with the new column of days relative to number of days in hydration treatment
```{r}
setwd("/Users/robinbedard/Desktop/Old Work/Thesis/csv files") 
days_in_tmt <- read.csv("DAYS IN TREATMENT - Sheet1.csv")
```

```{r}
days_in_tmt_clean <- days_in_tmt %>%
  mutate(IndivID = as.factor(str_trim(IndivID)),
         CEWL.BloodCollectDate = as.Date(str_trim(CEWL.BloodCollectDate),
                                         format = "%m-%d-%y"),
         DaysInTrmt = as.numeric(DaysInTrmt),
         GaveBirth = as.factor(GaveBirth)
  ) %>%
  #rename all column names 
  dplyr::select(Indiv_ID = IndivID, CEWL_Blood_Collect_Date = CEWL.BloodCollectDate, Days_in_Treatment = DaysInTrmt, Gave_Birth = GaveBirth)  %>%
  fill(Indiv_ID)
```

Joining the final table with the days in treatment column to create a new final data set 
```{r}
mother_data_all_final_4 <- left_join(mother_data_all_final_3, days_in_tmt_clean, by = c("Indiv_ID", "CEWL_Blood_Collect_Date"))
```

Averaging the osmolarities by days in treatments group
```{r}
osmol_means_by_days_in_tmt <- mother_data_all_final_4 %>%
  group_by(Days_in_Treatment, Hydration_Trmt, Gave_Birth) %>%
  summarise(mean = mean(Plasma_Osmol_Rep_mean))
```

Now I am trying to get the change in osmolarity to compare the changes over time. 
Downloading the sheet to calculate the change is osmolarity for each mother. Then reuploading.
```{r}
write.csv(mother_data_all_final_4, "/Users/robinbedard/Desktop/Old Work/Thesis/csv files/All.mother.data.csv")

relative_osmolarities <- read.csv("/Users/robinbedard/Desktop/Old Work/Thesis/csv files/osmol_relative_change.csv")
relative_osmolarities <- relative_osmolarities[ , c(1, 2, 4)]

relative_osmolarities <- relative_osmolarities %>%
  mutate(Indiv_ID = as.factor(str_trim(Indiv_ID)),
         CEWL_Blood_Collect_Date = as.Date(str_trim(CEWL_Blood_Collect_Date),
                                         format = "%m/%d/%y"))

#joining it to the final df
mother_data_all_final_5 <- full_join(mother_data_all_final_4, relative_osmolarities, by = c("Indiv_ID", "CEWL_Blood_Collect_Date"))
```

```{r}
relative_cewl <- read.csv("/Users/robinbedard/Desktop/Old Work/Thesis/csv files/mother_changecewl.csv")
  
relative_cewl <- relative_cewl[ , c(1, 2, 4, 5)]
  
relative_cewl <- relative_cewl %>%
    mutate(Indiv_ID = as.factor(str_trim(Indiv_ID)),
           CEWL_Blood_Collect_Date = as.Date(str_trim(CEWL_Blood_Collect_Date),
                                             format = "%m/%d/%y"))
  
mother_data_all_final_6 <- full_join(mother_data_all_final_5, relative_cewl, by = c("Indiv_ID", "CEWL_Blood_Collect_Date"))

relative_osmol_means <- mother_data_all_final_6 %>%
  group_by(Day_Relative, Hydration_Trmt) %>%
  summarise(mean = mean(Change_in_osmol))
```
##Thermocouple Calibration
First, I need to change an error in the data that has a body temperature of 75.5 for an individual measurement for snake 124. Should be 25.5.
```{r}
mother_data_all_final_6[55, 4] <- 25.5
```

Calibrating the body temperature data so that we know the recorded temperatures are accurate.
Uploading the csv files that has the thermocouple calibration data on it and the thermocouple reference sheet. Joining them together. 
```{r}
setwd("/Users/robinbedard/Desktop/Old Work/Thesis/csv files")
thermo_c <- read.csv("thermoc_calibration.csv")
thermo_coupl <- thermo_c %>%
  dplyr::select(Time, Value) %>% 
  mutate(Time = as.POSIXct(substr(Time, 1,5), format = "%H:%M"))

thermo_ref <- read.csv("thermalcouple_c_reference.csv") %>% 
  mutate(Time = as.POSIXct(Time, format = "%H:%M"))

thermo_c_final <- left_join(thermo_coupl, thermo_ref, by = "Time")
```
Calibrate Thermocouple Data:
First, calculate and save regression curves..
```{r}
# calculate regression curves
regression_a <- lm(data = thermo_c_final,
                   Value ~ Temp)

# create df to store calibration equations
TC_calibration <- data.frame(TC_A = (coef(regression_a))) %>%
  `rownames<-`(c("intercept", "slope"))

#Next, use calibration curves to correct the data we measured:
# this applies respective calibration equation
# to all cloacal thermocouple data points of that proper thermocouple
# 2=slope & 1=intercept

mother_data_all_final_7 <- mother_data_all_final_6 %>%
  mutate(calibrated_cloacal_temp = Tb_at_CEWL*TC_calibration$TC_A[2] +
           TC_calibration$TC_A[1])

summary(mother_data_all_final_7)
```
Now I have a new column with the calibrated cloacal temperature at the time the measurement was taken. 

##Body Condition
Getting the log of SVL and the log of Mass
```{r}
mother_data_all_final_8 <- mother_data_all_final_7 %>%
  mutate(log_Mass = log10(Mass_g)) %>%
  mutate(log_SVL = log10(SVL_cm))

ggplot(data = mother_data_all_final_8, aes(x = log_SVL, y = log_Mass)) +
  geom_point()

bc_lm <- lm(data = mother_data_all_final_8, log_Mass ~ log_SVL)
mother_data_all_final_8$Body_Condition <- bc_lm$resid
```

#Basic Results
```{r}
temp <- filter(mother_data_all_final_8, Preg_Stage == "DAC")
babies <- c(6, NA, 7, 8, 6, NA, NA, NA, NA, 12, NA, 9, 10, NA, 5, 10, NA, NA, 6, 8, 10, 8, 8, 8, NA, 5, 13, 8, 7)
results <- cbind(temp, babies)

#30 females total
dplyr::count(results, Gave_Birth)
#19 gave birth but 1 individual was the day before we left so 18 in study.

mean(results$babies, na.rm = TRUE)

dplyr::count(results, Hydration_Trmt)

results %>%
  filter(Gave_Birth == "Y") %>%
  dplyr::count(Hydration_Trmt)

clutch_bodycond_df <- results %>%
  filter(Gave_Birth == "Y")

clutch_bodycond_lm <- lm(data = clutch_bodycond_df, babies ~ Body_Condition)
summary(clutch_bodycond_lm)

ggplot(data = clutch_bodycond_df, aes(x  = Body_Condition, y = babies)) +
  geom_point()

#clutch size is not related to body condition. 
```

#Plotting Osmolarity Raw Data 
##Osmolarity vs. SVL
```{r}
ggplot(data = mother_data_all_final_8, aes(x = SVL_cm, y = Plasma_Osmol_Rep_mean, colour = Hydration_Trmt)) +
  geom_point() +
  theme_classic() +
  geom_smooth(method = "lm", se = FALSE) +
  labs(x = "SVL (cm)", y = "Plasma Osmolarity (mmol/kg)")
```

##Osmolarity vs. Mass
```{r}
ggplot(data = mother_data_all_final_8, aes(x = Mass_g, y = Plasma_Osmol_Rep_mean, colour = Hydration_Trmt)) +
  geom_point() +
  theme_classic() +
  geom_smooth(method = "lm", se = FALSE) +
  labs(x = "Mass (g)", y = "Plasma Osmolarity (mmol/kg)")
```

##Osmolarity vs. Shed Stage
```{r}
ggplot(data = mother_data_all_final_8, aes(x = Shed_Stage, y = Plasma_Osmol_Rep_mean, colour = Hydration_Trmt)) +
  geom_boxplot() +
  theme_classic() +
  geom_smooth(method = "lm", se = FALSE) +
  labs(x = "Shed Stage", y = "Plasma Osmolarity (mmol/kg)")
```

##Osmolarity vs. Cloacal Temp
```{r}
ggplot(data = mother_data_all_final_8, aes(x = calibrated_cloacal_temp, y = Plasma_Osmol_Rep_mean, colour = Hydration_Trmt)) +
  geom_point() +
  theme_classic() +
  geom_smooth(method = "lm", se = FALSE) +
  labs(x = "Cloacal Temp at Time of Sample Collection", y = "Plasma Osmolarity (mmol/kg)")
```

##Osmolarity vs. Sample Collect Date
```{r}
ggplot(data = mother_data_all_final_8, aes(x = CEWL_Blood_Collect_Date, y = Plasma_Osmol_Rep_mean, colour = Hydration_Trmt)) +
  geom_point() +
  theme_classic() +
  geom_smooth(method = "lm", se = FALSE) +
  labs(x = "Sample Collection Date", y = "Plasma Osmolarity (mmol/kg)")
```

##Osmolarity vs. Rookery Capture ID
This only includes the measurements for the day after capture. 
```{r}
filter(mother_data_all_final_8, Preg_Stage == "DAC") %>%
  ggplot(aes(x = Rookery_Capture_ID, y = Plasma_Osmol_Rep_mean)) +
  geom_boxplot() +
  theme_classic() +
  labs(x = "Rookery Capture Location", y = "Plasma Osmolarity (mmol/kg)")
```

##Osmolarity vs. Hydration Treatment
This includes the initial measurements before the treatments began and after.
```{r}
  ggplot(data = mother_data_all_final_8, aes(x = Hydration_Trmt, y = Plasma_Osmol_Rep_mean)) +
  geom_boxplot() +
  theme_classic() +
  labs(x = "Hydration Treatment", y = "Plasma Osmolarity (mmol/kg)")
```

This does not include the initial measurements so is only the measurements after the hydration treatment began
```{r}
filter(mother_data_all_final_8, Preg_Stage != "DAC") %>%
  ggplot(aes(x = Hydration_Trmt, y = Plasma_Osmol_Rep_mean)) +
  geom_boxplot() +
  theme_classic() +
  labs(x = "Hydration Treatment", y = "Plasma Osmolarity (mmol/kg) After Treatment began")
```

##Osmolarity vs. CEWL
```{r}
  ggplot(data = mother_data_all_final_8, aes(x = CEWL_g_m2h, y = Plasma_Osmol_Rep_mean, colour = Hydration_Trmt)) +
  geom_point() +
  theme_classic() +
  geom_smooth(method = "lm", se = FALSE) +
  labs(x = "CEWL", y = "Plasma Osmolarity (mmol/kg)")
```

##Osmolarity vs. Ambient Temp
```{r}
  ggplot(data = mother_data_all_final_8, aes(x = msmt_temp_C, y = Plasma_Osmol_Rep_mean, colour = Hydration_Trmt)) +
  geom_point() +
  theme_classic() +
  geom_smooth(method = "lm", se = FALSE) +
  labs(x = "Ambient Temp (C)", y = "Plasma Osmolarity (mmol/kg)")
```
##Osmolarity vs. Day Relative to the Day of Birth
```{r}
mother_data_all_final_8 %>%
  filter(Gave_Birth == "Y") %>%
  ggplot() +
  geom_jitter(aes(x = Day_Relative, 
                 y = Plasma_Osmol_Rep_mean, 
                 color = Hydration_Trmt), 
             size = 2, 
             alpha = 0.5) +
  theme_classic() +
  theme(text = element_text(color = "black",
                            size = 22),
        axis.text = element_text(color = "black", 
                                 size = 16),
        legend.text = element_text(color = "black",
                                 size = 22),
        plot.title = element_text(color = "black",
                                  size = 22),
        legend.text.align = 0,
        legend.position = "right") +
  stat_smooth(aes(x = Day_Relative, 
                 y = Plasma_Osmol_Rep_mean, 
                 color = Hydration_Trmt),
                 alpha = 0.5,
                 method = "lm",
                 se = FALSE) +
   stat_smooth(aes(x = Day_Relative, 
                 y = Plasma_Osmol_Rep_mean), 
                 color = "black",
                 method = "lm",
                 se = FALSE) +
  geom_vline(xintercept = 0, linetype = "dashed", color = "grey") +
  scale_color_manual(values = c("C" = "orange2", "W" = "royalblue4")) +
  labs(x = "",
       y = "Osmolality (mmol kg-1)",
       color = "Treatment") +
  scale_x_continuous(breaks = c(-14, -12, -10, -8, -6, -4, -2, 0, 2, 4, 6, 8, 10), limits = c(-14, 10)) +
  scale_y_continuous(limits = c(270, 375), 
                     breaks = seq(270, 375, by = 20)) -> osmol_dayrealtvie_all
```
Control Snakes
```{r}
mother_data_all_final_8 %>%
  filter(Gave_Birth == "Y") %>%
  filter(Hydration_Trmt == "C") %>%
  ggplot() +
  geom_line(aes(x = Day_Relative,
                y = Plasma_Osmol_Rep_mean,
                color = Hydration_Trmt,
                group = Indiv_ID),
            alpha = 1) +
  geom_vline(xintercept = 0, linetype = "dashed", color = "grey") +
  theme_classic() +
  labs(x = "", 
       y = "Osmolality (mmol kg-1)",
       color = "Treatment") +
  scale_color_manual(values = c("C" = "orange2", "W" = "royalblue4")) +
  theme(text = element_text(color = "black",
                            size = 22),
        axis.text = element_text(color = "black", 
                                 size = 16),
        legend.text = element_text(color = "black",
                                 size = 22),
        plot.title = element_text(color = "black",
                                  size = 22),
        legend.text.align = 0,
        legend.position = "right",) +
  scale_x_continuous(breaks = c(-14, -12, -10, -8, -6, -4, -2, 0, 2, 4, 6, 8, 10), limits = c(-14, 10)) +
  scale_y_continuous(limits = c(270, 375), 
                     breaks = seq(270, 375, by = 20)) -> osmol_dayrelative_control_fig
```

Hydration Snakes
```{r}
mother_data_all_final_8 %>%
  filter(Gave_Birth == "Y") %>%
  filter(Hydration_Trmt == "W") %>%
  ggplot() +
  geom_line(aes(x = Day_Relative,
                y = Plasma_Osmol_Rep_mean,
                color = Hydration_Trmt,
                group = Indiv_ID),
            alpha = 1) +
  geom_vline(xintercept = 0, linetype = "dashed", color = "grey") +
  theme_classic() +
  labs(x = "Day Relative to Parturition", 
       y = "Osmolality (mmol kg-1)",
       color = "Treatment") +
  scale_color_manual(values = c("C" = "orange2", "W" = "royalblue4")) +
  theme(text = element_text(color = "black",
                            size = 22),
        axis.text = element_text(color = "black", 
                                 size = 16),
        legend.text = element_text(color = "black",
                                 size = 22),
        plot.title = element_text(color = "black",
                                  size = 22),
        legend.text.align = 0,
        legend.position = "right",) +
  scale_x_continuous(breaks = c(-14, -12, -10, -8, -6, -4, -2, 0, 2, 4, 6, 8, 10), limits = c(-14, 10)) +
  scale_y_continuous(limits = c(270, 375), 
                     breaks = seq(270, 375, by = 20)) -> osmol_dayrelative_hyd_fig
```
###Pub figure
```{r}
ggarrange(osmol_dayrealtvie_all,
           osmol_dayrelative_control_fig, 
           osmol_dayrelative_hyd_fig,
          ncol = 1, nrow = 3,
          labels = c("A", "B", "C"),
          common.legend = TRUE,
          legend = "bottom"
          ) -> mother_osmol_pub_fig_day_relativebirth

ggsave("Osmolality Relative to Birth by Treatment.png", 
       plot = mother_osmol_pub_fig_day_relativebirth, 
       width = 6, 
       height = 14)
```
Attempting all on one figure. 
```{r}
control_birthsnakes <- mother_data_all_final_8 %>%
  filter(Gave_Birth == "Y") %>%
  filter(Hydration_Trmt == "C")

hydration_birthsnakes <- mother_data_all_final_8 %>%
  filter(Gave_Birth == "Y") %>%
  filter(Hydration_Trmt == "W")

all_birthsnakes <- mother_data_all_final_8 %>%
  filter(Gave_Birth == "Y")
```

```{r}
  ggplot() +
  geom_point(data = all_birthsnakes,
              aes(x = Day_Relative, 
                 y = Plasma_Osmol_Rep_mean, 
                 color = Hydration_Trmt), 
             size = 1, 
             alpha = 0.5) +
  geom_line(data = hydration_birthsnakes,
            aes(x = Day_Relative,
                y = Plasma_Osmol_Rep_mean,
                color = Hydration_Trmt,
                group = Indiv_ID),
            alpha = 0.5) +
    geom_line(data = control_birthsnakes,
            aes(x = Day_Relative,
                y = Plasma_Osmol_Rep_mean,
                color = Hydration_Trmt,
                group = Indiv_ID),
            alpha = 0.5) +
  theme_classic() +
  theme(text = element_text(color = "black",
                            size = 22),
        axis.text = element_text(color = "black", 
                                 size = 16),
        legend.text = element_text(color = "black",
                                 size = 22),
        plot.title = element_text(color = "black",
                                  size = 22),
        legend.text.align = 0,
        legend.position = "right") +
   stat_smooth(data = all_birthsnakes,
               aes(x = Day_Relative, 
                 y = Plasma_Osmol_Rep_mean), 
                 color = "black",
                 method = "lm",
                 se = FALSE) +
  geom_vline(xintercept = 0, linetype = "dashed", color = "grey") +
  scale_color_manual(values = c("C" = "orange2", "W" = "royalblue4")) +
  labs(x = "Day Relative to Birthing",
       y = "Plasma Osmolality (mmol kg-1)",
       color = "Treatment") +
  scale_x_continuous(limits = c(-14, 10)) +
  scale_y_continuous(limits = c(270, 390), 
                     breaks = seq(270, 390, by = 20)) -> day_relative_parturition_all

ggsave("Osmolality Relative to Parturition All Snakes.png", 
       plot = day_relative_parturition_all, 
       width = 10, 
       height = 8)
```

##Osmolarity vs. Days in Treatment
###Birth Snakes Raw
```{r}
  mother_data_all_final_8 %>%
  filter(Gave_Birth == "Y") %>%
  ggplot() +
  geom_jitter(aes(x = Days_in_Treatment, 
                 y = Plasma_Osmol_Rep_mean, 
                 color = Hydration_Trmt), 
             size = 2, 
             alpha = 0.5) +
  annotate(geom = "text", x = 4, y = 350, label = "p < 0.001", 
           size = 5) +
  theme_classic() +
  geom_smooth(aes(x = Days_in_Treatment, 
                  y = Plasma_Osmol_Rep_mean, 
                  colour = Hydration_Trmt), 
              method = "lm", se = FALSE, 
              show.legend = TRUE, 
              size = 1) +
  scale_color_manual(values = c("C" = "orange2", "W" = "royalblue4")) +
  labs(x = "", 
       y = "Plasma Osmolality (mmol kg-1)",
       title = "Snakes that did give birth",
       color = "Treatment") +
  theme(text = element_text(color = "black",
                            size = 22),
        axis.text = element_text(color = "black", 
                                 size = 16),
        legend.text = element_text(color = "black",
                                 size = 22),
        plot.title = element_text(color = "black",
                                  size = 22),
        legend.text.align = 0,
        legend.position = "right",) +
  scale_x_continuous(breaks = c(0, 2, 4, 6, 8, 10, 12, 14, 16), limits = c(0, 16)) +
  scale_y_continuous(limits = c(270, 375), 
                     breaks = seq(270, 375, by = 20)) -> osmol_birth_v_daysintmt
```


###No Birth Snakes Raw
```{r}
    mother_data_all_final_8 %>%
  filter(Gave_Birth == "N") %>%
  ggplot() +
  geom_jitter(aes(x = Days_in_Treatment, 
                 y = Plasma_Osmol_Rep_mean, 
                 color = Hydration_Trmt), 
             size = 2, 
             alpha = 0.5) +
  annotate(geom = "text", x = 4, y = 350, label = "p < 0.001", 
           size = 5) +
  theme_classic() +
  geom_smooth(aes(x = Days_in_Treatment, 
                  y = Plasma_Osmol_Rep_mean, 
                  colour = Hydration_Trmt), 
              method = "lm", se = FALSE, 
              show.legend = TRUE, 
              size = 1) +
  labs(x = "", 
       y = "",
       title = "Snakes that did not give birth",
       color = "Treatment") +
  scale_color_manual(values = c("C" = "orange2", "W" = "royalblue4")) +
  theme(text = element_text(color = "black",
                            size = 22),
        axis.text = element_text(color = "black", 
                                 size = 16),
        legend.text = element_text(color = "black",
                                 size = 22),
        plot.title = element_text(color = "black",
                                  size = 22),
        legend.text.align = 0,
        legend.position = "right",) +
  scale_x_continuous(breaks = c(0, 2, 4, 6, 8, 10, 12, 14, 16), limits = c(0, 16)) +
  scale_y_continuous(limits = c(270, 375), 
                     breaks = seq(270, 375, by = 20)) -> osmol_no_birth_v_daysintmt
```
###Birth Snakes Change
```{r}
mother_data_all_final_8 %>%
  filter(Gave_Birth == "Y") %>%
  ggplot() +
  geom_line(aes(x = Days_in_Treatment,
                y = Change_in_osmol,
                color = Hydration_Trmt,
                group = Indiv_ID),
            alpha = 1) +
  geom_hline(yintercept = 0, linetype = 'dashed', col = 'grey') +
  labs(x = "Number of Days in Treatment",
       y = "Change in Osmolality (mmol kg-1)",
       color = "Treatment") +
  theme_classic() +
  scale_color_manual(values = c("C" = "orange2", "W" = "royalblue4")) +
  #scale_colour_brewer(palette = "RdBu") +
  theme(text = element_text(color = "black",
                            size = 22),
        axis.text = element_text(color = "black", 
                                 size = 16),
        legend.text = element_text(color = "black",
                                 size = 22),
        plot.title = element_text(color = "black",
                                  size = 22),
        legend.text.align = 0,
        legend.position = "right") +
  scale_x_continuous(breaks = c(0, 2, 4, 6, 8, 10, 12, 14, 16), limits = c(0, 16)) +
  scale_y_continuous(breaks = c(-75, -50, -25, 0, 25, 50), limits = c(-80, 55)) -> change_osmol_indiv_birthsnakes
```
###No Birth Snakes Change
```{r}
mother_data_all_final_8 %>%
  filter(Gave_Birth == "N") %>%
  ggplot() +
  geom_line(aes(x = Days_in_Treatment,
                y = Change_in_osmol,
                color = Hydration_Trmt,
                group = Indiv_ID),
            alpha = 1,
            show.legend = FALSE) +
  geom_hline(yintercept = 0, linetype = 'dashed', col = 'grey') +
  labs(x = "Number of Days in Treatment",
       y = "",
       color = "Treatment") +
  scale_color_manual(values = c("C" = "orange2", "W" = "royalblue4")) +
  theme_classic() +
  theme(text = element_text(color = "black", 
                            size = 22),
        axis.text = element_text(color = "black", 
                                 size = 16),
        legend.text = element_text(color = "black",
                                 size = 22),
        plot.title = element_text(color = "black",
                                  size = 22),
        legend.text.align = 0,
        legend.position = "right") +
  scale_x_continuous(breaks = c(0, 2, 4, 6, 8, 10, 12, 14, 16), limits = c(0, 16)) +
  scale_y_continuous(breaks = c(-75, -50, -25, 0, 25, 50), limits = c(-80, 55)) -> change_osmol_indiv_no_birthsnakes

?theme
```

####Pub figure
```{r}
ggarrange(osmol_birth_v_daysintmt, osmol_no_birth_v_daysintmt,
          change_osmol_indiv_birthsnakes, change_osmol_indiv_no_birthsnakes,
          ncol = 2, nrow = 2,
          labels = c("A", "B", "C", "D"),
          common.legend = TRUE,
          legend = "bottom"
          ) -> mother_osmol_pub_fig

ggsave("Osmolality by Treatment Mothers.png", 
       plot = mother_osmol_pub_fig, 
       width = 11, 
       height = 12)
```


##Osmolarity vs. Body Condition
###Pub Fig
```{r}
mother_data_all_final_8 %>%
  filter(Preg_Stage == "DAC") %>%
ggplot(aes(x = Body_Condition, y = Plasma_Osmol_Rep_mean)) +
  geom_point(size = 2, 
             alpha = 0.7,
             color = "springgreen3") +
  annotate(geom = "text", 
           x = -.1, 
           y = 370, 
           label = "p = 0.095", 
           size = 5) +
  theme_classic() +
  geom_smooth(aes(x = Body_Condition, y = Plasma_Osmol_Rep_mean),
              method = "lm", 
              se = TRUE, 
              show.legend = TRUE, 
              size = 1,
              color = "black") +
  labs(x = "Baseline Body Condition Index", 
       y = "Baseline Plasma Osmolality (mmol kg-1)") +
  theme(text = element_text(color = "black",
                            size = 22),
        axis.text = element_text(color = "black", 
                                 size = 16),
        legend.text = element_text(color = "black",
                                 size = 22),
        plot.title = element_text(color = "black",
                                  size = 22),
        legend.text.align = 0,
        legend.position = "right") +
  scale_x_continuous(limits = c(-0.2, 0.2), 
                     breaks = seq(-0.2, 0.2, by = 0.1)) -> body_cond_v_osmol

ggsave("Osmolality v body condition DAC.png", 
       plot = body_cond_v_osmol, 
       width = 8, 
       height = 6.5)
```
##Change in Osmol
```{r}
ggplot() +
  geom_line(data = mother_data_all_final_8,
            aes(x = Days_in_Treatment,
                y = Change_in_osmol,
                color = Hydration_Trmt,
                group = Indiv_ID),
            alpha = 1) +
  labs(title = "Change in Plasma Osmolarity Relative to Number of Days in Tmt",
       x = "Days in Treatment",
       y = "Change in Osmolarity",
       color = "Treatment") +
  scale_color_discrete(name = "Treatment", labels = c("Control", "Hydration"))
```
##Individual Figures for Osmolarity Day Relative.
```{r}
#101
ggplot() +
  geom_line(data = mother_data_all_final_3[mother_data_all_final_3$Indiv_ID == "101", ],
            aes(x = Day_Relative,
                y = Plasma_Osmol_Rep_mean), color = "cyan3") +
  geom_point(data = mother_data_all_final_3[mother_data_all_final_3$Indiv_ID == "101", ],
             aes(x = Day_Relative,
                 y = Plasma_Osmol_Rep_mean), color = "cyan3") +
  geom_vline(xintercept = 0, linetype = "dashed", color = "grey") +
  geom_vline(xintercept = -11.5, linetype = "dotted", color = "grey") +
  theme_classic() +
  scale_x_continuous(breaks = seq(from = -12, to = 0, by = 1)) +
  labs(title = "Plasma Osmolarity Relative to Day of Parturiton (Indiv. 101; Hydration)",
       subtitle = "Day of Parturiton = Day 0",
       x = "Day",
       y = "Osmolarity")
```

```{r}
#103
ggplot() +
  geom_line(data = mother_data_all_final_3[mother_data_all_final_3$Indiv_ID == "103", ],
            aes(x = Day_Relative,
                y = Plasma_Osmol_Rep_mean), color = "coral2") +
  geom_point(data = mother_data_all_final_3[mother_data_all_final_3$Indiv_ID == "103", ],
             aes(x = Day_Relative,
                 y = Plasma_Osmol_Rep_mean), color = "coral2") +
  geom_vline(xintercept = 0, linetype = "dashed", color = "grey") +
  theme_classic() +
  scale_x_continuous(breaks = seq(from = -14, to = 0, by = 1)) +
  labs(title = "Plasma Osmolarity Relative to Day of Parturiton (Indiv. 103; Control)",
       subtitle = "Day of Parturiton = Day 0",
       x = "Day",
       y = "Osmolarity")
```

```{r}
#104
ggplot() +
  geom_line(data = mother_data_all_final_3[mother_data_all_final_3$Indiv_ID == "104", ],
            aes(x = Day_Relative,
                y = Plasma_Osmol_Rep_mean), color = "cyan3") +
  geom_point(data = mother_data_all_final_3[mother_data_all_final_3$Indiv_ID == "104", ],
             aes(x = Day_Relative,
                 y = Plasma_Osmol_Rep_mean), color = "cyan3") +
  geom_vline(xintercept = 0, linetype = "dashed", color = "grey") +
  geom_vline(xintercept = -13.5, linetype = "dotted", color = "grey") +
  theme_classic() +
  scale_x_continuous(breaks = seq(from = -14, to = 0, by = 1)) +
  labs(title = "Plasma Osmolarity Relative to Day of Parturiton (Indiv. 104; Hydration)",
       subtitle = "Day of Parturiton = Day 0",
       x = "Day",
       y = "Osmolarity")
```

```{r}
#105
ggplot() +
  geom_line(data = mother_data_all_final_3[mother_data_all_final_3$Indiv_ID == "105", ],
            aes(x = Day_Relative,
                y = Plasma_Osmol_Rep_mean), color = "coral2") +
  geom_point(data = mother_data_all_final_3[mother_data_all_final_3$Indiv_ID == "105", ],
             aes(x = Day_Relative,
                 y = Plasma_Osmol_Rep_mean), color = "coral2") +
  geom_vline(xintercept = 0, linetype = "dashed", color = "grey") +
  theme_classic() +
  scale_x_continuous(breaks = seq(from = -14, to = 0, by = 1)) +
  labs(title = "Plasma Osmolarity Relative to Day of Parturiton (Indiv. 105; Control)",
       subtitle = "Day of Parturiton = Day 0",
       x = "Day",
       y = "Osmolarity")
```

```{r}
#112
ggplot() +
  geom_line(data = mother_data_all_final_3[mother_data_all_final_3$Indiv_ID == "112", ],
            aes(x = Day_Relative,
                y = Plasma_Osmol_Rep_mean), color = "cyan3") +
  geom_point(data = mother_data_all_final_3[mother_data_all_final_3$Indiv_ID == "112", ],
             aes(x = Day_Relative,
                 y = Plasma_Osmol_Rep_mean), color = "cyan3") +
  geom_vline(xintercept = 0, linetype = "dashed", color = "grey") +
  geom_vline(xintercept = -12.5, linetype = "dotted", color = "grey") +
  theme_classic() +
  scale_x_continuous(breaks = seq(from = -13, to = 0, by = 1)) +
  labs(title = "Plasma Osmolarity Relative to Day of Parturiton (Indiv. 112; Hydration)",
       subtitle = "Day of Parturiton = Day 0",
       x = "Day",
       y = "Osmolarity")
```

```{r}
#114
ggplot() +
  geom_line(data = mother_data_all_final_3[mother_data_all_final_3$Indiv_ID == "114", ],
            aes(x = Day_Relative,
                y = Plasma_Osmol_Rep_mean), color = "coral2") +
  geom_point(data = mother_data_all_final_3[mother_data_all_final_3$Indiv_ID == "114", ],
             aes(x = Day_Relative,
                 y = Plasma_Osmol_Rep_mean), color = "coral2") +
  geom_vline(xintercept = 0, linetype = "dashed", color = "grey") +
  theme_classic() +
  scale_x_continuous(breaks = seq(from = -13, to = 0, by = 1)) +
  labs(title = "Plasma Osmolarity Relative to Day of Parturiton (Indiv. 114; Control)",
       subtitle = "Day of Parturiton = Day 0",
       x = "Day",
       y = "Osmolarity")
```

```{r}
#115
ggplot() +
  geom_line(data = mother_data_all_final_3[mother_data_all_final_3$Indiv_ID == "115", ],
            aes(x = Day_Relative,
                y = Plasma_Osmol_Rep_mean), color = "coral2") +
  geom_point(data = mother_data_all_final_3[mother_data_all_final_3$Indiv_ID == "115", ],
             aes(x = Day_Relative,
                 y = Plasma_Osmol_Rep_mean), color = "coral2") +
  geom_vline(xintercept = 0, linetype = "dashed", color = "grey") +
  theme_classic() +
  scale_x_continuous(breaks = seq(from = -14, to = 0, by = 1)) +
  labs(title = "Plasma Osmolarity Relative to Day of Parturiton (Indiv. 115; Control)",
       subtitle = "Day of Parturiton = Day 0",
       x = "Day",
       y = "Osmolarity")
```

```{r}
#119
ggplot() +
  geom_line(data = mother_data_all_final_3[mother_data_all_final_3$Indiv_ID == "119", ],
            aes(x = Day_Relative,
                y = Plasma_Osmol_Rep_mean), color = "cyan3") +
  geom_point(data = mother_data_all_final_3[mother_data_all_final_3$Indiv_ID == "119", ],
             aes(x = Day_Relative,
                 y = Plasma_Osmol_Rep_mean), color = "cyan3") +
  geom_vline(xintercept = 0, linetype = "dashed", color = "grey") +
  geom_vline(xintercept = -11.5, linetype = "dotted", color = "grey") +
  theme_classic() +
  scale_x_continuous(breaks = seq(from = -12, to = 0, by = 1)) +
  labs(title = "Plasma Osmolarity Relative to Day of Parturiton (Indiv. 119; Hydration)",
       subtitle = "Day of Parturiton = Day 0",
       x = "Day",
       y = "Osmolarity")
```

```{r}
#124
ggplot() +
  geom_line(data = mother_data_all_final_3[mother_data_all_final_3$Indiv_ID == "124", ],
            aes(x = Day_Relative,
                y = Plasma_Osmol_Rep_mean), color = "cyan3") +
  geom_point(data = mother_data_all_final_3[mother_data_all_final_3$Indiv_ID == "124", ],
             aes(x = Day_Relative,
                 y = Plasma_Osmol_Rep_mean), color = "cyan3") +
  geom_vline(xintercept = 0, linetype = "dashed", color = "grey") +
  geom_vline(xintercept = -3.5, linetype = "dotted", color = "grey") +
  theme_classic() +
  scale_x_continuous(breaks = seq(from = -15, to = 0, by = 1)) +
  labs(title = "Plasma Osmolarity Relative to Day of Parturiton (Indiv. 124; Hydration)",
       subtitle = "Day of Parturiton = Day 0",
       x = "Day",
       y = "Osmolarity")
```

```{r}
#125
ggplot() +
  geom_line(data = mother_data_all_final_3[mother_data_all_final_3$Indiv_ID == "125", ],
            aes(x = Day_Relative,
                y = Plasma_Osmol_Rep_mean), color = "coral2") +
  geom_point(data = mother_data_all_final_3[mother_data_all_final_3$Indiv_ID == "125", ],
             aes(x = Day_Relative,
                 y = Plasma_Osmol_Rep_mean), color = "coral2") +
  geom_vline(xintercept = 0, linetype = "dashed", color = "grey") +
  theme_classic() +
  scale_x_continuous(breaks = seq(from = -3, to = 10, by = 1)) +
  labs(title = "Plasma Osmolarity Relative to Day of Parturiton (Indiv. 125; Control)",
       subtitle = "Day of Parturiton = Day 0",
       x = "Day",
       y = "Osmolarity")
```

```{r}
#126
ggplot() +
  geom_line(data = mother_data_all_final_3[mother_data_all_final_3$Indiv_ID == "126", ],
            aes(x = Day_Relative,
                y = Plasma_Osmol_Rep_mean), color = "cyan3") +
  geom_point(data = mother_data_all_final_3[mother_data_all_final_3$Indiv_ID == "126", ],
             aes(x = Day_Relative,
                 y = Plasma_Osmol_Rep_mean), color = "cyan3") +
  geom_vline(xintercept = 0, linetype = "dashed", color = "grey") +
  geom_vline(xintercept = -5.5, linetype = "dotted", color = "grey") +
  theme_classic() +
  scale_x_continuous(breaks = seq(from = -16, to = 1, by = 1)) +
  labs(title = "Plasma Osmolarity Relative to Day of Parturiton (Indiv. 126; Hydration)",
       subtitle = "Day of Parturiton = Day 0",
       x = "Day",
       y = "Osmolarity")
```

```{r}
#127
ggplot() +
  geom_line(data = mother_data_all_final_3[mother_data_all_final_3$Indiv_ID == "127", ],
            aes(x = Day_Relative,
                y = Plasma_Osmol_Rep_mean), color = "cyan3") +
  geom_point(data = mother_data_all_final_3[mother_data_all_final_3$Indiv_ID == "127", ],
             aes(x = Day_Relative,
                 y = Plasma_Osmol_Rep_mean), color = "cyan3") +
  geom_vline(xintercept = 0, linetype = "dashed", color = "grey") +
  geom_vline(xintercept = -7.5, linetype = "dotted", color = "grey") +
  theme_classic() +
  scale_x_continuous(breaks = seq(from = -8, to = 1, by = 1)) +
  labs(title = "Plasma Osmolarity Relative to Day of Parturiton (Indiv. 127; Hydration)",
       subtitle = "Day of Parturiton = Day 0",
       x = "Day",
       y = "Osmolarity")
```

```{r}
#128
ggplot() +
  geom_line(data = mother_data_all_final_3[mother_data_all_final_3$Indiv_ID == "128", ],
            aes(x = Day_Relative,
                y = Plasma_Osmol_Rep_mean), color = "cyan3") +
  geom_point(data = mother_data_all_final_3[mother_data_all_final_3$Indiv_ID == "128", ],
             aes(x = Day_Relative,
                 y = Plasma_Osmol_Rep_mean), color = "cyan3") +
  geom_vline(xintercept = 0, linetype = "dashed", color = "grey") +
  geom_vline(xintercept = -1.5, linetype = "dotted", color = "grey") +
  theme_classic() +
  scale_x_continuous(breaks = seq(from = -2, to = 8, by = 1)) +
  labs(title = "Plasma Osmolarity Relative to Day of Parturiton (Indiv. 128; Hydration)",
       subtitle = "Day of Parturiton = Day 0",
       x = "Day",
       y = "Osmolarity")
```

```{r}
#129
ggplot() +
  geom_line(data = mother_data_all_final_3[mother_data_all_final_3$Indiv_ID == "129", ],
            aes(x = Day_Relative,
                y = Plasma_Osmol_Rep_mean), color = "coral2") +
  geom_point(data = mother_data_all_final_3[mother_data_all_final_3$Indiv_ID == "129", ],
             aes(x = Day_Relative,
                 y = Plasma_Osmol_Rep_mean), color = "coral2") +
  geom_vline(xintercept = 0, linetype = "dashed", color = "grey") +
  theme_classic() +
  scale_x_continuous(breaks = seq(from = -2, to = 7, by = 1)) +
  labs(title = "Plasma Osmolarity Relative to Day of Parturiton (Indiv. 129; Control)",
       subtitle = "Day of Parturiton = Day 0",
       x = "Day",
       y = "Osmolarity")
```

```{r}
#131
ggplot() +
  geom_line(data = mother_data_all_final_3[mother_data_all_final_3$Indiv_ID == "131", ],
            aes(x = Day_Relative,
                y = Plasma_Osmol_Rep_mean), color = "cyan3") +
  geom_point(data = mother_data_all_final_3[mother_data_all_final_3$Indiv_ID == "131", ],
             aes(x = Day_Relative,
                 y = Plasma_Osmol_Rep_mean), color = "cyan3") +
  geom_vline(xintercept = 0, linetype = "dashed", color = "grey") +
  geom_vline(xintercept = -3.5, linetype = "dotted", color = "grey") +
  theme_classic() +
  scale_x_continuous(breaks = seq(from = -4, to = 1, by = 1)) +
  labs(title = "Plasma Osmolarity Relative to Day of Parturiton (Indiv. 131; Hydration)",
       subtitle = "Day of Parturiton = Day 0",
       x = "Day",
       y = "Osmolarity")
```

```{r}
#133
ggplot() +
  geom_line(data = mother_data_all_final_3[mother_data_all_final_3$Indiv_ID == "133", ],
            aes(x = Day_Relative,
                y = Plasma_Osmol_Rep_mean), color = "coral2") +
  geom_point(data = mother_data_all_final_3[mother_data_all_final_3$Indiv_ID == "133", ],
             aes(x = Day_Relative,
                 y = Plasma_Osmol_Rep_mean), color = "coral2") +
  geom_vline(xintercept = 0, linetype = "dashed", color = "grey") +
  theme_classic() +
  scale_x_continuous(breaks = seq(from = -4, to = 1, by = 1)) +
  labs(title = "Plasma Osmolarity Relative to Day of Parturiton (Indiv. 133; Control)",
       subtitle = "Day of Parturiton = Day 0",
       x = "Day",
       y = "Osmolarity")
```

```{r}
#134
ggplot() +
  geom_line(data = mother_data_all_final_3[mother_data_all_final_3$Indiv_ID == "134", ],
            aes(x = Day_Relative,
                y = Plasma_Osmol_Rep_mean), color = "cyan3") +
  geom_point(data = mother_data_all_final_3[mother_data_all_final_3$Indiv_ID == "134", ],
             aes(x = Day_Relative,
                 y = Plasma_Osmol_Rep_mean), color = "cyan3") +
  geom_vline(xintercept = 0, linetype = "dashed", color = "grey") +
  geom_vline(xintercept = -3.5, linetype = "dotted", color = "grey") +
  theme_classic() +
  scale_x_continuous(breaks = seq(from = -4, to = 1, by = 1)) +
  labs(title = "Plasma Osmolarity Relative to Day of Parturiton (Indiv. 134; Hydration)",
       subtitle = "Day of Parturiton = Day 0",
       x = "Day",
       y = "Osmolarity")
```

```{r}
#135
ggplot() +
  geom_line(data = mother_data_all_final_3[mother_data_all_final_3$Indiv_ID == "135", ],
            aes(x = Day_Relative,
                y = Plasma_Osmol_Rep_mean), color = "coral2") +
  geom_point(data = mother_data_all_final_3[mother_data_all_final_3$Indiv_ID == "135", ],
             aes(x = Day_Relative,
                 y = Plasma_Osmol_Rep_mean), color = "coral2") +
  geom_vline(xintercept = 0, linetype = "dashed", color = "grey") +
  theme_classic() +
  scale_x_continuous(breaks = seq(from = -1, to = 8, by = 1)) +
  labs(title = "Plasma Osmolarity Relative to Day of Parturiton (Indiv. 135; Control)",
       subtitle = "Day of Parturiton = Day 0",
       x = "Day",
       y = "Osmolarity")
```

#Plotting CEWL Raw Data

##CEWL vs. SVL
```{r}
  ggplot(data = mother_data_all_final_8, aes(x = SVL_cm, y = CEWL_g_m2h, colour = Hydration_Trmt)) +
  geom_point() +
  theme_classic() +
  geom_smooth(method = "lm", se = FALSE) +
  labs(x = "SVL (cm)", y = "CEWL (g/m2h)")
```
##CEWL vs. Mass
```{r}
  ggplot(data = mother_data_all_final_8, aes(x = Mass_g, y = CEWL_g_m2h, colour = Hydration_Trmt)) +
  geom_point() +
  theme_classic() +
  geom_smooth(method = "lm", se = FALSE) +
  labs(x = "Mass (g)", y = "CEWL (g/m2h)")
```
##CEWL vs. Shed Stage
```{r}
  ggplot(data = mother_data_all_final_8, aes(x = Shed_Stage, y = CEWL_g_m2h, colour = Hydration_Trmt)) +
  geom_point() +
  geom_boxplot() +
  theme_classic() +
  geom_smooth(method = "lm", se = FALSE) +
  labs(x = "Shed Stage", y = "CEWL (g/m2h)")
```
##CEWL vs. Clocal Temp
```{r}
  ggplot(data = mother_data_all_final_8, aes(x = calibrated_cloacal_temp, y = CEWL_g_m2h, colour = Hydration_Trmt)) +
  geom_point() +
  theme_classic() +
  geom_smooth(method = "lm", se = FALSE) +
  labs(x = "Body Temp (C)", y = "CEWL (g/m2h)")
```
##CEWL vs. Sample Collect Date
```{r}
ggplot(data = mother_data_all_final_8, aes(x = CEWL_Blood_Collect_Date, y = CEWL_g_m2h, colour = Hydration_Trmt)) +
  geom_point() +
  theme_classic() +
  geom_smooth(method = "lm", se = FALSE) +
  labs(x = "Sample Collection Date", y = "CEWL")
```
##CEWL vs. Rookery Capture ID
This only includes the measurements for the day after capture. 
```{r}
filter(mother_data_all_final_8, Preg_Stage == "DAC") %>%
  ggplot(aes(x = Rookery_Capture_ID, y = CEWL_g_m2h)) +
  geom_boxplot() +
  theme_classic() +
  labs(x = "Rookery Capture Location", y = "CEWL")
```
##CEWL vs. Hydration Treatment
This includes the initial measurements before the treatments began and after.
```{r}
  ggplot(data = mother_data_all_final_8, aes(x = Hydration_Trmt, y = CEWL_g_m2h, fill = Hydration_Trmt)) +
  geom_boxplot() +
  theme_classic() +
  labs(x = "Hydration Treatment", y = "CEWL")
```
This does not include the initial measurements so is only the measurements after the hydration treatment began
```{r}
filter(mother_data_all_final_8, Preg_Stage != "DAC") %>%
  ggplot(aes(x = Hydration_Trmt, y = CEWL_g_m2h)) +
  geom_boxplot() +
  theme_classic() +
  labs(x = "Hydration Treatment", y = "CEWL After Treatment began")
```
##CEWL vs Osmolarity
```{r}
  ggplot(data = mother_data_all_final_8, aes(x = Plasma_Osmol_Rep_mean, y = CEWL_g_m2h, colour = Hydration_Trmt)) +
  geom_point() +
  theme_classic() +
  geom_smooth(method = "lm", se = FALSE) +
  labs(x = "Plasma Osmolarity (mmol/kg)", y = "CEWL")
```
##CEWL vs. Ambient Temp
###Pub fig
```{r}
ggplot(data = mother_data_all_final_8, aes(x = msmt_temp_C, y = CEWL_g_m2h)) +
  geom_point(size = 2, 
             alpha = 0.7,
             color = "springgreen3") +
  annotate(geom = "text", 
           x = 26.5, 
           y = 10, 
           label = "p < 0.0001", 
           size = 5) +
  theme_classic() +
  geom_smooth(aes(x = msmt_temp_C, y = CEWL_g_m2h),
              method = "lm", 
              se = TRUE, 
              show.legend = TRUE, 
              size = 1,
              color = "black") +
  labs(x = "Ambient Temperature (°C)", 
       y = "CEWL (g m2h-1)") +
  theme(text = element_text(color = "black",
                            size = 22),
        axis.text = element_text(color = "black", 
                                 size = 16),
        legend.text = element_text(color = "black",
                                 size = 22),
        plot.title = element_text(color = "black",
                                  size = 22),
        legend.text.align = 0,
        legend.position = "right") +
  #scale_x_continuous(breaks = c(0, 2, 4, 6, 8, 10, 12, 14, 16), limits = c(0, 16)) +
 scale_y_continuous(limits = c(9, 30.5),
                  breaks = seq(9, 30.5, by = 3)) -> temp_v_cewl_females

```
##CEWL vs. Ambient Humidity
###Pub fig
```{r}

ggplot(data = mother_data_all_final_8, aes(x = msmt_RH_percent, y = CEWL_g_m2h)) +
  geom_point(size = 2, 
             alpha = 0.7, 
             color = "springgreen3") +
  annotate(geom = "text", 
           x = 44, 
           y = 10, 
           label = "p < 0.0001", 
           size = 5) +
  theme_classic() +
  geom_smooth(aes(x = msmt_RH_percent, y = CEWL_g_m2h),
              method = "lm", 
              se = TRUE, 
              show.legend = TRUE, 
              size = 1,
              color = "black") +
  labs(x = "Ambient Humidity (%)", 
       y = "") +
  theme(text = element_text(color = "black",
                            size = 22),
        axis.text = element_text(color = "black", 
                                 size = 16),
        legend.text = element_text(color = "black",
                                 size = 22),
        plot.title = element_text(color = "black",
                                  size = 22),
        legend.text.align = 0,
        legend.position = "right") +
scale_x_continuous(breaks = c(34, 36, 38, 40, 42, 44, 46, 48), limits = c(34, 48)) +
 scale_y_continuous(limits = c(9, 30.5),
                  breaks = seq(9, 30.5, by = 3)) -> humidity_v_cewl_females

```

```{r}
ggarrange(temp_v_cewl_females, humidity_v_cewl_females,
          ncol = 2, nrow = 1,
          labels = c("A", "B"),
          common.legend = TRUE,
          legend = "bottom"
          ) -> CEWL_v_temp_humidity_mothers

ggsave("CEWL vs Temp and Humidity Females.png", 
       plot = CEWL_v_temp_humidity_mothers, 
       width = 10, 
       height = 4)
```


##CEWL vs. Day Relative to the Day of Birth
```{r}
mother_data_all_final_8 %>%
  filter(Gave_Birth == "Y") %>%
  ggplot(aes(x = Day_Relative, y = CEWL_g_m2h)) +
  geom_point() +
  theme_classic() +
  geom_smooth(method = "lm", se = FALSE) +
  labs(x = "Day Relative to the Day of Birth", y = "CEWL")
```
##CEWL vs. Days in Treatment
```{r}
  ggplot(data = mother_data_all_final_8, aes(x = Days_in_Treatment, y = CEWL_g_m2h, colour = Hydration_Trmt)) +
  geom_point() +
  theme_classic() +
  geom_smooth(method = "lm", se = FALSE) +
  labs(x = "Number of Days in Treatment", y = "CEWL")
```
##CEWL vs. Body Condition
```{r}
  ggplot(data = mother_data_all_final_8, aes(x = Body_Condition, y = CEWL_g_m2h)) +
  geom_point() +
  theme_classic() +
  geom_smooth(method = "lm", se = FALSE) +
  labs(x = "Body Condition", y = "CEWL")
```
##Change in CEWL
```{r}
ggplot() +
  geom_line(data = mother_data_all_final_6,
            aes(x = Days_in_Treatment,
                y = Change_in_CEWL,
                color = Hydration_Trmt,
                group = Indiv_ID),
            alpha = 1) +
  labs(title = "Change in CEWL Relative to Number of Days in Treatment",
       x = "Days in Treatment",
       y = "Change in CEWL",
       color = "Treatment") +
  scale_color_discrete(name = "Treatment", labels = c("Control", "Hydration"))
```
##Individual Figures for CEWL
```{r}
#101
ggplot() +
  geom_line(data = mother_data_all_final_3[mother_data_all_final_3$Indiv_ID == "101", ],
            aes(x = Day_Relative,
                y = CEWL_g_m2h), color = "cyan3") +
  geom_point(data = mother_data_all_final_3[mother_data_all_final_3$Indiv_ID == "101", ],
             aes(x = Day_Relative,
                 y = CEWL_g_m2h), color = "cyan3") +
  geom_vline(xintercept = 0, linetype = "dashed", color = "grey") +
  geom_vline(xintercept = -11.5, linetype = "dotted", color = "grey") +
  theme_classic() +
  scale_x_continuous(breaks = seq(from = -12, to = 0, by = 1)) +
  labs(title = "CEWL Relative to Day of Parturiton (Indiv. 101; Hydration)",
       subtitle = "Day of Parturiton = Day 0",
       x = "Day",
       y = "CEWL")
```

```{r}
#103
ggplot() +
  geom_line(data = mother_data_all_final_3[mother_data_all_final_3$Indiv_ID == "103", ],
            aes(x = Day_Relative,
                y = CEWL_g_m2h), color = "coral2") +
  geom_point(data = mother_data_all_final_3[mother_data_all_final_3$Indiv_ID == "103", ],
             aes(x = Day_Relative,
                 y = CEWL_g_m2h), color = "coral2") +
  geom_vline(xintercept = 0, linetype = "dashed", color = "grey") +
  theme_classic() +
  scale_x_continuous(breaks = seq(from = -14, to = 0, by = 1)) +
  labs(title = "CEWL Relative to Day of Parturiton (Indiv. 103; Control)",
       subtitle = "Day of Parturiton = Day 0",
       x = "Day",
       y = "CEWL")
```

```{r}
#104
ggplot() +
  geom_line(data = mother_data_all_final_3[mother_data_all_final_3$Indiv_ID == "104", ],
            aes(x = Day_Relative,
                y = CEWL_g_m2h), color = "cyan3") +
  geom_point(data = mother_data_all_final_3[mother_data_all_final_3$Indiv_ID == "104", ],
             aes(x = Day_Relative,
                 y = CEWL_g_m2h), color = "cyan3") +
  geom_vline(xintercept = 0, linetype = "dashed", color = "grey") +
  geom_vline(xintercept = -13.5, linetype = "dotted", color = "grey") +
  theme_classic() +
  scale_x_continuous(breaks = seq(from = -14, to = 0, by = 1)) +
  labs(title = "CEWL Relative to Day of Parturiton (Indiv. 104; Hydration)",
       subtitle = "Day of Parturiton = Day 0",
       x = "Day",
       y = "CEWL")
```

```{r}
#105
ggplot() +
  geom_line(data = mother_data_all_final_3[mother_data_all_final_3$Indiv_ID == "105", ],
            aes(x = Day_Relative,
                y = CEWL_g_m2h), color = "coral2") +
  geom_point(data = mother_data_all_final_3[mother_data_all_final_3$Indiv_ID == "105", ],
             aes(x = Day_Relative,
                 y = CEWL_g_m2h), color = "coral2") +
  geom_vline(xintercept = 0, linetype = "dashed", color = "grey") +
  theme_classic() +
  scale_x_continuous(breaks = seq(from = -14, to = 0, by = 1)) +
  labs(title = "CEWL Relative to Day of Parturiton (Indiv. 105; Control)",
       subtitle = "Day of Parturiton = Day 0",
       x = "Day",
       y = "CEWL")
```

```{r}
#112
ggplot() +
  geom_line(data = mother_data_all_final_3[mother_data_all_final_3$Indiv_ID == "112", ],
            aes(x = Day_Relative,
                y = CEWL_g_m2h), color = "cyan3") +
  geom_point(data = mother_data_all_final_3[mother_data_all_final_3$Indiv_ID == "112", ],
             aes(x = Day_Relative,
                 y = CEWL_g_m2h), color = "cyan3") +
  geom_vline(xintercept = 0, linetype = "dashed", color = "grey") +
  geom_vline(xintercept = -12.5, linetype = "dotted", color = "grey") +
  theme_classic() +
  scale_x_continuous(breaks = seq(from = -13, to = 0, by = 1)) +
  labs(title = "CEWL Relative to Day of Parturiton (Indiv. 112; Hydration)",
       subtitle = "Day of Parturiton = Day 0",
       x = "Day",
       y = "CEWL")
```

```{r}
#114
ggplot() +
  geom_line(data = mother_data_all_final_3[mother_data_all_final_3$Indiv_ID == "114", ],
            aes(x = Day_Relative,
                y = CEWL_g_m2h), color = "coral2") +
  geom_point(data = mother_data_all_final_3[mother_data_all_final_3$Indiv_ID == "114", ],
             aes(x = Day_Relative,
                 y = CEWL_g_m2h), color = "coral2") +
  geom_vline(xintercept = 0, linetype = "dashed", color = "grey") +
  theme_classic() +
  scale_x_continuous(breaks = seq(from = -13, to = 0, by = 1)) +
  labs(title = "CEWL Relative to Day of Parturiton (Indiv. 114; Control)",
       subtitle = "Day of Parturiton = Day 0",
       x = "Day",
       y = "CEWL")
```

```{r}
#115
ggplot() +
  geom_line(data = mother_data_all_final_3[mother_data_all_final_3$Indiv_ID == "115", ],
            aes(x = Day_Relative,
                y = CEWL_g_m2h), color = "coral2") +
  geom_point(data = mother_data_all_final_3[mother_data_all_final_3$Indiv_ID == "115", ],
             aes(x = Day_Relative,
                 y = CEWL_g_m2h), color = "coral2") +
  geom_vline(xintercept = 0, linetype = "dashed", color = "grey") +
  theme_classic() +
  scale_x_continuous(breaks = seq(from = -14, to = 0, by = 1)) +
  labs(title = "CEWL Relative to Day of Parturiton (Indiv. 115; Control)",
       subtitle = "Day of Parturiton = Day 0",
       x = "Day",
       y = "CEWL")
```

```{r}
#119
ggplot() +
  geom_line(data = mother_data_all_final_3[mother_data_all_final_3$Indiv_ID == "119", ],
            aes(x = Day_Relative,
                y = CEWL_g_m2h), color = "cyan3") +
  geom_point(data = mother_data_all_final_3[mother_data_all_final_3$Indiv_ID == "119", ],
             aes(x = Day_Relative,
                 y = CEWL_g_m2h), color = "cyan3") +
  geom_vline(xintercept = 0, linetype = "dashed", color = "grey") +
  geom_vline(xintercept = -11.5, linetype = "dotted", color = "grey") +
  theme_classic() +
  scale_x_continuous(breaks = seq(from = -12, to = 0, by = 1)) +
  labs(title = "CEWL Relative to Day of Parturiton (Indiv. 119; Hydration)",
       subtitle = "Day of Parturiton = Day 0",
       x = "Day",
       y = "CEWL")
```

```{r}
#124
ggplot() +
  geom_line(data = mother_data_all_final_3[mother_data_all_final_3$Indiv_ID == "124", ],
            aes(x = Day_Relative,
                y = CEWL_g_m2h), color = "cyan3") +
  geom_point(data = mother_data_all_final_3[mother_data_all_final_3$Indiv_ID == "124", ],
             aes(x = Day_Relative,
                 y = CEWL_g_m2h), color = "cyan3") +
  geom_vline(xintercept = 0, linetype = "dashed", color = "grey") +
  geom_vline(xintercept = -3.5, linetype = "dotted", color = "grey") +
  theme_classic() +
  scale_x_continuous(breaks = seq(from = -15, to = 0, by = 1)) +
  labs(title = "CEWL Relative to Day of Parturiton (Indiv. 124; Hydration)",
       subtitle = "Day of Parturiton = Day 0",
       x = "Day",
       y = "CEWL")
```

```{r}
#125
ggplot() +
  geom_line(data = mother_data_all_final_3[mother_data_all_final_3$Indiv_ID == "125", ],
            aes(x = Day_Relative,
                y = CEWL_g_m2h), color = "coral2") +
  geom_point(data = mother_data_all_final_3[mother_data_all_final_3$Indiv_ID == "125", ],
             aes(x = Day_Relative,
                 y = CEWL_g_m2h), color = "coral2") +
  geom_vline(xintercept = 0, linetype = "dashed", color = "grey") +
  theme_classic() +
  scale_x_continuous(breaks = seq(from = -3, to = 10, by = 1)) +
  labs(title = "CEWL Relative to Day of Parturiton (Indiv. 125; Control)",
       subtitle = "Day of Parturiton = Day 0",
       x = "Day",
       y = "CEWL")
```

```{r}
#126
ggplot() +
  geom_line(data = mother_data_all_final_3[mother_data_all_final_3$Indiv_ID == "126", ],
            aes(x = Day_Relative,
                y = CEWL_g_m2h), color = "cyan3") +
  geom_point(data = mother_data_all_final_3[mother_data_all_final_3$Indiv_ID == "126", ],
             aes(x = Day_Relative,
                 y = CEWL_g_m2h), color = "cyan3") +
  geom_vline(xintercept = 0, linetype = "dashed", color = "grey") +
  geom_vline(xintercept = -5.5, linetype = "dotted", color = "grey") +
  theme_classic() +
  scale_x_continuous(breaks = seq(from = -16, to = 1, by = 1)) +
  labs(title = "CEWL Relative to Day of Parturiton (Indiv. 126; Hydration)",
       subtitle = "Day of Parturiton = Day 0",
       x = "Day",
       y = "CEWL")
```

```{r}
#127
ggplot() +
  geom_line(data = mother_data_all_final_3[mother_data_all_final_3$Indiv_ID == "127", ],
            aes(x = Day_Relative,
                y = CEWL_g_m2h), color = "cyan3") +
  geom_point(data = mother_data_all_final_3[mother_data_all_final_3$Indiv_ID == "127", ],
             aes(x = Day_Relative,
                 y = CEWL_g_m2h), color = "cyan3") +
  geom_vline(xintercept = 0, linetype = "dashed", color = "grey") +
  geom_vline(xintercept = -7.5, linetype = "dotted", color = "grey") +
  theme_classic() +
  scale_x_continuous(breaks = seq(from = -8, to = 1, by = 1)) +
  labs(title = "CEWL Relative to Day of Parturiton (Indiv. 127; Hydration)",
       subtitle = "Day of Parturiton = Day 0",
       x = "Day",
       y = "CEWL")
```

```{r}
#128
ggplot() +
  geom_line(data = mother_data_all_final_3[mother_data_all_final_3$Indiv_ID == "128", ],
            aes(x = Day_Relative,
                y = CEWL_g_m2h), color = "cyan3") +
  geom_point(data = mother_data_all_final_3[mother_data_all_final_3$Indiv_ID == "128", ],
             aes(x = Day_Relative,
                 y = CEWL_g_m2h), color = "cyan3") +
  geom_vline(xintercept = 0, linetype = "dashed", color = "grey") +
  geom_vline(xintercept = -1.5, linetype = "dotted", color = "grey") +
  theme_classic() +
  scale_x_continuous(breaks = seq(from = -2, to = 8, by = 1)) +
  labs(title = "CEWL Relative to Day of Parturiton (Indiv. 128; Hydration)",
       subtitle = "Day of Parturiton = Day 0",
       x = "Day",
       y = "CEWL")
```

```{r}
#129
ggplot() +
  geom_line(data = mother_data_all_final_3[mother_data_all_final_3$Indiv_ID == "129", ],
            aes(x = Day_Relative,
                y = CEWL_g_m2h), color = "coral2") +
  geom_point(data = mother_data_all_final_3[mother_data_all_final_3$Indiv_ID == "129", ],
             aes(x = Day_Relative,
                 y = CEWL_g_m2h), color = "coral2") +
  geom_vline(xintercept = 0, linetype = "dashed", color = "grey") +
  theme_classic() +
  scale_x_continuous(breaks = seq(from = -2, to = 7, by = 1)) +
  labs(title = "CEWL Relative to Day of Parturiton (Indiv. 129; Control)",
       subtitle = "Day of Parturiton = Day 0",
       x = "Day",
       y = "CEWL")
```

```{r}
#131
ggplot() +
  geom_line(data = mother_data_all_final_3[mother_data_all_final_3$Indiv_ID == "131", ],
            aes(x = Day_Relative,
                y = CEWL_g_m2h), color = "cyan3") +
  geom_point(data = mother_data_all_final_3[mother_data_all_final_3$Indiv_ID == "131", ],
             aes(x = Day_Relative,
                 y = CEWL_g_m2h), color = "cyan3") +
  geom_vline(xintercept = 0, linetype = "dashed", color = "grey") +
  geom_vline(xintercept = -3.5, linetype = "dotted", color = "grey") +
  theme_classic() +
  scale_x_continuous(breaks = seq(from = -4, to = 1, by = 1)) +
  labs(title = "CEWL Relative to Day of Parturiton (Indiv. 131; Hydration)",
       subtitle = "Day of Parturiton = Day 0",
       x = "Day",
       y = "CEWL")
```

```{r}
#133
ggplot() +
  geom_line(data = mother_data_all_final_3[mother_data_all_final_3$Indiv_ID == "133", ],
            aes(x = Day_Relative,
                y = CEWL_g_m2h), color = "coral2") +
  geom_point(data = mother_data_all_final_3[mother_data_all_final_3$Indiv_ID == "133", ],
             aes(x = Day_Relative,
                 y = CEWL_g_m2h), color = "coral2") +
  geom_vline(xintercept = 0, linetype = "dashed", color = "grey") +
  theme_classic() +
  scale_x_continuous(breaks = seq(from = -4, to = 1, by = 1)) +
  labs(title = "CEWL Relative to Day of Parturiton (Indiv. 133; Control)",
       subtitle = "Day of Parturiton = Day 0",
       x = "Day",
       y = "CEWL")
```

```{r}
#134
ggplot() +
  geom_line(data = mother_data_all_final_3[mother_data_all_final_3$Indiv_ID == "134", ],
            aes(x = Day_Relative,
                y = CEWL_g_m2h), color = "cyan3") +
  geom_point(data = mother_data_all_final_3[mother_data_all_final_3$Indiv_ID == "134", ],
             aes(x = Day_Relative,
                 y = CEWL_g_m2h), color = "cyan3") +
  geom_vline(xintercept = 0, linetype = "dashed", color = "grey") +
  geom_vline(xintercept = -3.5, linetype = "dotted", color = "grey") +
  theme_classic() +
  scale_x_continuous(breaks = seq(from = -4, to = 1, by = 1)) +
  labs(title = "CEWL Relative to Day of Parturiton (Indiv. 134; Hydration)",
       subtitle = "Day of Parturiton = Day 0",
       x = "Day",
       y = "CEWL")
```

```{r}
#135
ggplot() +
  geom_line(data = mother_data_all_final_3[mother_data_all_final_3$Indiv_ID == "135", ],
            aes(x = Day_Relative,
                y = CEWL_g_m2h), color = "coral2") +
  geom_point(data = mother_data_all_final_3[mother_data_all_final_3$Indiv_ID == "135", ],
             aes(x = Day_Relative,
                 y = CEWL_g_m2h), color = "coral2") +
  geom_vline(xintercept = 0, linetype = "dashed", color = "grey") +
  theme_classic() +
  scale_x_continuous(breaks = seq(from = -1, to = 8, by = 1)) +
  labs(title = "CEWL Relative to Day of Parturiton (Indiv. 135; Control)",
       subtitle = "Day of Parturiton = Day 0",
       x = "Day",
       y = "CEWL")
```


#Correlation Plot
Making a correlation plot to see which numerical variables are related to one another in this data set.

First, selecting out all of the numerical variables since correlation plots are based on numerical variables only.
```{r}
summary(mother_data_all_final_8)

correl_df <- mother_data_all_final_8 %>%
  mutate(Indiv_ID = as.numeric(Indiv_ID)) %>%
  ungroup() %>%
  dplyr::select(Plasma_Osmol_Rep_mean, SVL_cm, Mass_g, calibrated_cloacal_temp, CEWL_g_m2h, msmt_temp_C, msmt_RH_percent, Body_Condition, Day_Relative, Days_in_Treatment, Change_in_osmol, Change_in_CEWL)
```

Making the correlation chart
```{r}
chart.Correlation(correl_df, histogram=TRUE, pch=19)
```

#CEWL Models

##Categorical Variable Relationships
First, I have to find which categorical variables are related to CEWL.
```{r}
summary(mother_data_all_final_8)

#Shed stage 
summary(lm(CEWL_g_m2h ~ Shed_Stage, data = mother_data_all_final_8))
#not correlated, no need to include in model

#Preg_Stage
TukeyHSD(aov(CEWL_g_m2h ~ Preg_Stage, data = mother_data_all_final_8))
#Some differences, but this variable isnt biologically relavent. I really don't need it anyore. Doesn't accurately represent preg stage.

#Sample collect dater
TukeyHSD(aov(CEWL_g_m2h ~ as.factor(CEWL_Blood_Collect_Date), mother_data_all_final_8))
#Some difference. I'll include it but I think it is going to cause issues. 

#Rookery capture ID
TukeyHSD(aov(CEWL_g_m2h ~ Rookery_Capture_ID, data = mother_data_all_final_8))
#No differences, no need to include in the model

#Hydration treatment
summary(lm(CEWL_g_m2h ~ Hydration_Trmt, data = mother_data_all_final_8))
TukeyHSD(aov(CEWL_g_m2h ~ Hydration_Trmt, data = mother_data_all_final_8))
#Initial lm, no difference between hydration groups but I will still keep it in the model because this is what we are primarily interested in. Likely differences with interactions. 

#Date of parturition
TukeyHSD(aov(CEWL_g_m2h ~ as.factor(Date_Parturition), mother_data_all_final_8))
#No differences between the dates of parturition, wont include in model.

#If they gave birth or not
summary(lm(CEWL_g_m2h ~ Gave_Birth, data = mother_data_all_final_8))
#no difference, wont include in the model
```
Overall, the categorial variables that I will include in the model are collect date and hydration treatment.

##Numerical Variable Relationships

Based on the correlation plot, the numerical variables that I initially want to include in the full model for CEWL are calibrated body temp, ambient temp, ambient humidity, day relative to birth, and days in treatment

Overall, all of the variables that I will include in the initial model are calibrated body temp, ambient temp, ambient humidity, day relative to birth, days in treatment, hydration treatment, and sample collect date. I will also include the interactions that I think may be relevant. 

Since day relative is important, I will also have to make two separate models for the snakes that gave birth and the snakes that didn't. If, in the end, the best model for the snakes that did give birth doesn't include the day relative, then I can put all snakes in the same model. If not, separate. 

First, making a dataframe with the snakes that did give birth. 
```{r}
birth_snakes <- mother_data_all_final_8 %>%
  filter(Gave_Birth == "Y")

birth_snakes <- birth_snakes[-c(24,25,26), ]
```

Now, a dataframe with the snakes that did not give birth
```{r}
no_birth_snakes <- mother_data_all_final_8 %>%
  filter(Gave_Birth == "N")
```

##Baseline Model
First, I need a dataframe with only the baseline measurements. 
```{r}
mothers_baseline <- mother_data_all_final_8 %>%
  filter(Preg_Stage == "DAC")
```

#SAVANNAH: OLD BASELINE CEWL MODEL
Now creating an initial model with all variables that may impact baseline CEWL so mass, SVL, body condition, body temperature at the time of measurement, ambient temperature, and ambient humidity, treatment. Also seeing if capture date and indiv ID are a random effect.

```{r}
baseline_cewl_1 <- lme4::lmer(data = mothers_baseline,
                      CEWL_g_m2h ~
                        calibrated_cloacal_temp +
                        msmt_temp_C +
                        msmt_RH_percent +
                        Mass_g +
                        SVL_cm +
                        Body_Condition +
                        (1|CEWL_Blood_Collect_Date))
                    
car::vif(baseline_cewl_1)
summary(baseline_cewl_1)
drop1(baseline_cewl_1)
anova(baseline_cewl_1)
```
due to multicolinearity, I will first remove mass and svl and keep body condition. 
```{r}
baseline_cewl_2 <- lme4::lmer(data = mothers_baseline,
                      CEWL_g_m2h ~
                        calibrated_cloacal_temp +
                        msmt_temp_C +
                        msmt_RH_percent +
                        Body_Condition +
                        (1|CEWL_Blood_Collect_Date))
                    

summary(baseline_cewl_2)
drop1(baseline_cewl_2)
anova(baseline_cewl_2)
```
Next, drop body condition. 
```{r}
baseline_cewl_3 <- lme4::lmer(data = mothers_baseline,
                      CEWL_g_m2h ~
                        calibrated_cloacal_temp +
                        msmt_temp_C +
                        msmt_RH_percent +
                        (1|CEWL_Blood_Collect_Date))
                    

summary(baseline_cewl_3)
drop1(baseline_cewl_3)
anova(baseline_cewl_3)
```
next drop cloacal temp
```{r}
baseline_cewl_4 <- lme4::lmer(data = mothers_baseline,
                      CEWL_g_m2h ~
                        msmt_temp_C +
                        msmt_RH_percent +
                        (1|CEWL_Blood_Collect_Date))
                    

summary(baseline_cewl_4)
drop1(baseline_cewl_4)
anova(baseline_cewl_4)
```
next drop ambient temp
```{r}
baseline_cewl_5 <- lme4::lmer(data = mothers_baseline,
                      CEWL_g_m2h ~
                        msmt_RH_percent +
                        (1|CEWL_Blood_Collect_Date))
                    

summary(baseline_cewl_5)
drop1(baseline_cewl_5)
anova(baseline_cewl_5)
```
null model
```{r}
baseline_cewl_null <- lme4::lmer(data = mothers_baseline,
                      CEWL_g_m2h ~
                        (1|CEWL_Blood_Collect_Date))
                    

summary(baseline_cewl_null)
drop1(baseline_cewl_null)
anova(baseline_cewl_null)
```

###Model selection
```{r CEWL mod compare}
baseline_cewl_mods <- list(baseline_cewl_2, baseline_cewl_3, baseline_cewl_4, baseline_cewl_5, baseline_cewl_null)

#specify model names
baeline_cewl_mod_names_all <- c('model2', 
                    'model3',
                    'model4',
                    'model6',
                    'modelnull')

#calculate AIC of each model
cewl_AICc_all <- data.frame(aictab(cand.set = baseline_cewl_mods, 
                                 modnames = baeline_cewl_mod_names_all))
cewl_AICc_all
```
Best model was 4 which included:
```{r}
baseline_final_mod <- lmerTest::lmer(data = mothers_baseline,
                      CEWL_g_m2h ~
                        msmt_temp_C +
                        msmt_RH_percent +
                        (1|CEWL_Blood_Collect_Date))

summary(baseline_final_mod)
anova(baseline_final_mod)
```
Result: Baseline CEWL was best explained by ambient conditions including humidity (lmm: estimate = 1.05, SE = 0.33, F(1, 24.07) = 10.34, p = 0.0037) and temperature (lmm: estimate = 4.39, SE = 1.1, F(1, 24.2) = 15.86, p = 0.00054)

Getting CI
```{r}
cewl_tmt_DAC_lm <- lm(data = mothers_baseline, CEWL_g_m2h ~ Hydration_Trmt)
mom_baseline_cewl_CI <- data.frame(emmeans(cewl_tmt_DAC_lm, "Hydration_Trmt"))
```


####Pub Fig
```{r}
ggplot() +
  geom_jitter(data = mothers_baseline, 
             aes(x = Hydration_Trmt, 
                 y = CEWL_g_m2h, 
                 color = Hydration_Trmt),
             size = 2,
             alpha = 0.5,
             show.legend = TRUE) +
  geom_point(data = mom_baseline_cewl_CI, 
             aes(x = Hydration_Trmt, 
                 y = emmean),
             color = "black", 
             size = 3) +
  theme_classic() +
  annotate(geom = "text", x = 1.6, y = 10, label = "p = 0.30", 
           size = 5) +
  scale_color_manual(values = c("C" = "orange2", "W" = "dodgerblue")) +
  labs(x = "", y = "CEWL (g m2h-1)") +
  geom_errorbar(data = mom_baseline_cewl_CI, aes(x = Hydration_Trmt,
                               y = emmean, 
                               ymin = lower.CL, 
                               ymax = upper.CL,
                               width = .3),
                color = "black") +
  theme(text = element_text(color = "black", 
                            size = 22),
        axis.text = element_text(color = "black", 
                                 size = 16)) +
scale_y_continuous(limits = c(8, 30.5), breaks = seq(8, 31, by = 2)) -> baseline_cewl_fig
```
###Post Treatment Model
```{r}
not_dac_or_1wab <- mother_data_all_final_8 %>%
  filter(Preg_Stage != "DAC") %>%
  filter(Preg_Stage != "1WAB") %>%
  filter(Preg_Stage != "2WAC")

df_1wac <- mother_data_all_final_8 %>%
  filter(Preg_Stage == "1WAC")

df_dab <- mother_data_all_final_8 %>%
  filter(Preg_Stage == "DAB")

dab_no_dac <- df_dab[c(9, 10, 11, 13, 14, 15, 16, 17, 18), ]

post_tmt_df <- full_join(df_1wac, dab_no_dac)
```
#SAVANNAH: OLD POST TREATMENT CEWL MODEL
 post treatment linear model to see the effect of treatment on cewl. This has one measurement per individual. For most individuals it is their one week after capture measuremeant. If the snake gave birth prior to that one week timeframe, this is their post birth osmolality.
```{r}
post_tmt_cewl_lm <- lm(data = post_tmt_df, CEWL_g_m2h ~ Hydration_Trmt)

summary(post_tmt_cewl_lm)
anova(post_tmt_cewl_lm)
```
Getting confidence intervals for figure. 
```{r}
CI_mom_CEWL <- data.frame(emmeans(post_tmt_cewl_lm, "Hydration_Trmt"))
```

#####Pub Figure
```{r}
ggplot() +
  geom_jitter(data = post_tmt_df, 
             aes(x = Hydration_Trmt, 
                 y = CEWL_g_m2h, 
                 color = Hydration_Trmt),
             size = 2,
             alpha = 0.5,
             show.legend = TRUE) +
  geom_point(data = CI_mom_CEWL, 
             aes(x = Hydration_Trmt, 
                 y = emmean),
             color = "black", 
             size = 2) +
  theme_classic() +
  annotate(geom = "text", x = 1.3, y = 30, label = "p = 0.58", 
           size = 5) +
  scale_color_manual(values = c("C" = "orange2", "W" = "dodgerblue")) +
  labs(x = "", y = "") +
  geom_errorbar(data = CI_mom_CEWL, aes(x = Hydration_Trmt,
                               y = emmean, 
                               ymin = lower.CL, 
                               ymax = upper.CL,
                               width = .3),
                color = "black")+
  theme(text = element_text(color = "black", 
                            size = 22),
        axis.text = element_text(color = "black", 
                                 size = 16)) +
  scale_y_continuous(limits = c(8, 30.5), breaks = seq(8, 31, by = 2)) -> cewl_posttmt_mothers

ggsave("Mother CEWL v Treatment Experimental.png", 
       plot = cewl_v_tmt_mothers,
       width = 4,
       height = 4)

```


##Initial Models (Experimental)
Is there a difference in cewl between the treatment group and the control group the day after capture? 
```{r}
DAC_cewl <- mother_data_all_final_8 %>%
  dplyr::filter(Preg_Stage == "DAC")

DAC_cewl_lm <- lm(CEWL_g_m2h ~ Hydration_Trmt, data = DAC_cewl)

summary(DAC_cewl_lm)
anova(DAC_cewl_lm)

#Result: Baseline rates of CEWL did not differ between treatment groups (estimate = 1.68, SE = 1.60, F(1,27) = 1.10, p = 0.30).
mother_data_all_final_8 %>%
  dplyr::filter(Preg_Stage == "DAC") %>%
  ggplot(aes(x = Hydration_Trmt, y = Plasma_Osmol_Rep_mean, fill = Hydration_Trmt)) +
  geom_boxplot() +
  theme_classic() +
  labs(x = "Hydration Treatment", y = "Plasma Osmolarity")
```
Snakes that DID give birth
```{r}
BirthSnakes_CEWL_LMM_1 <- lme4::lmer(data = birth_snakes,
                      CEWL_g_m2h ~
                        Hydration_Trmt *
                        (Day_Relative + Days_in_Treatment) +
                        calibrated_cloacal_temp +
                        msmt_temp_C +
                        msmt_RH_percent +
                        (1|Indiv_ID))

summary(BirthSnakes_CEWL_LMM_1)
#Lower t values are less significant
drop1(BirthSnakes_CEWL_LMM_1)
anova(BirthSnakes_CEWL_LMM_1)
#Warning means random effects are small. 
```
Based on model, 1 the first variable to drop is the interaction between hydration treatment and the number of days in treatment. 
```{r}
BirthSnakes_CEWL_LMM_2 <- lme4::lmer(data = birth_snakes,
                      CEWL_g_m2h ~
                        Hydration_Trmt *
                        Day_Relative +
                        calibrated_cloacal_temp +
                        msmt_temp_C +
                        msmt_RH_percent +
                        Days_in_Treatment +
                        (1|Indiv_ID))

summary(BirthSnakes_CEWL_LMM_2)
#Lower t values are less significant
drop1(BirthSnakes_CEWL_LMM_2)
anova(BirthSnakes_CEWL_LMM_2)
#Warning means random effects are small. 
```
Based on model 2, the next variable to drop is days in treatment. 
```{r}
BirthSnakes_CEWL_LMM_3 <- lme4::lmer(data = birth_snakes,
                      CEWL_g_m2h ~
                        Hydration_Trmt *
                        Day_Relative +
                        calibrated_cloacal_temp +
                        msmt_temp_C +
                        msmt_RH_percent +
                        (1|Indiv_ID))

summary(BirthSnakes_CEWL_LMM_3)
#Lower t values are less significant
drop1(BirthSnakes_CEWL_LMM_3)
anova(BirthSnakes_CEWL_LMM_3)
#Warning means random effects are small. 
```
Based on model 3, the next variable to drop is the interaction between hydration treatment and day relative. 
```{r}
BirthSnakes_CEWL_LMM_4 <- lme4::lmer(data = birth_snakes,
                      CEWL_g_m2h ~
                        Hydration_Trmt +
                        Day_Relative +
                        calibrated_cloacal_temp +
                        msmt_temp_C +
                        msmt_RH_percent +
                        (1|Indiv_ID))

summary(BirthSnakes_CEWL_LMM_4)
#Lower t values are less significant
drop1(BirthSnakes_CEWL_LMM_4)
anova(BirthSnakes_CEWL_LMM_4)
#Warning means random effects are small. 
```
Based on model 4, the next variable to drop is hydration treatment. 
```{r}
BirthSnakes_CEWL_LMM_5 <- lme4::lmer(data = birth_snakes,
                      CEWL_g_m2h ~
                        calibrated_cloacal_temp +
                        msmt_temp_C +
                        Day_Relative +
                        msmt_RH_percent +
                        (1|Indiv_ID))

summary(BirthSnakes_CEWL_LMM_5)
#Lower t values are less significant
drop1(BirthSnakes_CEWL_LMM_5)
anova(BirthSnakes_CEWL_LMM_5)
#Warning means random effects are small. 
```
Next variable to drop is day relative 
```{r}
BirthSnakes_CEWL_LMM_6 <- lme4::lmer(data = birth_snakes,
                      CEWL_g_m2h ~
                        calibrated_cloacal_temp +
                        msmt_temp_C +
                        msmt_RH_percent +
                        (1|Indiv_ID))

summary(BirthSnakes_CEWL_LMM_6)
#Lower t values are less significant
drop1(BirthSnakes_CEWL_LMM_6)
anova(BirthSnakes_CEWL_LMM_6)
#Warning means random effects are small. 
```
next to drop is body temp
```{r}
BirthSnakes_CEWL_LMM_7 <- lme4::lmer(data = birth_snakes,
                      CEWL_g_m2h ~
                        msmt_temp_C +
                        msmt_RH_percent +
                        (1|Indiv_ID))

summary(BirthSnakes_CEWL_LMM_7)
#Lower t values are less significant
drop1(BirthSnakes_CEWL_LMM_7)
anova(BirthSnakes_CEWL_LMM_7)
#Warning means random effects are small. 
```
Next to drop is ambient temp
```{r}
BirthSnakes_CEWL_LMM_8 <- lme4::lmer(data = birth_snakes,
                      CEWL_g_m2h ~
                        msmt_RH_percent +
                        (1|Indiv_ID))

summary(BirthSnakes_CEWL_LMM_8)
#Lower t values are less significant
drop1(BirthSnakes_CEWL_LMM_8)
anova(BirthSnakes_CEWL_LMM_8)
#Warning means random effects are small. 
```
null model 
```{r}
BirthSnakes_CEWL_LMM_null <- lme4::lmer(data = birth_snakes,
                      CEWL_g_m2h ~ 1 + (1|Indiv_ID))

summary(BirthSnakes_CEWL_LMM_null)
#Lower t values are less significant
drop1(BirthSnakes_CEWL_LMM_null)
anova(BirthSnakes_CEWL_LMM_null)
#Warning means random effects are small. 
```
Model Selection
```{r CEWL mod compare}
cewl_models <- list(BirthSnakes_CEWL_LMM_1, BirthSnakes_CEWL_LMM_2, BirthSnakes_CEWL_LMM_3, BirthSnakes_CEWL_LMM_4, BirthSnakes_CEWL_LMM_5, BirthSnakes_CEWL_LMM_6, BirthSnakes_CEWL_LMM_7, BirthSnakes_CEWL_LMM_8, BirthSnakes_CEWL_LMM_null)

#specify model names
cewl_mod_names <- c('model1', 
                    'model2', 
                    'model3',
                    'model4',
                    'model5',
                    'model6',
                    'model7',
                    'model8',
                    'modelnull')

#calculate AIC of each model
cewl_AICc <- data.frame(aictab(cand.set = cewl_models, 
                                 modnames = cewl_mod_names))
cewl_AICc
```
#SAVANNAH: OLD EXPERIMENTAL CEWL MODEL

Since day relative to birth is not significant, I can include all snakes in one model together. 
###All Snakes
```{r}
CEWL_LMM_1 <- lme4::lmer(data = mother_data_all_final_8,
                      CEWL_g_m2h ~
                        Hydration_Trmt *
                        (Days_in_Treatment) +
                        calibrated_cloacal_temp +
                        msmt_temp_C +
                        msmt_RH_percent +
                        (1|Indiv_ID))

summary(CEWL_LMM_1)
#Lower t values are less significant
drop1(CEWL_LMM_1)
anova(CEWL_LMM_1)
```
Based on model 1, the first variable to drop is the interaction between hydration treatment and days in treatment. 
```{r}
CEWL_LMM_2 <- lme4::lmer(data = mother_data_all_final_8,
                      CEWL_g_m2h ~
                        Hydration_Trmt +
                        Days_in_Treatment +
                        calibrated_cloacal_temp +
                        msmt_temp_C +
                        msmt_RH_percent +
                        (1|Indiv_ID))

summary(CEWL_LMM_2)
#Lower t values are less significant
drop1(CEWL_LMM_2)
anova(CEWL_LMM_2)
```
The next variable to drop is body temp. 
```{r}
CEWL_LMM_3 <- lme4::lmer(data = mother_data_all_final_8,
                      CEWL_g_m2h ~
                        Hydration_Trmt +
                        Days_in_Treatment +
                        msmt_temp_C +
                        msmt_RH_percent +
                        (1|Indiv_ID))

summary(CEWL_LMM_3)
#Lower t values are less significant
drop1(CEWL_LMM_3)
anova(CEWL_LMM_3)
```
The next to drop is days in treatment 
```{r}
CEWL_LMM_4 <- lme4::lmer(data = mother_data_all_final_8,
                      CEWL_g_m2h ~
                        Hydration_Trmt +
                        msmt_temp_C +
                        msmt_RH_percent +
                        (1|Indiv_ID))

summary(CEWL_LMM_4)
#Lower t values are less significant
drop1(CEWL_LMM_4)
anova(CEWL_LMM_4)
```
The next variable to drop is hydration treatment. 
```{r}
CEWL_LMM_5 <- lme4::lmer(data = mother_data_all_final_8,
                      CEWL_g_m2h ~
                        msmt_temp_C +
                        msmt_RH_percent +
                        (1|Indiv_ID))

summary(CEWL_LMM_5)
#Lower t values are less significant
drop1(CEWL_LMM_5)
anova(CEWL_LMM_5)
```
Next to drop is ambient temp
```{r}
CEWL_LMM_6 <- lme4::lmer(data = mother_data_all_final_8,
                      CEWL_g_m2h ~
                        msmt_RH_percent +
                        (1|Indiv_ID))

summary(CEWL_LMM_6)
#Lower t values are less significant
drop1(CEWL_LMM_6)
anova(CEWL_LMM_6)
```
null model
```{r}
CEWL_LMM_null <- lme4::lmer(data = mother_data_all_final_8,
                      CEWL_g_m2h ~ 1 +
                        (1|Indiv_ID))

summary(CEWL_LMM_null)
#Lower t values are less significant
anova(CEWL_LMM_null)
```
####Model Selection
```{r CEWL mod compare}
cewl_models_all <- list(CEWL_LMM_1, CEWL_LMM_2, CEWL_LMM_3, CEWL_LMM_4, CEWL_LMM_5, CEWL_LMM_6, CEWL_LMM_null)

#specify model names
cewl_mod_names_all <- c('model1', 
                    'model2', 
                    'model3',
                    'model4',
                    'model5',
                    'model6',
                    'modelnull')

#calculate AIC of each model
cewl_AICc_all <- data.frame(aictab(cand.set = cewl_models_all, 
                                 modnames = cewl_mod_names_all))
cewl_AICc_all
```
The best model is model 4 below: 
```{r}
CEWL_LMM_4 <- lmerTest::lmer(data = mother_data_all_final_8,
                      CEWL_g_m2h ~
                        Hydration_Trmt +
                        msmt_temp_C +
                        msmt_RH_percent +
                        (1|Indiv_ID))

summary(CEWL_LMM_4)
anova(CEWL_LMM_4, type = "3", ddf = "Kenward-Roger")
#Result: For all pregnant and post-parturiant female snakes, CEWL had a positive relationship with ambient temperature (estimate = 2.72, SE = 0.51, F(1,73.62) = 27.52, p < 0.0001) and ambient humidity (estimate = 1.18, SE = 0.17, F(1,73.48) = 45.23, p < 0.0001) . On average, snakes in the hydration treatment had higher rates of CEWL (estimate = 2.14, SE = 0.89, F(1,26.96) = 5.69, p = 0.024).

```

####Final Model & Assumptions
We are choosing model 4 as our best model. 
Check linear regression assumptions/conditions:
```{r CEWL exp model assumptions}
plot(CEWL_LMM_4)
shapiro.test(residuals(CEWL_LMM_4))
car::vif(CEWL_LMM_4)
#all ok?
```

#SAVANNAH: OLD BASELINE OSMOL MODEL
#Osmolarity Models

##Baseline Model

```{r}
mothers_baseline_birthsnakes <- mothers_baseline %>%
  filter(Gave_Birth == "Y")

partur <- lm(data = mothers_baseline_birthsnakes, 
             Plasma_Osmol_Rep_mean ~ Day_Relative)

summary(partur)
anova(partur)
```
Day relative to birth was not significant. Will run all individuals in one model. 

Now creating an initial model with all variables that may impact baseline osmol so mass, SVL, body condition, capture date.
```{r}
baseline_osmol_1 <- lme4::lmer(data = mothers_baseline,
                      Plasma_Osmol_Rep_mean ~
                        Mass_g +
                        SVL_cm +
                        Body_Condition +
                        (1|CEWL_Blood_Collect_Date))
                    
summary(baseline_osmol_1)
drop1(baseline_osmol_1)
anova(baseline_osmol_1)

TukeyHSD(aov(data = mothers_baseline, formula = Plasma_Osmol_Rep_mean ~ Rookery_Capture_ID))
```
The capture date didn't account for any of the variance so first dropping the random effect.
```{r}
baseline_osmol_2 <- lm(data = mothers_baseline,
                      Plasma_Osmol_Rep_mean ~
                        Mass_g +
                        SVL_cm +
                        Body_Condition)
                    
car::vif(baseline_osmol_2)
summary(baseline_osmol_2)
drop1(baseline_osmol_2)
anova(baseline_osmol_2)
```
multicollinearity with these three variables. Will try dropping mass first since it explains the least amount of variability. 
```{r}
baseline_osmol_3 <- lm(data = mothers_baseline,
                      Plasma_Osmol_Rep_mean ~
                        SVL_cm +
                        Body_Condition)
                    
car::vif(baseline_osmol_3)
summary(baseline_osmol_3)
drop1(baseline_osmol_3)
anova(baseline_osmol_3)
```
No more issues of multicollinearity. Now will drop SVL. 
```{r}
baseline_osmol_4 <- lm(data = mothers_baseline,
                      Plasma_Osmol_Rep_mean ~
                        Body_Condition)
                    
summary(baseline_osmol_4)
drop1(baseline_osmol_4)
anova(baseline_osmol_4)
```

null model
```{r}
baseline_osmol_null <- lm(data = mothers_baseline,
                      Plasma_Osmol_Rep_mean ~ 1)
```

###Model selection
```{r CEWL mod compare}
baseline_osmol_mods <- list(baseline_osmol_2, baseline_osmol_3, baseline_osmol_4, baseline_osmol_null)

#specify model names
baeline_osmol_mod_names_all <- c('model2', 
                    'model3',
                    'model4',
                    'modelnull')

#calculate AIC of each model
cewl_AICc_all <- data.frame(aictab(cand.set = baseline_osmol_mods, 
                                 modnames = baeline_osmol_mod_names_all))
cewl_AICc_all
```
The best model is model is 3:
```{r}
baseline_osmol <- lm(data = mothers_baseline,
                      Plasma_Osmol_Rep_mean ~
                        SVL_cm +
                        Body_Condition)

test3 <- lm(data = mothers_baseline,
                      Plasma_Osmol_Rep_mean ~
                        Body_Condition)

summary(test3)
anova(test3)

summary(baseline_osmol)
anova(baseline_osmol)
```
Result: Baseline osmolality was best explained by body condition (lm: estimate = -81.37, SE = 46.9, F(1, 26) = 3.01, p = 0.095) and SVL (lm: estimate = 0.95, SE = 0.50, F(1, 26) = 2.5, p = 0.13). 

###Pub Figure

Linear model mother osmolality DAC

```{r}
osmol_tmt_DAC_lm <- lm(data = mothers_baseline, Plasma_Osmol_Rep_mean ~ Hydration_Trmt)
mom_baseline_osmol_CI <- data.frame(emmeans(osmol_tmt_DAC_lm, "Hydration_Trmt"))

summary(osmol_tmt_DAC_lm)
anova(osmol_tmt_DAC_lm)

ggplot(data = mothers_baseline,
       aes(x = Body_Condition,
           y = Plasma_Osmol_Rep_mean)) +
  geom_point() +
  geom_smooth(method = "lm")
```
Getting CI
```{r}
mom_baseline_osmol_CI <- data.frame(emmeans(osmol_tmt_DAC_lm, "Hydration_Trmt"))
```

```{r}
ggplot() +
  geom_jitter(data = mothers_baseline, 
             aes(x = Hydration_Trmt, 
                 y = Plasma_Osmol_Rep_mean, 
                 color = Hydration_Trmt),
             size = 2,
             alpha = 0.5,
             show.legend = TRUE) +
  geom_point(data = mom_baseline_osmol_CI, 
             aes(x = Hydration_Trmt, 
                 y = emmean),
             color = "black", 
             size = 3) +
  theme_classic() +
  annotate(geom = "text", x = 1, y = 370, label = "p < 0.0001", 
           size = 5) +
  scale_color_manual(values = c("C" = "orange2", "W" = "dodgerblue")) +
  labs(x = "", y = "Osmolality (mmol kg-1)", color = "Treatment", title = "Before Treatment") +
  geom_errorbar(data = mom_baseline_osmol_CI, aes(x = Hydration_Trmt,
                               y = emmean, 
                               ymin = lower.CL, 
                               ymax = upper.CL,
                               width = .3),
                color = "black") +
   theme(text = element_text(color = "black",
                            size = 22),
        axis.text = element_text(color = "black", 
                                 size = 16),
        legend.text = element_text(color = "black",
                                 size = 22),
        plot.title = element_text(color = "black",
                                  size = 22),
        legend.text.align = 0,
        legend.position = "right") + 
  scale_y_continuous(limits = c(270, 382), breaks = seq(270, 382, by = 20)) -> baseline_osmol_mothers_tmrmt_fig

ggsave("Mother Baseline Osmolality by Treatment.png", 
       plot = baseline_osmol_mothers_tmrmt_fig,
       width = 4,
       height = 4)
```

##Initial Models  (Experimental)
Is there a difference in osmolarity between the treatment group and the control group the day after capture? 
```{r}
DAC_osmol <- mother_data_all_final_8 %>%
  dplyr::filter(Preg_Stage == "DAC")

DAC_osmol_lm <- lm(Plasma_Osmol_Rep_mean ~ Hydration_Trmt, data = DAC_osmol)

summary(DAC_osmol_lm)
anova(DAC_osmol_lm)

#Result: On average, the hydration treatment had higher baseline levels of osmolarity compared to the control group (estimate = 25.03, SE = 5.41, F(1,27) = 21.38, p < 0.0001).
mother_data_all_final_8 %>%
  dplyr::filter(Preg_Stage == "DAC") %>%
  ggplot(aes(x = Hydration_Trmt, y = Plasma_Osmol_Rep_mean, fill = Hydration_Trmt)) +
  geom_boxplot() +
  theme_classic() +
  labs(x = "Hydration Treatment", y = "Plasma Osmolarity")
```
####Post Treatment Osmolality
```{r}
not_dac_or_1wab <- mother_data_all_final_8 %>%
  filter(Preg_Stage != "DAC") %>%
  filter(Preg_Stage != "1WAB") %>%
  filter(Preg_Stage != "2WAC")

df_1wac <- mother_data_all_final_8 %>%
  filter(Preg_Stage == "1WAC")

df_dab <- mother_data_all_final_8 %>%
  filter(Preg_Stage == "DAB")

dab_no_dac <- df_dab[c(9, 10, 11, 13, 14, 15, 16, 17, 18), ]

osmolality_post_tmt_df <- full_join(df_1wac, dab_no_dac)
```
#SAVANNAH: OLD POST TREATMENT OSMOL MODEL

****Remember that birthing effecting osmolality, so we created two separate models for the snakes that gave birth and those that didn't. See both below. 

post treatment linear model to see the effect of treatment on osmolality. This has one measurement per individual. For most individuals it is their one week after capture measuremeant. If the snake gave birth prior to that one week timeframe, this is their post birth osmolality.
```{r}
post_tmt_osmol_lm <- lm(data = osmolality_post_tmt_df, Plasma_Osmol_Rep_mean ~ Hydration_Trmt)

summary(post_tmt_osmol_lm)
anova(post_tmt_osmol_lm)
```



```{r}
#getting CI
CI_mothers_osmol <- data.frame(emmeans(post_tmt_osmol_lm, "Hydration_Trmt"))

#CI_mothers_osmol <- data.frame(pairs(emmeans(post_tmt_osmol_lm, "Hydration_Trmt")))
```

#####Pub Fig (all snakes)
```{r}
post_tmt_osmol_lm %>%
ggplot() +
  geom_jitter(aes(x = Hydration_Trmt, 
                 y = Plasma_Osmol_Rep_mean, 
                 color = Hydration_Trmt),
             size = 2,
             alpha = 0.5,
             show.legend = TRUE) +
  geom_point(data = CI_mothers_osmol, 
             aes(x = Hydration_Trmt, 
                 y = emmean),
             color = "black", 
             size = 3) +
  theme_classic() +
  annotate(geom = "text", x = 1.5, y = 370, label = "p = 0.054", 
           size = 5) +
  scale_color_manual(values = c("C" = "orange2", "W" = "dodgerblue")) +
  labs(x = "", y = "", color = "", title = "After Treatment") +
  geom_errorbar(data = CI_mothers_osmol, aes(x = Hydration_Trmt,
                               y = emmean, 
                               ymin = lower.CL, 
                               ymax = upper.CL,
                               width = .3),
                color = "black") +
  theme(text = element_text(color = "black",
                            size = 22),
        axis.text = element_text(color = "black", 
                                 size = 16),
        legend.text = element_text(color = "black",
                                 size = 22),
        plot.title = element_text(color = "black",
                                  size = 22),
        legend.text.align = 0,
        legend.position = "right") +
  scale_y_continuous(limits = c(270, 382), breaks = seq(270, 382, by = 20)) -> mother_osmol_posttmt_fig
```



###Snakes that DID give birth
```{r}
summary(birth_snakes)
BirthSnakes_LMM_1 <- lme4::lmer(data = birth_snakes,
                      Plasma_Osmol_Rep_mean ~
                        Hydration_Trmt *
                        Days_in_Treatment +
                        Day_Relative +
                        Body_Condition +
                        (1|Indiv_ID))

summary(BirthSnakes_LMM_1)
#Lower t values are less significant
drop1(BirthSnakes_LMM_1)
anova(BirthSnakes_LMM_1)
```
Based on model 1, the first variable to drop is body condition. 
```{r}
summary(birth_snakes)
BirthSnakes_LMM_2 <- lme4::lmer(data = birth_snakes,
                      Plasma_Osmol_Rep_mean ~
                        Hydration_Trmt *
                        Days_in_Treatment +
                        Day_Relative +
                        (1|Indiv_ID))

summary(BirthSnakes_LMM_2)
#Lower t values are less significant
drop1(BirthSnakes_LMM_2)
anova(BirthSnakes_LMM_2)
```
The next variable to drop is the interaction.
```{r}
summary(birth_snakes)
BirthSnakes_LMM_3 <- lme4::lmer(data = birth_snakes,
                      Plasma_Osmol_Rep_mean ~
                        Hydration_Trmt +
                        Days_in_Treatment +
                        Day_Relative +
                        (1|Indiv_ID))

summary(BirthSnakes_LMM_3)
#Lower t values are less significant
drop1(BirthSnakes_LMM_3)
anova(BirthSnakes_LMM_3)
```
Next to drop is treatment
```{r}
summary(birth_snakes)
BirthSnakes_LMM_4 <- lme4::lmer(data = birth_snakes,
                      Plasma_Osmol_Rep_mean ~
                        Days_in_Treatment +
                        Day_Relative +
                        (1|Indiv_ID))

summary(BirthSnakes_LMM_4)
#Lower t values are less significant
drop1(BirthSnakes_LMM_4)
anova(BirthSnakes_LMM_4)
```
next to drop is days in tmt
```{r}
BirthSnakes_LMM_5 <- lme4::lmer(data = birth_snakes,
                      Plasma_Osmol_Rep_mean ~
                        Day_Relative +
                        (1|Indiv_ID))

summary(BirthSnakes_LMM_5)
#Lower t values are less significant
drop1(BirthSnakes_LMM_5)
anova(BirthSnakes_LMM_5)
```

null model 
```{r}
summary(birth_snakes)
BirthSnakes_LMM_null<- lme4::lmer(data = birth_snakes,
                      Plasma_Osmol_Rep_mean ~ 1 +
                        (1|Indiv_ID))

summary(BirthSnakes_LMM_null)
#Lower t values are less significant
drop1(BirthSnakes_LMM_null)
anova(BirthSnakes_LMM_null)
```
####Model Selection
```{r CEWL mod compare}
osmolarity_models <- list(BirthSnakes_LMM_1, BirthSnakes_LMM_2, BirthSnakes_LMM_3, BirthSnakes_LMM_4, BirthSnakes_LMM_5, BirthSnakes_LMM_null)

#specify model names
osmolarity_mod_names <- c('model1', 
                    'model2', 
                    'model3',
                    'model4',
                    'model5',
                    'modelnull')

#calculate AIC of each model
osmolarity_AICc <- data.frame(aictab(cand.set = osmolarity_models, 
                                 modnames = osmolarity_mod_names))
osmolarity_AICc
```
The best model is 2. Looking at model 1, body condition explains 0% of the data. It can't be that one. Going with 2. 
```{r}
BirthSnakes_LMM_2 <- lmerTest::lmer(data = birth_snakes,
                      Plasma_Osmol_Rep_mean ~
                        Hydration_Trmt *
                        Days_in_Treatment +
                        Day_Relative +
                        (1|Indiv_ID))

summary(BirthSnakes_LMM_2)
#Lower t values are less significant
anova(BirthSnakes_LMM_2)
emtrends(BirthSnakes_LMM_2, "Hydration_Trmt", var = "Days_in_Treatment")
pairs(emtrends(BirthSnakes_LMM_2, "Hydration_Trmt", var = "Days_in_Treatment"))
#result: The best osmolarity model for the snakes that did give birth included the day the measurement was taken relative to the day of parturition, hydration treatment, the number of days in treatment, and the interaction between hydration treatment and the number of days in treatment (Table 1) Table 1 = a combo of summary and anova table. Plasma osmolarity increased by 2.16 for every day in treatment for snakes in the control treatment, but decreased by 1.42 for snakes in the hydration treatment (pairwise comparison of the slopes: estimate = 3.58, SE = 0.86, p < 0.001)
```
####Final Model & Assumptions
We are choosing model 2 as our best model. 
Check linear regression assumptions/conditions:
```{r CEWL exp model assumptions}
plot(BirthSnakes_LMM_2)
shapiro.test(residuals(BirthSnakes_LMM_2))
car::vif(BirthSnakes_LMM_2)
#all ok?
```

###Snakes that DID NOT give brith
```{r}
No_BirthSnakes_LMM_1 <- lmerTest::lmer(data = no_birth_snakes,
                      Plasma_Osmol_Rep_mean ~
                        Hydration_Trmt *
                        Days_in_Treatment +
                        (1|Indiv_ID))

summary(No_BirthSnakes_LMM_1)
#Lower t values are less significant
drop1(No_BirthSnakes_LMM_1)
anova(No_BirthSnakes_LMM_1)
```
First drop interaction
```{r}
No_BirthSnakes_LMM_2 <- lmerTest::lmer(data = no_birth_snakes,
                      Plasma_Osmol_Rep_mean ~
                        Hydration_Trmt +
                        Days_in_Treatment +
                        (1|Indiv_ID))

summary(No_BirthSnakes_LMM_2)
#Lower t values are less significant
drop1(No_BirthSnakes_LMM_2)
anova(No_BirthSnakes_LMM_2)
```
Now drop  days in treatment 
```{r}
No_BirthSnakes_LMM_3 <- lmerTest::lmer(data = no_birth_snakes,
                      Plasma_Osmol_Rep_mean ~
                        Hydration_Trmt +
                        (1|Indiv_ID))

summary(No_BirthSnakes_LMM_3)
#Lower t values are less significant
drop1(No_BirthSnakes_LMM_3)
anova(No_BirthSnakes_LMM_3)
```
null model 
```{r}
No_BirthSnakes_LMM_null <- lmerTest::lmer(data = no_birth_snakes,
                      Plasma_Osmol_Rep_mean ~ 1 +
                        (1|Indiv_ID))
```

####Model Selection
```{r CEWL mod compare}
osmolarity_models <- list(No_BirthSnakes_LMM_1, No_BirthSnakes_LMM_2, No_BirthSnakes_LMM_3, No_BirthSnakes_LMM_null)

#specify model names
osmolarity_mod_names <- c('model1', 
                    'model2', 
                    'model3',
                    'modelnull')

#calculate AIC of each model
osmolarity_AICc <- data.frame(aictab(cand.set = osmolarity_models, 
                                 modnames = osmolarity_mod_names))
osmolarity_AICc
```
####Final Model & Assumptions
Best model is 1
```{r}
No_BirthSnakes_LMM_1 <- lmerTest::lmer(data = no_birth_snakes,
                      Plasma_Osmol_Rep_mean ~
                        Hydration_Trmt *
                        Days_in_Treatment +
                        (1|Indiv_ID))

summary(No_BirthSnakes_LMM_1)
anova(No_BirthSnakes_LMM_1)
emtrends(No_BirthSnakes_LMM_1, "Hydration_Trmt", var = "Days_in_Treatment")
pairs(emtrends(No_BirthSnakes_LMM_1, "Hydration_Trmt", var = "Days_in_Treatment"))
#Result: The best osmolarity model for the mothers that did not give birth included hydration treatment, the number of days in treatment, and the interaction between treatment and the number of days in treatment (Table). Plasma osmolarity increased by 2.04 per day in treatment for the snakes in the control group and decreased by 2.24 for snakes in the hydration treatment (pairwise comparison of slopes: estimate = 4.29, SE = 0.88, t = 4.91, p < 0.001). 
```
Check linear regression assumptions/conditions:
```{r CEWL exp model assumptions}
plot(No_BirthSnakes_LMM_1)
shapiro.test(residuals(No_BirthSnakes_LMM_1))
car::vif(No_BirthSnakes_LMM_1)
#all ok
```

#CEWL vs Osmolarity 
Looking at the relationship between cewl and osmolarity. I am not sure if I can do this because the correlation have multiple measurements from 1 individual. 
```{r}
cor(mother_data_all_final_8$Plasma_Osmol_Rep_mean, mother_data_all_final_8$CEWL_g_m2h)
cor.test(mother_data_all_final_8$Plasma_Osmol_Rep_mean, mother_data_all_final_8$CEWL_g_m2h)

cewl_osmol_lm <- lm(data = mother_data_all_final_8,
                    CEWL_g_m2h ~ Plasma_Osmol_Rep_mean)
summary(cewl_osmol_lm)

cewl_osmol_lm_2 <- lm(data = mother_data_all_final_8,
                    Plasma_Osmol_Rep_mean ~ CEWL_g_m2h)
summary(cewl_osmol_lm_2)
```

Individual dfs
```{r}
mothers_DAC <- mother_data_all_final_8 %>%
  filter(Preg_Stage == "DAC")

mothers_DAB <- mother_data_all_final_8 %>%
  filter(Preg_Stage == "DAB")

mothers_1WAC <- mother_data_all_final_8 %>%
  filter(Preg_Stage == "1WAC")
```

Day after capture
```{r}
cor(mothers_DAC$Plasma_Osmol_Rep_mean, mothers_DAC$CEWL_g_m2h)
cor.test(mothers_DAC$Plasma_Osmol_Rep_mean, mothers_DAC$CEWL_g_m2h)

dac_lm <- lm(data = mothers_DAC, CEWL_g_m2h ~ Plasma_Osmol_Rep_mean)
summary(dac_lm)
anova(dac_lm)

#Result: For the pregnant females day after capture, there is a positive relationship between plasma osmolarity and CEWL (estimate = 0.098, SE = 0.039, F(1,27) = 6.24, p = 0.019, R = 0.43).
```
Seems to be a significant correlation.
##Pub Figure
```{r}
ggplot(data = mothers_DAC, aes(x = Plasma_Osmol_Rep_mean, y = CEWL_g_m2h)) +
  geom_point(size = 2, 
             alpha = 0.7,
             color = "springgreen3") +
  annotate(geom = "text", 
           x = 300, 
           y = 30, 
           label = "p = 0.019", 
           size = 5) +
  theme_classic() +
  geom_smooth(aes(x = Plasma_Osmol_Rep_mean, y = CEWL_g_m2h),
              method = "lm", 
              se = TRUE, 
              show.legend = TRUE, 
              size = 1,
              color = "black") +
  labs(x = "Plasma Osmolality (mmol kg-1)", 
       y = "CEWL (g m2h-1)") +
  theme(text = element_text(color = "black",
                            size = 22),
        axis.text = element_text(color = "black", 
                                 size = 16),
        legend.text = element_text(color = "black",
                                 size = 22),
        plot.title = element_text(color = "black",
                                  size = 22),
        legend.text.align = 0,
        legend.position = "right",) +
  scale_x_continuous(limits = c(280, 383), breaks = seq(280, 383, by = 20)) +
  scale_y_continuous(limits = c(5, 33),
                  breaks = seq(5, 33, by = 5)) -> Osmol_v_CEWL_DAC

ggsave("Osmolality vs CEWL Day After Capture.png", 
       plot = Osmol_v_CEWL_DAC, 
       width = 7, 
       height = 4)
```

Day after birth
```{r}
cor(mothers_DAB$Plasma_Osmol_Rep_mean, mothers_DAB$CEWL_g_m2h)
cor.test(mothers_DAB$Plasma_Osmol_Rep_mean, mothers_DAB$CEWL_g_m2h)

dab_lm <- lm(data = mothers_DAB, CEWL_g_m2h ~ Plasma_Osmol_Rep_mean)
summary(dab_lm)
anova(dab_lm)
#Result: For the snakes day after parturition, there is no significant correlation between plasma osmolarity and CEWL (estimate = 0.035, SE - 0.065, F(1,16) = 0.29, p = 0.60). However, the relationship is still positive. 
```
No correlation.
Figure:
```{r}
ggplot(data = mothers_DAB, aes(x = Plasma_Osmol_Rep_mean, y = CEWL_g_m2h)) +
  geom_point(size = 2, 
             alpha = 0.7,
             color = "springgreen3") +
  annotate(geom = "text", 
           x = 365, 
           y = 30, 
           label = "p = 0.60", 
           size = 5) +
  theme_classic() +
  geom_smooth(aes(x = Plasma_Osmol_Rep_mean, y = CEWL_g_m2h),
              method = "lm", 
              se = TRUE, 
              show.legend = TRUE, 
              size = 1,
              color = "black") +
  labs(x = "Plasma Osmolality (mmol kg-1)", 
       y = "CEWL (g m2h-1)") +
  theme(text = element_text(color = "black",
                            size = 22),
        axis.text = element_text(color = "black", 
                                 size = 16),
        legend.text = element_text(color = "black",
                                 size = 22),
        plot.title = element_text(color = "black",
                                  size = 22),
        legend.text.align = 0,
        legend.position = "right",) +
  scale_x_continuous(limits = c(280, 383), breaks = seq(280, 383, by = 20)) +
  scale_y_continuous(limits = c(5, 33),
                  breaks = seq(5, 33, by = 5)) -> mother_dab_cewl_v_osmol_fig
```

1 week after capture
```{r}
cor(mothers_1WAC$Plasma_Osmol_Rep_mean, mothers_1WAC$CEWL_g_m2h)
cor.test(mothers_1WAC$Plasma_Osmol_Rep_mean, mothers_1WAC$CEWL_g_m2h)

wac_lm <- lm(data = mothers_1WAC, CEWL_g_m2h ~ Plasma_Osmol_Rep_mean)
summary(wac_lm)
anova(wac_lm)
#Result: For all pregnant snakes one week after capture and prior to parturition, there is no significant correlation between plasma osmolarity and CEWL (estimate = 0.029, SE - 0.044, F(1,18) = 0.44, p = 0.51). However, the relationship is still positive. 
```
No correlation
Figure:
```{r}
ggplot(data = mothers_1WAC, aes(x = Plasma_Osmol_Rep_mean, y = CEWL_g_m2h)) +
  geom_point() +
  theme_classic() +
  geom_smooth(method = "lm") +
  stat_cor(method = "pearson") +
  labs(x = "Plasma Osmolality", y = "CEWL", title = "Pregnant Females 1 Week After Capture")
```
Osmol and CEWL before/post tmt
```{r}
ggarrange(baseline_osmol_mothers_tmrmt_fig, mother_osmol_posttmt_fig, baseline_cewl_fig, cewl_posttmt_mothers,
          ncol = 2, nrow = 2,
          labels = c("A", "B", "C", "D"),
          common.legend = TRUE,
          legend = "bottom",
          align = "v") -> mother_osmol_cewl_pre_post_tmt_fig

ggsave("Mothers Osmol and CEWl before and after TMT.png", 
       plot = mother_osmol_cewl_pre_post_tmt_fig, 
       width = 10, 
       height = 10)
```

#Pub Fig: CEWL v Osmol moms + neonates
Have to run neonate rmd for this to work. 
```{r}
ggarrange(Osmol_v_CEWL_DAC, mother_dab_cewl_v_osmol_fig, neonate_CEWL_v_osmol, clutch_Cewl_v_osmol_ps,
          ncol = 1, nrow = 4,
          labels = c("A", "B", "C", "D"),
          align = "v") -> CEWL_v_osmol_all

ggsave("Osmolality versus CEWL all together.png", 
       plot = CEWL_v_osmol_all, 
       width = 8, 
       height = 19)
```
#Poster figure
```{r}
  mother_data_all_final_8 %>%
  filter(Gave_Birth == "Y") %>%
  ggplot() +
  geom_jitter(aes(x = Days_in_Treatment, 
                 y = Plasma_Osmol_Rep_mean, 
                 color = Hydration_Trmt), 
             size = 2, 
             alpha = 0.5) +
  annotate(geom = "text", x = 4, y = 350, label = "p < 0.001", 
           size = 5) +
  theme_classic() +
  geom_smooth(aes(x = Days_in_Treatment, 
                  y = Plasma_Osmol_Rep_mean, 
                  colour = Hydration_Trmt), 
              method = "lm", se = FALSE, 
              show.legend = TRUE, 
              size = 1) +
  scale_color_manual(values = c("C" = "orange2", "W" = "dodgerblue")) +
  labs(x = "Number of Days in Treatment", 
       y = "Plasma Osmolality (mmol kg-1)",
       title = "Snakes that did give birth",
       color = "Treatment") +
  theme(text = element_text(color = "black",
                            size = 22),
        axis.text = element_text(color = "black", 
                                 size = 16),
        legend.text = element_text(color = "black",
                                 size = 22),
        plot.title = element_text(color = "black",
                                  size = 22),
        legend.text.align = 0,
        legend.position = "right",) +
  scale_x_continuous(breaks = c(0, 2, 4, 6, 8, 10, 12, 14, 16), limits = c(0, 16)) +
  scale_y_continuous(limits = c(270, 375), 
                     breaks = seq(270, 375, by = 20)) -> poster1
```

```{r}
    mother_data_all_final_8 %>%
  filter(Gave_Birth == "N") %>%
  ggplot() +
  geom_jitter(aes(x = Days_in_Treatment, 
                 y = Plasma_Osmol_Rep_mean, 
                 color = Hydration_Trmt), 
             size = 2, 
             alpha = 0.5) +
  annotate(geom = "text", x = 4, y = 350, label = "p < 0.001", 
           size = 5) +
  theme_classic() +
  geom_smooth(aes(x = Days_in_Treatment, 
                  y = Plasma_Osmol_Rep_mean, 
                  colour = Hydration_Trmt), 
              method = "lm", se = FALSE, 
              show.legend = TRUE, 
              size = 1) +
  labs(x = "Number of Days in Treatment", 
       y = "",
       title = "Snakes that did not give birth",
       color = "Treatment") +
  scale_color_manual(values = c("C" = "orange2", "W" = "dodgerblue")) +
  theme(text = element_text(color = "black",
                            size = 22),
        axis.text = element_text(color = "black", 
                                 size = 16),
        legend.text = element_text(color = "black",
                                 size = 22),
        plot.title = element_text(color = "black",
                                  size = 22),
        legend.text.align = 0,
        legend.position = "right",) +
  scale_x_continuous(breaks = c(0, 2, 4, 6, 8, 10, 12, 14, 16), limits = c(0, 16)) +
  scale_y_continuous(limits = c(270, 375), 
                     breaks = seq(270, 375, by = 20)) -> poster2
```

```{r}
  ggplot() +
  geom_point(data = all_birthsnakes,
              aes(x = Day_Relative, 
                 y = Plasma_Osmol_Rep_mean, 
                 color = Hydration_Trmt), 
             size = 1, 
             alpha = 0.6) +
  geom_line(data = hydration_birthsnakes,
            aes(x = Day_Relative,
                y = Plasma_Osmol_Rep_mean,
                color = Hydration_Trmt,
                group = Indiv_ID),
            alpha = 0.6) +
    geom_line(data = control_birthsnakes,
            aes(x = Day_Relative,
                y = Plasma_Osmol_Rep_mean,
                color = Hydration_Trmt,
                group = Indiv_ID),
            alpha = 0.6) +
  theme_classic() +
  theme(text = element_text(color = "black",
                            size = 22),
        axis.text = element_text(color = "black", 
                                 size = 16),
        legend.text = element_text(color = "black",
                                 size = 22),
        plot.title = element_text(color = "black",
                                  size = 22),
        legend.text.align = 0,
        legend.position = "right") +
   stat_smooth(data = all_birthsnakes,
               aes(x = Day_Relative, 
                 y = Plasma_Osmol_Rep_mean), 
                 color = "black",
                 method = "lm",
                 se = FALSE) +
  geom_vline(xintercept = 0, linetype = "dashed", color = "grey") +
  scale_color_manual(values = c("C" = "orange2", "W" = "dodgerblue")) +
  labs(x = "Day Relative to Birthing",
       y = "",
       color = "Treatment",
       title = "All Pregnant Snakes") +
  scale_x_continuous(limits = c(-14, 10)) +
  scale_y_continuous(limits = c(270, 375), 
                     breaks = seq(270, 375, by = 20)) -> poster3
```

```{r}
ggarrange(poster1, poster2, poster3,
          ncol = 3, nrow = 1,
          labels = c("A", "B", "C"),
          align = "h",
          common.legend = TRUE,
          legend = "bottom") -> posterfigure

ggsave("posterfigure.png", 
       plot = posterfigure, 
       width = 18, 
       height = 6)
```
#Mass Analysis
Doing a quick analysis to see mass loss or gain from the point of capture to after 1 week in treatment

First getting a df with all of the DAC and 1WAC measurements.
```{r}
dac_or_1wac_temp <- 
  mother_data_all_final_8 %>%
  filter(Preg_Stage == "DAC" | Preg_Stage == "1WAC")

dac_or_1wac_temp[40, 2] <- 513.9

dac_or_1wac_temp_t <- dac_or_1wac_temp %>% 
  mutate(Preg_Stage = str_replace_all(Preg_Stage, "DAC", "Before Treatment"))
```
#***SAVANNAH: MASS ANALYSIS 
NEW MASS ANALYSIS
```{r}
new_mass_lm <- lmer(data = dac_or_1wac_temp, Mass_g ~ Preg_Stage * Hydration_Trmt + (1|Indiv_ID))

Means1 <- emmeans(new_mass_lm, pairwise ~ Preg_Stage | Hydration_Trmt)
Means1$emmean
Means1$contrasts

Means2 <- emmeans(new_mass_lm, pairwise ~ Hydration_Trmt | Preg_Stage)
Means2$emmean
Means2$contrasts

new_mass_lm_CI <- data.frame(emmeans(new_mass_lm, pairwise ~ Hydration_Trmt | Preg_Stage)$emmean)

new_mass_lm_CI <- new_mass_lm_CI %>% 
  mutate(Preg_Stage = str_replace_all(Preg_Stage, "DAC", "Before Treatment")) %>%
  mutate(Preg_Stage = str_replace_all(Preg_Stage, "1WAC", "After Treatment"))
```


Making a new column for the change in mass
```{r}
dac_or_1wac <- dac_or_1wac_temp %>%
  group_by(Indiv_ID) %>%
  arrange(Preg_Stage) %>%
  mutate(delta_mass = Mass_g - lag(Mass_g)) %>%
  filter(complete.cases(delta_mass))
```
T-test to see if the change in mass is significantly different from 0. T-test on the mean change in mass, so only one observation per indiv. Don't need a paired t-test. 
```{r}
t.test(dac_or_1wac$delta_mass)
#Result: There was no change in mass altogether. 
```
Now seeing if the change in mass is significantly different between treatments 
```{r}
mass_lm <- lm(data = dac_or_1wac, 
   delta_mass ~ Hydration_Trmt)

summary(mass_lm)
anova(mass_lm)

#The change in mass was significantly different for the two treatment groups (estimate = 37.060, SE = 6.43, F(1, 18) = 33.13, p = <0.0001)
```
Creating a df with only W treatment and only C treatment 
```{r}
dac_or_1wac_hyd <- dac_or_1wac %>%
  filter(Hydration_Trmt == "W")

dac_or_1wac_control <- dac_or_1wac %>%
  filter(Hydration_Trmt == "C")
```

T-test to see if the change in mass is significantly different from 0 for hydration group.
```{r}
t.test(dac_or_1wac_hyd$delta_mass)
#For the hydration treatment, mass significantly increased after treatment (t = 3.72, df = 9, p = 0.0048)
```
T-test to see if the change in mass is significantly different from 0 for control group.
```{r}
t.test(dac_or_1wac_control$delta_mass)
#For the control treatment, mass significantly decreased after treatment (t = -4.74, df = 9, p = 0.0011)
```
Change in mass is significantly different for the two treatment groups. WHoo!
CI
```{r}
mass_lm_CI <- data.frame(emmeans(mass_lm, "Hydration_Trmt"))
```

Figure
```{r}
ggplot() +
  geom_jitter(data = dac_or_1wac, 
             aes(x = Hydration_Trmt, 
                 y = delta_mass, 
                 color = Hydration_Trmt),
             size = 2,
             alpha = 0.5) +
  geom_point(data = mass_lm_CI, 
             aes(x = Hydration_Trmt, 
                 y = emmean),
             color = "black", 
             size = 2) +
  theme_classic() +
  annotate(geom = "text", x = 1, y = 30, label = "p < 0.0001", 
           size = 5) +
  scale_color_manual(values = c("C" = "orange2", "W" = "royalblue4")) +
  labs(x = "", y = "Change in Mass (g)", colour = "Hydration Treatment") +
  geom_errorbar(data = mass_lm_CI, aes(x = Hydration_Trmt,
                               y = emmean, 
                               ymin = lower.CL, 
                               ymax = upper.CL,
                               width = .3),
                color = "black") +
  geom_hline(yintercept = 0, linetype = 'dashed', col = 'grey') +
  theme(text = element_text(color = "black", 
                            size = 22),
        axis.text = element_text(color = "black", 
                                 size = 16)) +
  scale_y_continuous(limits = c(-45, 60),
                  breaks = c(-45, -30, -15, 0, 15, 30, 45, 60)) -> change_mass_tmt_mothers
```

```{r}
dac_or_1wac_temp[ , 5] <- factor(dac_or_1wac_temp$Preg_Stage, levels = c("DAC", "1WAC"), labels = c("Before Treatment", "After Treatment"))
```

```{r}
dac_or_1wac <- dac_or_1wac %>%
  mutate(mass_relative = 0)
```

```{r}
dac_or_1wac[ , 5] <- factor(dac_or_1wac$Preg_Stage, levels = c("DAC", "1WAC"), labels = c("Before Treatment", "After Treatment"))
```

```{r}
mass_df <- full_join(dac_or_1wac_temp, dac_or_1wac)

as.numeric(mass_df$delta_mass)

mass_df[ ,26] <- replace(mass_df$delta_mass,is.na(mass_df$delta_mass), 0)
```


```{r}
  ggplot(data = mass_df, 
         aes(x = Preg_Stage, 
           y = delta_mass, 
           colour = Hydration_Trmt)) +
  geom_point(data = mass_df,
             aes(x = Preg_Stage, 
                 y = delta_mass, 
                 colour = Hydration_Trmt),
                 size = 2,
                alpha = 0.5) +
  theme_classic() +
  geom_hline(yintercept = 0, linetype = 'dashed', col = 'grey')+
  geom_line(aes(group = Indiv_ID)) +
  annotate(geom = "text", x = 1, y = 30, label = "p = 0.0048", 
           size = 5, color = "royalblue4") +
  annotate(geom = "text", x = 1, y = -30, label = "p = 0.0011", 
           size = 5, color = "orange2") +
  scale_color_manual(values = c("C" = "orange2", "W" = "royalblue4")) +
  labs(x = "", y = "Change in Mass (g)", colour = "Hydration Treatment") +
  theme(text = element_text(color = "black",
                            size = 22),
        axis.text = element_text(color = "black", 
                                 size = 16),
        legend.text = element_text(color = "black",
                                 size = 22),
        plot.title = element_text(color = "black",
                                  size = 22),
        legend.text.align = 0,
        legend.position = "right") +
  scale_y_continuous(limits = c(-45, 60),
                  breaks = c(-45, -30, -15, 0, 15, 30, 45, 60)) -> change_mass_indiv
```

```{r}
ggarrange(change_mass_tmt_mothers,
           change_mass_indiv,
          ncol = 1, nrow = 2,
          labels = c("A", "B"),
          common.legend = TRUE,
          legend = "bottom"
          ) -> mothers_change_mass

ggsave("mothers change in mass.png", 
       plot = mothers_change_mass, 
       width = 6, 
       height = 12)
```
#***SAVANNAH: OSMOLALITY MODEL
NEW OSMOL ANALYSIS
```{r}
osmol <- full_join(osmolality_post_tmt_df, mothers_baseline)

osmol_2 <- osmol %>%
  mutate(Preg_Stage2 = case_when(Preg_Stage == "DAC" ~ "Before Treatment", 
                                 Preg_Stage == "1WAC" ~ "After Treatment", 
                                 Preg_Stage == "DAB" ~ "After Treatment")) %>%
  mutate(Preg_Stage2 = factor(Preg_Stage2, levels = c("Before Treatment", 
                                                      "After Treatment")))
```

```{r}
osmol_lm_time_tmt <- lmer(data = osmol_2, Plasma_Osmol_Rep_mean ~ Hydration_Trmt * Preg_Stage2 + (1|Indiv_ID))

Means3 <- emmeans(osmol_lm_time_tmt, pairwise ~ Preg_Stage2 | Hydration_Trmt)
Means3$emmean
Means3$contrasts

Means4 <- emmeans(osmol_lm_time_tmt, pairwise ~ Hydration_Trmt | Preg_Stage2)
Means4$emmean
Means4$contrasts


osmol_lm_time_tmt_CI <- data.frame(emmeans(osmol_lm_time_tmt, pairwise ~ Hydration_Trmt | Preg_Stage2)$emmean)

tmt_contrasts <- data.frame(emmeans(osmol_lm_time_tmt, pairwise ~ Hydration_Trmt | Preg_Stage2)$contrasts)

pregstage_contrasts <- data.frame(emmeans(osmol_lm_time_tmt, pairwise ~ Preg_Stage2 | Hydration_Trmt)$contrasts)
#is it different between the two time points? 


summary(osmol_lm_time_tmt)
anova(osmol_lm_time_tmt)
```
```{r}
ggplot() +
  geom_jitter(data = osmol_2, 
             aes(x = Preg_Stage2, 
                 y = Plasma_Osmol_Rep_mean, 
                 color = Hydration_Trmt),
             size = 2,
             alpha = 0.5,
             show.legend = TRUE,
             position = position_jitter(height = 0, width = 0.3)) +
  theme_classic() +
#  annotate(geom = "text", x = 1, y = 370, label = "p < 0.0001", 
      #     size = 5) +
  scale_color_manual(values = c("C" = "orange2", "W" = "royalblue4")) +
  labs(x = "", y = "Plasma Osmolality (mmol kg-1)", color = "Treatment") +
  geom_line(data = osmol_lm_time_tmt_CI, 
                aes(x = Preg_Stage2,
                               y = emmean, 
                               width = .3,
                    group = Hydration_Trmt,
                   # group = 1,
                    color = Hydration_Trmt)) +
  geom_errorbar(data = osmol_lm_time_tmt_CI, 
                aes(x = Preg_Stage2,
                               y = emmean, 
                               ymin = lower.CL, 
                               ymax = upper.CL,
                               width = .3,
                    color = Hydration_Trmt)) +
  geom_point(data = osmol_lm_time_tmt_CI, 
             aes(x = Preg_Stage2, 
                 y = emmean,
                 color = Hydration_Trmt), 
             size = 3) +
   theme(text = element_text(color = "black",
                            size = 22),
        axis.text = element_text(color = "black", 
                                 size = 16),
        legend.text = element_text(color = "black",
                                 size = 22),
        plot.title = element_text(color = "black",
                                  size = 22),
        legend.text.align = 0,
        legend.position = "right") + 
  scale_y_continuous(limits = c(280, 382), breaks = seq(280, 382, by = 20)) -> mother_osmolality_all_fig

ggsave("Mother Osmolality All.png", 
       plot = mother_osmolality_all_fig,
       width = 4,
       height = 4)
```
#***SAVANNAh: CEWL ANALYSIS
```{r}
cewl_lm_time_tmt <- lmer(data = osmol_2, CEWL_g_m2h ~ Hydration_Trmt * Preg_Stage2 + (1|Indiv_ID))



Means5 <- emmeans(cewl_lm_time_tmt, pairwise ~ Preg_Stage2 | Hydration_Trmt)
Means5$emmean
Means5$contrasts

Means6 <- emmeans(cewl_lm_time_tmt, pairwise ~ Hydration_Trmt | Preg_Stage2)
Means6$emmean
Means6$contrasts



summary(cewl_lm_time_tmt)
anova(cewl_lm_time_tmt)

cewl_lm_time_tmt_CI <- data.frame(emmeans(cewl_lm_time_tmt, pairwise ~ Hydration_Trmt | Preg_Stage2)$emmean)

tmt_contrasts_cewl <- data.frame(emmeans(cewl_lm_time_tmt, pairwise ~ Hydration_Trmt | Preg_Stage2)$contrasts)

pregstage_contrasts_cewl <- data.frame(emmeans(cewl_lm_time_tmt, pairwise ~ Preg_Stage2 | Hydration_Trmt)$contrasts)
#is it different between the two time points? 
```

```{r}
ggplot() +
  geom_jitter(data = osmol_2, 
             aes(x = Preg_Stage2, 
                 y = CEWL_g_m2h, 
                 color = Hydration_Trmt),
             size = 2,
             alpha = 0.5,
             show.legend = TRUE,
             position = position_jitter(height = 0, width = 0.3)) +
  theme_classic() +
#  annotate(geom = "text", x = 1, y = 370, label = "p < 0.0001", 
      #     size = 5) +
  scale_color_manual(values = c("C" = "orange2", "W" = "royalblue4")) +
  labs(x = "", y = "CEWL (g m2h-1)", color = "Treatment") +
  geom_line(data = cewl_lm_time_tmt_CI, 
                aes(x = Preg_Stage2,
                               y = emmean, 
                               width = .3,
                    group = Hydration_Trmt,
                   # group = 1,
                    color = Hydration_Trmt)) +
  geom_errorbar(data = cewl_lm_time_tmt_CI, 
                aes(x = Preg_Stage2,
                               y = emmean, 
                               ymin = lower.CL, 
                               ymax = upper.CL,
                               width = .3,
                    color = Hydration_Trmt)) +
  geom_point(data = cewl_lm_time_tmt_CI, 
             aes(x = Preg_Stage2, 
                 y = emmean,
                 color = Hydration_Trmt), 
             size = 3) +
   theme(text = element_text(color = "black",
                            size = 22),
        axis.text = element_text(color = "black", 
                                 size = 16),
        legend.text = element_text(color = "black",
                                 size = 22),
        plot.title = element_text(color = "black",
                                  size = 22),
        legend.text.align = 0,
        legend.position = "right")  -> mother_cewl_all
 # scale_y_continuous(limits = c(280, 382), breaks = seq(280, 382, by = 20)) -> mother_osmolality_all_fig
```

```{r}
ggarrange(mother_osmolality_all_fig,
           mother_cewl_all,
          ncol = 1, nrow = 2,
          labels = c("A", "B"),
          common.legend = TRUE,
          legend = "bottom"
          ) -> mothers_osmol_cewl_all

ggsave("mothers change in cewl and osmol.png", 
       plot = mothers_osmol_cewl_all, 
       width = 6, 
       height = 12)
```
#*PUBLICATION FIGURES
##*FIGURE 1
###osmol raw fig
```{r}
ggplot() +
  geom_jitter(data = osmol_2, 
             aes(x = Preg_Stage2, 
                 y = Plasma_Osmol_Rep_mean, 
                 color = Hydration_Trmt,
                 shape = Hydration_Trmt),
             size = 2.5,
             alpha = 0.5,
             show.legend = TRUE,
             position = position_jitter(height = 0, width = 0.3)) +
  theme_classic() +
 annotate(geom = "text", x = 1, y = 370, label = "*", 
           size = 10) +
 annotate(geom = "text", x = 2, y = 370, label = "*", 
           size = 10) +
 annotate(geom = "text", x = 2.5, y = 328, label = "*", 
           size = 10, color = "orange2") +
 annotate(geom = "text", x = 2.5, y = 316, label = "*", 
           size = 10, color = "royalblue4") +
  scale_color_manual(values = c("orange2", "royalblue4"), labels = c("C" = "Control", "W" = "Hydration Treatment"), name = NULL) +
  scale_shape_manual(values = c(15, 17), name = NULL, labels = c("C" = "Control", "W" = "Hydration Treatment")) +
  labs(x = "", y = "Plasma Osmolality (mmol kg-1)", color = "Treatment") +
  geom_line(data = osmol_lm_time_tmt_CI,
                aes(x = Preg_Stage2,
                               y = emmean, 
                               width = .3,
                    group = Hydration_Trmt,
                   # group = 1,
                    color = Hydration_Trmt)) +
  geom_errorbar(data = osmol_lm_time_tmt_CI, 
                aes(x = Preg_Stage2,
                               y = emmean, 
                               ymin = lower.CL, 
                               ymax = upper.CL,
                               width = .3,
                    color = Hydration_Trmt)) +
  geom_point(data = osmol_lm_time_tmt_CI, 
             aes(x = Preg_Stage2, 
                 y = emmean,
                 color = Hydration_Trmt,
                 shape = Hydration_Trmt), 
             size = 4) +
   theme(text = element_text(color = "black",
                            size = 22),
        axis.text = element_text(color = "black", 
                                 size = 16),
        legend.text = element_text(color = "black",
                                 size = 22),
        plot.title = element_text(color = "black",
                                  size = 22),
        legend.text.align = 0,
        legend.position = "right") + 
  scale_y_continuous(limits = c(280, 382), breaks = seq(280, 382, by = 20))-> mother_osmolality_all_fig_pub
```
###cewl raw fig
```{r}
ggplot() +
  geom_jitter(data = osmol_2, 
             aes(x = Preg_Stage2, 
                 y = CEWL_g_m2h, 
                 color = Hydration_Trmt,
                 shape = Hydration_Trmt),
             size = 2.5,
             alpha = 0.5,
             show.legend = TRUE,
             position = position_jitter(height = 0, width = 0.3)) +
  theme_classic() +
  annotate(geom = "text", x = 2.5, y = 16, label = "//", 
           size = 7) +
  annotate(geom = "text", x = 1, y = 28, label = "NS", 
           size = 4) +
  annotate(geom = "text", x = 2, y = 28, label = "NS", 
           size = 4) +
   scale_color_manual(values = c("orange2", "royalblue4"), labels = c("C" = "Control", "W" = "Hydration Treatment"), name = NULL) +
  scale_shape_manual(values = c(15, 17), name = NULL, labels = c("C" = "Control", "W" = "Hydration Treatment")) +
  labs(x = "", y = "CEWL (g m2h-1)", color = "Treatment") +
  geom_line(data = cewl_lm_time_tmt_CI, 
                aes(x = Preg_Stage2,
                               y = emmean, 
                               width = .3,
                    group = Hydration_Trmt,
                   # group = 1,
                    color = Hydration_Trmt)) +
  geom_errorbar(data = cewl_lm_time_tmt_CI, 
                aes(x = Preg_Stage2,
                               y = emmean, 
                               ymin = lower.CL, 
                               ymax = upper.CL,
                               width = .3,
                    color = Hydration_Trmt)) +
  geom_point(data = cewl_lm_time_tmt_CI, 
             aes(x = Preg_Stage2, 
                 y = emmean,
                 color = Hydration_Trmt,
                 shape = Hydration_Trmt), 
             size = 4) +
   theme(text = element_text(color = "black",
                            size = 22),
        axis.text = element_text(color = "black", 
                                 size = 16),
        legend.text = element_text(color = "black",
                                 size = 22),
        plot.title = element_text(color = "black",
                                  size = 22),
        legend.text.align = 0,
        legend.position = "right")  -> mother_cewl_all_pub
 # scale_y_continuous(limits = c(280, 382), breaks = seq(280, 382, by = 20)) -> 
```
###change in mass fig
```{r}
  ggplot(data = mass_df, 
         aes(x = Preg_Stage, 
           y = delta_mass, 
           colour = Hydration_Trmt,
           shape = Hydration_Trmt)) +
  geom_point(data = mass_df,
             aes(x = Preg_Stage, 
                 y = delta_mass, 
                 colour = Hydration_Trmt),
                 size = 2.5,
                alpha = .5) +
  theme_classic() +
  annotate(geom = "text", x = 2.5, y = 30, label = "*", 
           size = 10, color = "royalblue4") +
  annotate(geom = "text", x = 2.5, y = -30, label = "*", 
           size = 10, color = "orange2") +
  geom_hline(yintercept = 0, linetype = 'dashed', col = 'grey')+
  geom_line(aes(group = Indiv_ID), alpha = 0.5) +
  annotate(geom = "text", x = 2, y = 60, label = "*", 
           size = 10) +
 # annotate(geom = "text", x = 1, y = -30, label = "p = 0.0011", 
   #        size = 5, color = "orange2") +
  scale_color_manual(values = c("orange2", "royalblue4"), labels = c("C" = "Control", "W" = "Hydration Treatment"), name = NULL) +
  scale_shape_manual(values = c(15, 17), name = NULL, labels = c("C" = "Control", "W" = "Hydration Treatment")) +
  labs(x = "", y = "Change in Mass (g)", colour = "Hydration Treatment") +
  theme(text = element_text(color = "black",
                            size = 22),
        axis.text = element_text(color = "black", 
                                 size = 16),
        legend.text = element_text(color = "black",
                                 size = 22),
        plot.title = element_text(color = "black",
                                  size = 22),
        legend.text.align = 0,
        legend.position = "right") +
  scale_y_continuous(limits = c(-45, 60),
                  breaks = c(-45, -30, -15, 0, 15, 30, 45, 60)) -> change_mass_indiv_pub
```
###mass raw fig
```{r}
ggplot() +
  geom_jitter(data = dac_or_1wac_temp, 
             aes(x = Preg_Stage, 
                 y = Mass_g, 
                 color = Hydration_Trmt,
                 shape = Hydration_Trmt),
             size = 2.5,
             alpha = 0.5,
             show.legend = TRUE,
             position = position_jitter(height = 0, width = 0.3)) +
  theme_classic() +
annotate(geom = "text", x = 2.5, y = 455, label = "*", 
           size = 10, color = "orange2") +
 annotate(geom = "text", x = 2.5, y = 490, label = "*", 
           size = 10, color = "royalblue4") +
 annotate(geom = "text", x = 2, y = 730, label = "*", 
           size = 10) +
 annotate(geom = "text", x = 1, y = 740, label = "NS", 
           size = 4) +
  scale_color_manual(values = c("orange2", "royalblue4"), labels = c("C" = "Control", "W" = "Hydration Treatment"), name = NULL) +
  scale_shape_manual(values = c(15, 17), name = NULL, labels = c("C" = "Control", "W" = "Hydration Treatment")) +
  labs(x = "", y = "Mass (g)", color = "Treatment") +
  geom_line(data = new_mass_lm_CI,
                aes(x = Preg_Stage,
                               y = emmean, 
                               width = .3,
                    group = Hydration_Trmt,
                   # group = 1,
                    color = Hydration_Trmt)) +
  geom_errorbar(data = new_mass_lm_CI, 
                aes(x = Preg_Stage,
                               y = emmean, 
                               ymin = lower.CL, 
                               ymax = upper.CL,
                               width = .3,
                    color = Hydration_Trmt)) +
  geom_point(data = new_mass_lm_CI, 
             aes(x = Preg_Stage, 
                 y = emmean,
                 color = Hydration_Trmt,
                 shape = Hydration_Trmt), 
             size = 4) +
   theme(text = element_text(color = "black",
                            size = 22),
        axis.text = element_text(color = "black", 
                                 size = 16),
        legend.text = element_text(color = "black",
                                 size = 22),
        plot.title = element_text(color = "black",
                                  size = 22),
        legend.text.align = 0,
        legend.position = "right") +
  scale_y_continuous(limits = c(280, 800), 
                     breaks = seq(280, 800, by = 100)) -> mother_mass_all_fig_pub
```

###change in osmol fig
```{r}
  ggplot(data = osmol_2, 
         aes(x = Preg_Stage2, 
           y = Change_in_osmol, 
           colour = Hydration_Trmt,
           shape = Hydration_Trmt)) +
  geom_point(data = osmol_2,
             aes(x = Preg_Stage2, 
                 y = Change_in_osmol, 
                 colour = Hydration_Trmt),
                 size = 2.5,
                alpha = .5) +
  theme_classic() +
  annotate(geom = "text", x = 2.5, y = 20, label = "*", 
          size = 10, color = "orange2") +
  annotate(geom = "text", x = 2.5, y = -30, label = "*", 
          size = 10, color = "royalblue4") +
  annotate(geom = "text", x = 2, y = 45, label = "*", 
          size = 10) +
  geom_hline(yintercept = 0, linetype = 'dashed', col = 'grey')+
  geom_line(aes(group = Indiv_ID), alpha = 0.5) +
  scale_color_manual(values = c("orange2", "royalblue4"), labels = c("C" = "Control", "W" = "Hydration Treatment"), name = NULL) +
  scale_shape_manual(values = c(15, 17), name = NULL, labels = c("C" = "Control", "W" = "Hydration Treatment")) +
  labs(x = "", y = "Change in Osmolality (mmol kg-1)", colour = "Hydration Treatment") +
  theme(text = element_text(color = "black",
                            size = 22),
        axis.text = element_text(color = "black", 
                                 size = 16),
        legend.text = element_text(color = "black",
                                 size = 22),
        plot.title = element_text(color = "black",
                                  size = 22),
        legend.text.align = 0,
        legend.position = "right") +
  scale_y_continuous(limits = c(-55, 45),
                  breaks = c(-60, -45, -30, -15, 0, 15, 30, 45)) -> change_osmol_indiv_pub
```
###change in cewl fig
```{r}
  ggplot(data = osmol_2, 
         aes(x = Preg_Stage2, 
           y = Change_in_CEWL, 
           colour = Hydration_Trmt,
           shape = Hydration_Trmt)) +
  geom_point(data = osmol_2,
             aes(x = Preg_Stage2, 
                 y = Change_in_CEWL, 
                 colour = Hydration_Trmt),
                 size = 2.5,
                alpha = .5) +
  theme_classic() +
 annotate(geom = "text", x = 2.5, y = -5, label = "//", 
          size = 7) +
annotate(geom = "text", x = 2, y = 10, label = "NS", 
          size = 4) +
  #annotate(geom = "text", x = 2, y = 45, label = "*", 
         # size = 8) +
  geom_hline(yintercept = 0, linetype = 'dashed', col = 'grey')+
  geom_line(aes(group = Indiv_ID), alpha = 0.5) +
  scale_color_manual(values = c("orange2", "royalblue4"), labels = c("C" = "Control", "W" = "Hydration Treatment"), name = NULL) +
  scale_shape_manual(values = c(15, 17), name = NULL, labels = c("C" = "Control", "W" = "Hydration Treatment")) +
  labs(x = "", y = "Change in CEWL (g m2h-1)", colour = "Hydration Treatment") +
  theme(text = element_text(color = "black",
                            size = 22),
        axis.text = element_text(color = "black", 
                                 size = 16),
        legend.text = element_text(color = "black",
                                 size = 22),
        plot.title = element_text(color = "black",
                                  size = 22),
        legend.text.align = 0,
        legend.position = "right") +
 scale_y_continuous(limits = c(-16, 10),
                 breaks = c(-15, -10, -5, 0, 5, 10)) -> change_cewl_indiv_pub
  
```
####arrange
```{r}
ggarrange(mother_osmolality_all_fig_pub,
            change_osmol_indiv_pub,
            mother_mass_all_fig_pub,
          change_mass_indiv_pub,
          mother_cewl_all_pub,
          change_cewl_indiv_pub,
          ncol = 2, nrow = 3,
          labels = c("A", "B", "C", "D", "E", "F"),
          common.legend = TRUE,
          legend = "bottom"
          ) -> figure_1_publication

ggsave("Publication Figure 1.png", 
       plot = figure_1_publication, 
       width = 10, 
       height = 18)
```

##Fig 2


```{r}
ggplot(data = mother_data_all_final_8, aes(x = msmt_temp_C, y = CEWL_g_m2h)) +
  geom_point(size = 2, 
             alpha = 0.7,
             color = "springgreen3") +
  annotate(geom = "text", 
           x = 26.5, 
           y = 10, 
           label = "p < 0.0001", 
           size = 5) +
  theme_classic() +
  geom_smooth(aes(x = msmt_temp_C, y = CEWL_g_m2h),
              method = "lm", 
              se = TRUE, 
              show.legend = TRUE, 
              size = 1,
              color = "black") +
  labs(x = "Ambient Temperature (°C)", 
       y = "CEWL (g m2h-1)") +
  theme(text = element_text(color = "black",
                            size = 22),
        axis.text = element_text(color = "black", 
                                 size = 16),
        legend.text = element_text(color = "black",
                                 size = 22),
        plot.title = element_text(color = "black",
                                  size = 22),
        legend.text.align = 0,
        legend.position = "right") +
  #scale_x_continuous(breaks = c(0, 2, 4, 6, 8, 10, 12, 14, 16), limits = c(0, 16)) +
 scale_y_continuous(limits = c(9, 30.5),
                  breaks = seq(9, 30.5, by = 3)) -> temp_v_cewl_females_pub

```

```{r}

ggplot(data = mother_data_all_final_8, aes(x = msmt_RH_percent, y = CEWL_g_m2h)) +
  geom_point(size = 2, 
             alpha = 0.7, 
             color = "springgreen3") +
  annotate(geom = "text", 
           x = 44, 
           y = 10, 
           label = "p < 0.0001", 
           size = 5) +
  theme_classic() +
  geom_smooth(aes(x = msmt_RH_percent, y = CEWL_g_m2h),
              method = "lm", 
              se = TRUE, 
              show.legend = TRUE, 
              size = 1,
              color = "black") +
  labs(x = "Ambient Humidity (%)", 
       y = "") +
  theme(text = element_text(color = "black",
                            size = 22),
        axis.text = element_text(color = "black", 
                                 size = 16),
        legend.text = element_text(color = "black",
                                 size = 22),
        plot.title = element_text(color = "black",
                                  size = 22),
        legend.text.align = 0,
        legend.position = "right") +
scale_x_continuous(breaks = c(34, 36, 38, 40, 42, 44, 46, 48), limits = c(34, 48)) +
 scale_y_continuous(limits = c(9, 30.5),
                  breaks = seq(9, 30.5, by = 3)) -> humidity_v_cewl_females_pub

```

```{r}
ggarrange(temp_v_cewl_females_pub, humidity_v_cewl_females_pub,
          ncol = 2, nrow = 1,
          labels = c("A", "B"),
          common.legend = TRUE,
          legend = "bottom"
          ) -> CEWL_v_temp_humidity_mothers_pub

ggsave("CEWL vs Temp and Humidity Females.png", 
       plot = CEWL_v_temp_humidity_mothers_pub, 
       width = 10, 
       height = 4)
```